\bibitem[Anderson(1972)]{anderson1972more}
P.~W. Anderson.
\newblock More is different.
\newblock \emph{Science}, 177\penalty0 (4047):\penalty0 393--396, 1972.

\bibitem[Barab{\'a}si(2011)]{barabasi2011network}
Albert-L{\'a}szl{\'o} Barab{\'a}si.
\newblock The network takeover.
\newblock \emph{Nat. Phys.}, 8\penalty0 (1):\penalty0 14, 2011.

\bibitem[Albert and Barab{\'a}si(2002)]{albert2002statistical}
R{\'e}ka Albert and Albert-L{\'a}szl{\'o} Barab{\'a}si.
\newblock Statistical mechanics of complex networks.
\newblock \emph{Rev. Mod. Phys.}, 74\penalty0 (1):\penalty0 47, 2002.

\bibitem[Dorogovtsev and {J. F. F. Mendes}(2002)]{dorogovtsev2002evolution}
S.~N. Dorogovtsev and {J. F. F. Mendes}.
\newblock Evolution of networks.
\newblock \emph{Adv. Phys.}, 51\penalty0 (4):\penalty0 1079--1187, 2002.

\bibitem[Newman(2003{\natexlab{a}})]{newman2003structure}
M.~E.~J. Newman.
\newblock The structure and function of complex networks.
\newblock \emph{SIAM Rev.}, 45:\penalty0 167--256, 2003{\natexlab{a}}.

\bibitem[Boccaletti et~al.(Fervier 2006)Boccaletti, Latora, Moreno, Chavez, and
Hwang]{boccaletti2006complex}
S.~Boccaletti, V.~Latora, Y.~Moreno, M.~Chavez, and D-U. Hwang.
\newblock Complex networks : {{Structure}} and dynamics.
\newblock \emph{Phys. Rep.}, 424\penalty0 (4-5):\penalty0 175--308, Fervier
2006.

\bibitem[Newman(2010)]{newman2010networks}
M.~E.~J. Newman.
\newblock \emph{Networks: An Introduction}.
\newblock {Oxford University Press}, {Oxford; New York}, 2010.
\newblock ISBN 978-0-19-920665-0 0-19-920665-1.

\bibitem[Estrada(2011)]{estrada2011structure}
Ernesto Estrada.
\newblock \emph{The Structure of Complex Networks: {{Theory}} and
    Applications}.
\newblock {Oxford University Press, Inc.}, {New York, NY, USA}, 2011.
\newblock ISBN 0-19-959175-X 978-0-19-959175-6.

\bibitem[Barab{\'a}si and P{\'o}sfai(2016)]{barabasi2016network}
Albert-L{\'a}szl{\'o} Barab{\'a}si and M{\'a}rton P{\'o}sfai.
\newblock \emph{Network Science}.
\newblock {Cambridge University Press}, {Cambridge}, 2016.
\newblock ISBN 978-1-107-07626-6 1-107-07626-9.

\bibitem[Latora et~al.(2017)Latora, Nicosia, and Russo]{latora2017complex}
Vito Latora, Vincenzo Nicosia, and Giovanni Russo.
\newblock \emph{Complex Networks: {{Principles}}, Methods and Applications}.
\newblock {Cambridge University Press}, 2017.

\bibitem[Butts(2009)]{butts2009revisiting}
Carter~T Butts.
\newblock Revisiting the foundations of network analysis.
\newblock \emph{Science}, 325\penalty0 (5939):\penalty0 414--416, 2009.

\bibitem[Holme and Saram{\"a}ki(2012)]{holme2012temporal}
Petter Holme and Jari Saram{\"a}ki.
\newblock Temporal networks.
\newblock \emph{Phys. Rep.}, 519\penalty0 (3):\penalty0 97--125, 2012.

\bibitem[Boccaletti et~al.(2014)Boccaletti, Bianconi, Criado, Del~Genio,
{G{\'o}mez-Gardenes}, Romance, {Sendina-Nadal}, Wang, and
Zanin]{boccaletti2014structure}
Stefano Boccaletti, Ginestra Bianconi, Regino Criado, Charo~I Del~Genio,
Jes{\'u}s {G{\'o}mez-Gardenes}, Miguel Romance, Irene {Sendina-Nadal}, Zhen
Wang, and Massimiliano Zanin.
\newblock The structure and dynamics of multilayer networks.
\newblock \emph{Phys. Rep.}, 544\penalty0 (1):\penalty0 1--122, 2014.

\bibitem[Levine et~al.(2017)Levine, Bascompte, Adler, and
Allesina]{levine2017beyond}
Jonathan~M Levine, Jordi Bascompte, Peter~B Adler, and Stefano Allesina.
\newblock Beyond pairwise mechanisms of species coexistence in complex
communities.
\newblock \emph{Nature}, 546\penalty0 (7656):\penalty0 56, 2017.

\bibitem[Centola(2010)]{centola2010spread}
Damon Centola.
\newblock The spread of behavior in an online social network experiment.
\newblock \emph{Science}, 329\penalty0 (5996):\penalty0 1194--1197, 2010.

\bibitem[Newman et~al.(2001)Newman, Strogatz, and Watts]{newman2001random}
Mark E.~J. Newman, Steven~H. Strogatz, and Duncan~J. Watts.
\newblock Random graphs with arbitrary degree distributions and their
applications.
\newblock \emph{Phys. Rev. E}, 64:\penalty0 026118, 2001.

\bibitem[Atkin(1972)]{atkin1972cohomology}
Ronald~H Atkin.
\newblock From cohomology in physics to q-connectivity in social science.
\newblock \emph{Int. J. Man-Mach. Stud.}, 4\penalty0 (2):\penalty0 139--167,
1972.

\bibitem[Berge(1973)]{berge1973graphs}
Claude Berge.
\newblock Graphs and hypergraphs.
\newblock 1973.

\bibitem[Atkin(1974)]{atkin1974mathematical}
Ron Atkin.
\newblock \emph{Mathematical Structure in Human Affairs}.
\newblock {Heinemann Educational Publishers}, 1974.

\bibitem[Kivel{\"a} et~al.(2014)Kivel{\"a}, Arenas, Barthelemy, Gleeson,
Moreno, and Porter]{kivela2014multilayer}
Mikko Kivel{\"a}, Alex Arenas, Marc Barthelemy, James~P Gleeson, Yamir Moreno,
and Mason~A Porter.
\newblock Multilayer networks.
\newblock \emph{J Comp Netw}, 2\penalty0 (3):\penalty0 203--271, 2014.

\bibitem[Battiston et~al.(2017{\natexlab{a}})Battiston, Nicosia, and
Latora]{battiston2017new}
Federico Battiston, Vincenzo Nicosia, and Vito Latora.
\newblock The new challenges of multiplex networks: Measures and models.
\newblock \emph{The European Physical Journal Special Topics}, 226\penalty0
(3):\penalty0 401--416, 2017{\natexlab{a}}.

\bibitem[Bianconi(2018)]{bianconi2018multilayer}
Ginestra Bianconi.
\newblock \emph{Multilayer networks: structure and function}.
\newblock Oxford university press, 2018.

\bibitem[Aleta and Moreno(2019)]{aleta2019multilayer}
Alberto Aleta and Yamir Moreno.
\newblock Multilayer networks in a nutshell.
\newblock \emph{Annual Review of Condensed Matter Physics}, 10:\penalty0
45--62, 2019.

\bibitem[Lambiotte et~al.(2019)Lambiotte, Rosvall, and
Scholtes]{lambiotte2019networks}
Renaud Lambiotte, Martin Rosvall, and Ingo Scholtes.
\newblock From networks to optimal higher-order models of complex systems.
\newblock \emph{Nat. Phys.}, page~1, 2019.

\bibitem[Bondy et~al.(1976)Bondy, Murty, et~al.]{bondy1976graph}
John~Adrian Bondy, Uppaluri Siva~Ramachandra Murty, et~al.
\newblock \emph{Graph Theory with Applications}, volume 290.
\newblock {Macmillan London}, 1976.

\bibitem[Alon(2003)]{alon2003biological}
Uri Alon.
\newblock Biological networks: The tinkerer as an engineer.
\newblock \emph{Science}, 301\penalty0 (5641):\penalty0 1866--1867, 2003.

\bibitem[Kashtan and Alon(2005)]{kashtan2005spontaneous}
Nadav Kashtan and Uri Alon.
\newblock Spontaneous evolution of modularity and network motifs.
\newblock \emph{Proc. Natl. Acad. Sci.}, 102\penalty0 (39):\penalty0
13773--13778, 2005.

\bibitem[Grilli et~al.(2017)Grilli, Barab{\'a}s, {Michalska-Smith}, and
Allesina]{grilli2017higher}
Jacopo Grilli, Gy{\"o}rgy Barab{\'a}s, Matthew~J {Michalska-Smith}, and Stefano
Allesina.
\newblock Higher-order interactions stabilize dynamics in competitive network
models.
\newblock \emph{Nature}, 548\penalty0 (7666):\penalty0 210, 2017.

\bibitem[Montoya et~al.(2006)Montoya, Pimm, and
Sol{\'e}]{montoya2006ecological}
Jos{\'e}~M Montoya, Stuart~L Pimm, and Ricard~V Sol{\'e}.
\newblock Ecological networks and their fragility.
\newblock \emph{Nature}, 442\penalty0 (7100):\penalty0 259, 2006.

\bibitem[Borgatti et~al.(2009)Borgatti, Mehra, Brass, and
Labianca]{borgatti2009network}
Stephen~P Borgatti, Ajay Mehra, Daniel~J Brass, and Giuseppe Labianca.
\newblock Network analysis in the social sciences.
\newblock \emph{science}, 323\penalty0 (5916):\penalty0 892--895, 2009.

\bibitem[McPherson et~al.(2001)McPherson, {Smith-Lovin}, and
Cook]{mcpherson2001birds}
Miller McPherson, Lynn {Smith-Lovin}, and James~M Cook.
\newblock Birds of a feather: {{Homophily}} in social networks.
\newblock \emph{Annu. Rev. Sociol.}, 27\penalty0 (1):\penalty0 415--444, 2001.

\bibitem[Gao et~al.(2012)Gao, Buldyrev, Stanley, and Havlin]{gao2012networks}
Jianxi Gao, Sergey~V Buldyrev, H~Eugene Stanley, and Shlomo Havlin.
\newblock Networks formed from interdependent networks.
\newblock \emph{Nat. Phys.}, 8\penalty0 (1):\penalty0 40, 2012.

\bibitem[Buldyrev et~al.(2010)Buldyrev, Parshani, Paul, Stanley, and
Havlin]{buldyrev2010catastrophic}
Sergey~V Buldyrev, Roni Parshani, Gerald Paul, H~Eugene Stanley, and Shlomo
Havlin.
\newblock Catastrophic cascade of failures in interdependent networks.
\newblock \emph{Nature}, 464\penalty0 (7291):\penalty0 1025, 2010.

\bibitem[Bullmore and Sporns(2009)]{bullmore2009complex}
Ed~Bullmore and Olaf Sporns.
\newblock Complex brain networks: Graph theoretical analysis of structural and
functional systems.
\newblock \emph{Nat. Rev. Neurosci.}, 10\penalty0 (3):\penalty0 186, 2009.

\bibitem[Bassett and Sporns(2017)]{bassett2017network}
Danielle~S Bassett and Olaf Sporns.
\newblock Network neuroscience.
\newblock \emph{Nat. Neurosci.}, 20\penalty0 (3):\penalty0 353, 2017.

\bibitem[Medaglia et~al.(2015)Medaglia, Lynall, and
Bassett]{medaglia2015cognitive}
John~D Medaglia, Mary-Ellen Lynall, and Danielle~S Bassett.
\newblock Cognitive network neuroscience.
\newblock \emph{J. Cogn. Neurosci.}, 27\penalty0 (8):\penalty0 1471--1491,
2015.

\bibitem[Bogu{\~n}{\'a} et~al.(2014)Bogu{\~n}{\'a}, Kitsak, and
Krioukov]{boguna2014cosmological}
Mari{\'a}n Bogu{\~n}{\'a}, Maksim Kitsak, and Dmitri Krioukov.
\newblock Cosmological networks.
\newblock \emph{New J. Phys.}, 16\penalty0 (9):\penalty0 093031, 2014.

\bibitem[Fortunato(2010)]{fortunato2010community}
Santo Fortunato.
\newblock Community detection in graphs.
\newblock \emph{Phys. Rep.}, 486\penalty0 (3-5):\penalty0 75--174, 2010.

\bibitem[Palla et~al.(2005)Palla, Der{\'e}nyi, Farkas, and
Vicsek]{palla2005uncovering}
Gergely Palla, Imre Der{\'e}nyi, Ill{\'e}s Farkas, and Tam{\'a}s Vicsek.
\newblock Uncovering the overlapping community structure of complex networks in
nature and society.
\newblock \emph{nature}, 435\penalty0 (7043):\penalty0 814, 2005.

\bibitem[Karrer and Newman(2011)]{karrer2011stochastic}
Brian Karrer and M.~E.~J Newman.
\newblock Stochastic blockmodels and community structure in networks.
\newblock \emph{Phys. Rev. E}, 83\penalty0 (1):\penalty0 016107, 2011.

\bibitem[Lancichinetti and Fortunato(2011)]{lancichinetti2011limits}
Andrea Lancichinetti and Santo Fortunato.
\newblock Limits of modularity maximization in community detection.
\newblock \emph{Phys. Rev. E}, 84\penalty0 (6):\penalty0 066122, 2011.

\bibitem[Abbe and Sandon(2015)]{abbe2015community}
Emmanuel Abbe and Colin Sandon.
\newblock Community detection in general stochastic block models:
{{Fundamental}} limits and efficient algorithms for recovery.
\newblock In \emph{2015 {{IEEE}} 56th Annual Symposium on Foundations of
    Computer Science}, pages 670--688. {IEEE}, 2015.

\bibitem[Lancichinetti et~al.(2008)Lancichinetti, Fortunato, and
Radicchi]{lancichinetti2008benchmark}
Andrea Lancichinetti, Santo Fortunato, and Filippo Radicchi.
\newblock Benchmark graphs for testing community detection algorithms.
\newblock \emph{Phys. Rev. E}, 78\penalty0 (4):\penalty0 046110, 2008.

\bibitem[Guillaume and Latapy(2004)]{guillaume2004bipartite}
Jean-Loup Guillaume and Matthieu Latapy.
\newblock Bipartite structure of all complex networks.
\newblock \emph{Inf Process Lett}, 90\penalty0 (5):\penalty0 215--221, 2004.

\bibitem[Guillaume and Latapy(2006)]{guillaume2006bipartite}
Jean-Loup Guillaume and Matthieu Latapy.
\newblock Bipartite graphs as models of complex networks.
\newblock \emph{Phys. A}, 371\penalty0 (2):\penalty0 795--813, 2006.

\bibitem[Wasserman and Faust(1994)]{wasserman1994social}
Stanley Wasserman and Katherine Faust.
\newblock \emph{Social Network Analysis : {{Methods}} and Applications
    (Structural Analysis in the Social Sciences)}.
\newblock {Cambridge University Press}, 1994.
\newblock ISBN 0-521-38707-8.

\bibitem[Newman et~al.(2002)Newman, Watts, and Strogatz]{newman2002random}
M.~E.~J Newman, Duncan~J Watts, and Steven~H Strogatz.
\newblock Random graph models of social networks.
\newblock \emph{Proc. Natl. Acad. Sci.}, 99\penalty0 (suppl 1):\penalty0
2566--2572, 2002.

\bibitem[Guimer{\`a} et~al.(2007)Guimer{\`a}, {Sales-Pardo}, and
Amaral]{guimera2007module}
Roger Guimer{\`a}, Marta {Sales-Pardo}, and Lu{\'i}s A~Nunes Amaral.
\newblock Module identification in bipartite and directed networks.
\newblock \emph{Phys. Rev. E}, 76\penalty0 (3):\penalty0 036102, 2007.

\bibitem[Zhou et~al.(2007{\natexlab{a}})Zhou, Ren, Medo, and
Zhang]{zhou2007bipartite}
Tao Zhou, Jie Ren, Mat{\'u}{\v s} Medo, and Yi-Cheng Zhang.
\newblock Bipartite network projection and personal recommendation.
\newblock \emph{Phys. Rev. E}, 76\penalty0 (4):\penalty0 046115,
2007{\natexlab{a}}.

\bibitem[Zweig and Kaufmann(2011)]{zweig2011systematic}
Katharina~Anna Zweig and Michael Kaufmann.
\newblock A systematic approach to the one-mode projection of bipartite graphs.
\newblock \emph{Soc. Netw. Anal. Min.}, 1\penalty0 (3):\penalty0 187--218,
2011.

\bibitem[Schaub and Segarra(2018)]{schaub2018flow}
Michael~T Schaub and Santiago Segarra.
\newblock Flow smoothing and denoising: Graph signal processing in the
edge-space.
\newblock In \emph{2018 {{IEEE}} Global Conference on Signal and Information
    Processing ({{GlobalSIP}})}, pages 735--739. {IEEE}, 2018.

\bibitem[Milo et~al.(2002)Milo, {Shen-Orr}, Itzkovitz, Kashtan, Chklovskii, and
Alon]{milo2002network}
Ron Milo, Shai {Shen-Orr}, Shalev Itzkovitz, Nadav Kashtan, Dmitri Chklovskii,
and Uri Alon.
\newblock Network motifs: Simple building blocks of complex networks.
\newblock \emph{Science}, 298\penalty0 (5594):\penalty0 824--827, 2002.

\bibitem[Alon(2007)]{alon2007network}
Uri Alon.
\newblock Network motifs: Theory and experimental approaches.
\newblock \emph{Nat. Rev. Genet.}, 8\penalty0 (6):\penalty0 450, 2007.

\bibitem[Benson et~al.(2016)Benson, Gleich, and Leskovec]{benson2016higher}
Austin~R Benson, David~F Gleich, and Jure Leskovec.
\newblock Higher-order organization of complex networks.
\newblock \emph{Science}, 353\penalty0 (6295):\penalty0 163--166, 2016.

\bibitem[Morgan et~al.(2018)Morgan, Achard, Termenon, Bullmore, and
V{\'e}rtes]{morgan2018low}
Sarah~E Morgan, Sophie Achard, Maite Termenon, Edward~T Bullmore, and Petra~E
V{\'e}rtes.
\newblock Low-dimensional morphospace of topological motifs in human {{fMRI}}
brain networks.
\newblock \emph{Netw Neurosci}, 2\penalty0 (02):\penalty0 285--302, 2018.

\bibitem[{Avena-Koenigsberger} et~al.(2015){Avena-Koenigsberger}, Go{\~n}i,
Sol{\'e}, and Sporns]{avena2015network}
Andrea {Avena-Koenigsberger}, Joaqu{\'i}n Go{\~n}i, Ricard Sol{\'e}, and Olaf
Sporns.
\newblock Network morphospace.
\newblock \emph{J. R. Soc. Interface}, 12\penalty0 (103):\penalty0 20140881,
2015.

\bibitem[{Shen-Orr} et~al.(2002){Shen-Orr}, Milo, Mangan, and
Alon]{shen2002network}
Shai~S {Shen-Orr}, Ron Milo, Shmoolik Mangan, and Uri Alon.
\newblock Network motifs in the transcriptional regulation network of
{{Escherichia}} coli.
\newblock \emph{Nat. Genet.}, 31\penalty0 (1):\penalty0 64, 2002.

\bibitem[Fowler et~al.(2009)Fowler, Dawes, and Christakis]{fowler2009model}
James~H Fowler, Christopher~T Dawes, and Nicholas~A Christakis.
\newblock Model of genetic variation in human social networks.
\newblock \emph{Proc. Natl. Acad. Sci.}, 106\penalty0 (6):\penalty0 1720--1724,
2009.

\bibitem[Paranjape et~al.(2017)Paranjape, Benson, and
Leskovec]{paranjape2017motifs}
Ashwin Paranjape, Austin~R Benson, and Jure Leskovec.
\newblock Motifs in temporal networks.
\newblock In \emph{Proceedings of the Tenth {{ACM}} International Conference on
    Web Search and Data Mining}, pages 601--610. {ACM}, 2017.

\bibitem[Kovanen et~al.(2011)Kovanen, Karsai, Kaski, Kert{\'e}sz, and
Saram{\"a}ki]{kovanen2011temporal}
Lauri Kovanen, M{\'a}rton Karsai, Kimmo Kaski, J{\'a}nos Kert{\'e}sz, and Jari
Saram{\"a}ki.
\newblock Temporal motifs in time-dependent networks.
\newblock \emph{J. Stat. Mech. Theory Exp.}, 2011\penalty0 (11):\penalty0
P11005, 2011.

\bibitem[Mahadevan et~al.(2006)Mahadevan, Krioukov, Fall, and
Vahdat]{mahadevan2006systematic}
Priya Mahadevan, Dmitri Krioukov, Kevin Fall, and Amin Vahdat.
\newblock Systematic topology analysis and generation using degree
correlations.
\newblock In \emph{{{ACM SIGCOMM}} Computer Communication Review}, volume~36,
pages 135--146. {ACM}, 2006.

\bibitem[Orsini et~al.(2015)Orsini, Dankulov, {Colomer-de-Sim{\'o}n},
Jamakovic, Mahadevan, Vahdat, Bassler, Toroczkai, Bogun{\'a}, Caldarelli,
et~al.]{orsini2015quantifying}
Chiara Orsini, Marija~M Dankulov, Pol {Colomer-de-Sim{\'o}n}, Almerima
Jamakovic, Priya Mahadevan, Amin Vahdat, Kevin~E Bassler, Zolt{\'a}n
Toroczkai, Mari{\'a}n Bogun{\'a}, Guido Caldarelli, et~al.
\newblock Quantifying randomness in real networks.
\newblock \emph{Nat. Commun.}, 6:\penalty0 8627, 2015.

\bibitem[Der{\'e}nyi et~al.(2005)Der{\'e}nyi, Palla, and
Vicsek]{derenyi2005clique}
Imre Der{\'e}nyi, Gergely Palla, and Tam{\'a}s Vicsek.
\newblock Clique percolation in random networks.
\newblock \emph{Phys. Rev. Lett.}, 94\penalty0 (16):\penalty0 160202, 2005.

\bibitem[Dunbar and Spoors(1995)]{dunbar1995social}
Robin~IM Dunbar and Matt Spoors.
\newblock Social networks, support cliques, and kinship.
\newblock \emph{Hum. Nat.}, 6\penalty0 (3):\penalty0 273--290, 1995.

\bibitem[Provan and Sebastian(1998)]{provan1998networks}
Keith~G Provan and Juliann~G Sebastian.
\newblock Networks within networks: {{Service}} link overlap, organizational
cliques, and network effectiveness.
\newblock \emph{Acad. Manage. J.}, 41\penalty0 (4):\penalty0 453--463, 1998.

\bibitem[Hatcherr(2002)]{hatcher2002algebraic}
A.~Hatcherr.
\newblock Algebraic topology.
\newblock 2002.

\bibitem[Horak and Jost(2013)]{horak2013spectra}
Danijela Horak and J{\"u}rgen Jost.
\newblock Spectra of combinatorial {{Laplace}} operators on simplicial
complexes.
\newblock \emph{Adv. Math.}, 244:\penalty0 303--336, 2013.

\bibitem[Muhammad and Egerstedt(2006)]{muhammad2006control}
Abubakr Muhammad and Magnus Egerstedt.
\newblock Control using higher order {{Laplacians}} in network topologies.
\newblock In \emph{Proc. of 17th International Symposium on Mathematical Theory
    of Networks and Systems}, pages 1024--1038. {Citeseer}, 2006.

\bibitem[Costa and Farber(2016)]{costa2016random}
Armindo Costa and Michael Farber.
\newblock Random simplicial complexes.
\newblock In \emph{Configuration Spaces}, pages 129--153. {Springer, Berlin},
2016.

\bibitem[Bianconi and Rahmede(2016)]{bianconi2016network}
Ginestra Bianconi and Christoph Rahmede.
\newblock Network geometry with flavor: {{From}} complexity to quantum
geometry.
\newblock \emph{Phys. Rev. E}, 93\penalty0 (3):\penalty0 032315, 2016.

\bibitem[Ghrist(2014)]{ghrist2014elementary}
R.~Ghrist.
\newblock \emph{Elementary Applied Topology}.
\newblock {CreateSpace Independent Publishing Platform}, 2014.
\newblock ISBN 978-1-5028-8085-7.

\bibitem[Carlsson(2009)]{carlsson2009topology}
Gunnar Carlsson.
\newblock Topology and data.
\newblock \emph{Bull. Am. Math. Soc.}, 46\penalty0 (2):\penalty0 255--308,
2009.

\bibitem[Patania et~al.(2017{\natexlab{a}})Patania, Vaccarino, and
Petri]{patania2017topological}
Alice Patania, Francesco Vaccarino, and Giovanni Petri.
\newblock Topological analysis of data.
\newblock \emph{EPJ Data Sci.}, 6\penalty0 (1):\penalty0 7, 2017{\natexlab{a}}.

\bibitem[Expert et~al.(2019)Expert, Lord, Kringelbach, and
Petri]{expert2019topological}
Paul Expert, Louis-David Lord, Morten~L. Kringelbach, and Giovanni Petri.
\newblock Editorial: {{Topological}} neuroscience.
\newblock \emph{Netw Neurosci}, 3\penalty0 (3):\penalty0 653--655, 2019.

\bibitem[Higuchi et~al.(1999)Higuchi, Miyoshi, and
Tsujishita]{higuchi1999higher}
Akira Higuchi, Hiroyuki Miyoshi, and Toru Tsujishita.
\newblock Higher dimensional hypercategories.
\newblock \emph{arXiv:math/9907150}, 1999.

\bibitem[Louis(2015)]{louis2015hypergraph}
Anand Louis.
\newblock Hypergraph {Markov} operators, eigenvalues and approximation
algorithms.
\newblock In \emph{Proceedings of the Forty-Seventh Annual {{ACM}} Symposium on
    {{Theory}} of Computing}, pages 713--722. {ACM}, 2015.

\bibitem[Chan et~al.(2018)Chan, Louis, Tang, and Zhang]{chan2018spectral}
T-H~Hubert Chan, Anand Louis, Zhihao~Gavin Tang, and Chenzi Zhang.
\newblock Spectral properties of hypergraph {{Laplacian}} and approximation
algorithms.
\newblock \emph{J. ACM JACM}, 65\penalty0 (3):\penalty0 15, 2018.

\bibitem[Chan and Liang(2019)]{chan2019generalizing}
T-H~Hubert Chan and Zhibin Liang.
\newblock Generalizing the hypergraph {Laplacian} via a diffusion process with
mediators.
\newblock \emph{Theor. Comput. Sci.}, 2019.

\bibitem[Ghoshal et~al.(2009)Ghoshal, Zlati{\'c}, Caldarelli, and
Newman]{ghoshal2009random}
Gourab Ghoshal, Vinko Zlati{\'c}, Guido Caldarelli, and M.~E.~J Newman.
\newblock Random hypergraphs and their applications.
\newblock \emph{Phys. Rev. E}, 79\penalty0 (6):\penalty0 066118, 2009.

\bibitem[Kumar et~al.(2018)Kumar, Vaidyanathan, Ananthapadmanabhan,
Parthasarathy, and Ravindran]{kumar2018hypergraph}
Tarun Kumar, Sankaran Vaidyanathan, Harini Ananthapadmanabhan, Srinivasan
Parthasarathy, and Balaraman Ravindran.
\newblock Hypergraph clustering: {{A}} modularity maximization approach.
\newblock \emph{arXiv:1812.10869}, 2018.

\bibitem[Chodrow and Mellor(2020)]{chodrow2020annotated}
Philip Chodrow and Andrew Mellor.
\newblock Annotated hypergraphs: Models and applications.
\newblock \emph{Appl. Netw. Sci.}, 5\penalty0 (1):\penalty0 9, 2020.

\bibitem[Estrada and {Rodr{\'i}guez-Vel{\'a}zquez}(2005)]{estrada2005complex}
Ernesto Estrada and Juan~A {Rodr{\'i}guez-Vel{\'a}zquez}.
\newblock Complex networks as hypergraphs.
\newblock \emph{arXiv:physics/0505137}, 2005.

\bibitem[Kami{\'n}ski et~al.(2019)Kami{\'n}ski, Poulin, Pra{\l}at, Szufel, and
Theberge]{kaminski2019clustering}
Bogumi{\l} Kami{\'n}ski, Val{\'e}rie Poulin, Pawe{\l} Pra{\l}at, Przemys{\l}aw
Szufel, and Francois Theberge.
\newblock Clustering via hypergraph modularity.
\newblock \emph{PLOS ONE}, 14\penalty0 (11), 2019.

\bibitem[Zhou et~al.(2007{\natexlab{b}})Zhou, Huang, and
Sch{\"o}lkopf]{zhou2007learning}
Dengyong Zhou, Jiayuan Huang, and Bernhard Sch{\"o}lkopf.
\newblock Learning with hypergraphs: {{Clustering}}, classification, and
embedding.
\newblock In \emph{Advances in Neural Information Processing Systems}, pages
1601--1608, 2007{\natexlab{b}}.

\bibitem[Chodrow(2019)]{chodrow2019configuration}
Philip~S Chodrow.
\newblock Configuration models of random hypergraphs and their applications.
\newblock \emph{arXiv:1902.09302}, 2019.

\bibitem[Rodriguez(2003)]{rodriguez2003laplacian}
Juan~Alberto Rodriguez.
\newblock On the {{Laplacian}} spectrum and walk-regular hypergraphs.
\newblock \emph{Linear Multilinear Algebra}, 51\penalty0 (3):\penalty0
285--297, 2003.

\bibitem[Bellaachia and {Al-Dhelaan}(2013)]{bellaachia2013random}
Abdelghani Bellaachia and Mohammed {Al-Dhelaan}.
\newblock Random walks in hypergraph.
\newblock In \emph{Proceedings of the 2013 International Conference on Applied
    Mathematics and Computational Methods, Venice Italy}, pages 187--194, 2013.

\bibitem[Avin et~al.(2010)Avin, Lando, and Lotker]{avin2010radio}
Chen Avin, Yuval Lando, and Zvi Lotker.
\newblock Radio cover time in hyper-graphs.
\newblock In \emph{Proceedings of the 6th International Workshop on Foundations
    of Mobile Computing}, pages 3--12. {ACM}, 2010.

\bibitem[Young et~al.(2017)Young, Petri, Vaccarino, and
Patania]{young2017construction}
Jean-Gabriel Young, Giovanni Petri, Francesco Vaccarino, and Alice Patania.
\newblock Construction of and efficient sampling from the simplicial
configuration model.
\newblock \emph{Phys. Rev. E}, 96\penalty0 (3):\penalty0 032312, 2017.

\bibitem[Goldberg(2002)]{goldberg2002combinatorial}
Timothy~E Goldberg.
\newblock Combinatorial {{Laplacians}} of simplicial complexes.
\newblock \emph{Sr. Thesis Bard Coll.}, 2002.

\bibitem[Maleti{\'c} et~al.(2008)Maleti{\'c}, Rajkovi{\'c}, and
Vasiljevi{\'c}]{maletic2008simplicial}
Slobodan Maleti{\'c}, Milan Rajkovi{\'c}, and Danijela Vasiljevi{\'c}.
\newblock Simplicial complexes of networks and their statistical properties.
\newblock In \emph{International Conference on Computational Science}, pages
568--575. {Springer}, 2008.

\bibitem[Duval and Reiner(2002)]{duval2002shifted}
Art Duval and Victor Reiner.
\newblock Shifted simplicial complexes are {{Laplacian}} integral.
\newblock \emph{Trans. Am. Math. Soc.}, 354\penalty0 (11):\penalty0 4313--4344,
2002.

\bibitem[Serrano and G{\'o}mez(2019{\natexlab{a}})]{serrano2019higher}
Daniel~Hern{\'a}ndez Serrano and Dar{\'i}o~S{\'a}nchez G{\'o}mez.
\newblock Higher order degree in simplicial complexes, multi combinatorial
{{Laplacian}} and applications of {{TDA}} to complex networks.
\newblock \emph{arXiv:1908.02583}, 2019{\natexlab{a}}.

\bibitem[Estrada and Ross(2018)]{estrada2018centralities}
Ernesto Estrada and Grant~J Ross.
\newblock Centralities in simplicial complexes. applications to protein
interaction networks.
\newblock \emph{J. Theor. Biol.}, 438:\penalty0 46--60, 2018.

\bibitem[Courtney and Bianconi(2016)]{courtney2016generalized}
Owen~T. Courtney and Ginestra Bianconi.
\newblock Generalized network structures: {{The}} configuration model and the
canonical ensemble of simplicial complexes.
\newblock \emph{Phys. Rev. E}, 93\penalty0 (6):\penalty0 062311, 2016.

\bibitem[Patania et~al.(2017{\natexlab{b}})Patania, Petri, and
Vaccarino]{patania2017shape}
Alice Patania, Giovanni Petri, and Francesco Vaccarino.
\newblock The shape of collaborations.
\newblock \emph{EPJ Data Sci.}, 6\penalty0 (1):\penalty0 18,
2017{\natexlab{b}}.

\bibitem[Kapoor et~al.(2013)Kapoor, Sharma, and Srivastava]{kapoor2013weighted}
Komal Kapoor, Dhruv Sharma, and Jaideep Srivastava.
\newblock Weighted node degree centrality for hypergraphs.
\newblock In \emph{2013 {{IEEE}} 2nd Network Science Workshop ({{NSW}})}, pages
152--155. {IEEE}, 2013.

\bibitem[Jiang and Omer(2007)]{jiang2007spatial}
Bin Jiang and Itzhak Omer.
\newblock Spatial topology and its structural analysis based on the concept of
simplicial complex.
\newblock \emph{Trans. GIS}, 11\penalty0 (6):\penalty0 943--960, 2007.

\bibitem[Serrano and G{\'o}mez(2019{\natexlab{b}})]{serrano2019centrality}
Daniel~Hern{\'a}ndez Serrano and Dar{\'i}o~S{\'a}nchez G{\'o}mez.
\newblock Centrality measures in simplicial complexes: Applications of {{TDA}}
to {{Network Science}}.
\newblock \emph{arXiv:1908.02967}, 2019{\natexlab{b}}.

\bibitem[Lu and Peng(2011)]{lu2011high}
Linyuan Lu and Xing Peng.
\newblock High-ordered random walks and generalized {{Laplacians}} on
hypergraphs.
\newblock In \emph{International Workshop on Algorithms and Models for the
    Web-Graph}, pages 14--25. {Springer}, 2011.

\bibitem[Estrada and {Rodr{\'i}guez-Vel{\'a}zquez}(2006)]{estrada2006subgraph}
Ernesto Estrada and Juan~A {Rodr{\'i}guez-Vel{\'a}zquez}.
\newblock Subgraph centrality and clustering in complex hyper-networks.
\newblock \emph{Phys. A}, 364:\penalty0 581--594, 2006.

\bibitem[Aksoy et~al.(2019)Aksoy, Joslyn, Marrero, Praggastis, and
Purvine]{aksoy2019hypernetwork}
Sinan~G Aksoy, Cliff Joslyn, Carlos~Ortiz Marrero, Brenda Praggastis, and
Emilie Purvine.
\newblock Hypernetwork science via high-order hypergraph walks.
\newblock \emph{arXiv:1906.11295}, 2019.

\bibitem[Bonacich(1972)]{bonacich1972factoring}
Phillip Bonacich.
\newblock Factoring and weighting approaches to status scores and clique
identification.
\newblock \emph{J. Math. Sociol.}, 2\penalty0 (1):\penalty0 113--120, 1972.

\bibitem[Newman(2006)]{newman2006modularity}
M.~E.~J Newman.
\newblock Modularity and community structure in networks.
\newblock \emph{Proc. Natl. Acad. Sci.}, 103\penalty0 (23):\penalty0
8577--8582, 2006.

\bibitem[Langville and Meyer(2004)]{langville2004deeper}
Amy~N Langville and Carl~D Meyer.
\newblock Deeper inside pagerank.
\newblock \emph{Internet Math.}, 1\penalty0 (3):\penalty0 335--380, 2004.

\bibitem[Fletcher and Wennekers(2018)]{fletcher2018structure}
Jack~McKay Fletcher and Thomas Wennekers.
\newblock From structure to activity: Using centrality measures to predict
neuronal activity.
\newblock \emph{Int. J. Neural Syst.}, 28\penalty0 (02):\penalty0 1750013,
2018.

\bibitem[Bonacich(1991)]{bonacich1991simultaneous}
Phillip Bonacich.
\newblock Simultaneous group and individual centralities.
\newblock \emph{Soc. Netw.}, 13\penalty0 (2):\penalty0 155--168, 1991.

\bibitem[Bonacich et~al.(2004)Bonacich, Holdren, and
Johnston]{bonacich2004hyper}
Phillip Bonacich, Annie~Cody Holdren, and Michael Johnston.
\newblock Hyper-edges and multidimensional centrality.
\newblock \emph{Soc Netw}, 26\penalty0 (3):\penalty0 189--203, 2004.

\bibitem[Benson(2019)]{benson2019three}
Austin~R Benson.
\newblock Three hypergraph eigenvector centralities.
\newblock \emph{SIAM J. Math. Data Sci.}, 1\penalty0 (2):\penalty0 293--312,
2019.

\bibitem[Qi and Luo(2017)]{qi2017tensor}
Liqun Qi and Ziyan Luo.
\newblock \emph{Tensor Analysis: Spectral Theory and Special Tensors}, volume
151.
\newblock {Siam}, 2017.

\bibitem[Granovetter(1977)]{granovetter1977strength}
Mark~S Granovetter.
\newblock The strength of weak ties.
\newblock In \emph{Social Networks}, pages 347--367. {Elsevier}, 1977.

\bibitem[Opsahl(2013)]{opsahl2013triadic}
Tore Opsahl.
\newblock Triadic closure in two-mode networks: {{Redefining}} the global and
local clustering coefficients.
\newblock \emph{Soc. Netw.}, 35\penalty0 (2):\penalty0 159--167, 2013.

\bibitem[Borgatti and Everett(1997)]{borgatti1997network}
Stephen~P Borgatti and Martin~G Everett.
\newblock Network analysis of 2-mode data.
\newblock \emph{Soc. Netw.}, 19\penalty0 (3):\penalty0 243--269, 1997.

\bibitem[{Kartun-Giles} and Bianconi(2019)]{kartun2019beyond}
Alexander~P {Kartun-Giles} and Ginestra Bianconi.
\newblock Beyond the clustering coefficient: {{A}} topological analysis of node
neighbourhoods in complex networks.
\newblock \emph{Chaos Solitons Fractals X}, 1:\penalty0 100004, 2019.

\bibitem[Yin et~al.(2017)Yin, Benson, Leskovec, and Gleich]{yin2017local}
Hao Yin, Austin~R Benson, Jure Leskovec, and David~F Gleich.
\newblock Local higher-order graph clustering.
\newblock In \emph{Proceedings of the 23rd {{ACM SIGKDD}} International
    Conference on Knowledge Discovery and Data Mining}, pages 555--564. {ACM},
2017.

\bibitem[Benson et~al.(2018)Benson, Abebe, Schaub, Jadbabaie, and
Kleinberg]{benson2018simplicial}
Austin~R Benson, Rediet Abebe, Michael~T Schaub, Ali Jadbabaie, and Jon
Kleinberg.
\newblock Simplicial closure and higher-order link prediction.
\newblock \emph{Proc Natl Acad Sci USA}, 115\penalty0 (48):\penalty0
E11221--E11230, 2018.

\bibitem[Edelsbrunner(2014)]{edelsbrunner2014short}
H.~Edelsbrunner.
\newblock \emph{A Short Course in Computational Geometry and Topology}.
\newblock {{SpringerBriefs}} in Applied Sciences and Technology. {Springer
    International Publishing}, 2014.
\newblock ISBN 978-3-319-05957-0.

\bibitem[Ghrist(2008)]{ghrist2008barcodes}
Robert Ghrist.
\newblock Barcodes: The persistent topology of data.
\newblock \emph{Bull. Am. Math. Soc.}, 45\penalty0 (1):\penalty0 61--75, 2008.

\bibitem[Verri et~al.(1993)Verri, Uras, Frosini, and Ferri]{verri1993use}
Alessandro Verri, Claudio Uras, Patrizio Frosini, and Massimo Ferri.
\newblock On the use of size functions for shape analysis.
\newblock \emph{Biol. Cybern.}, 70\penalty0 (2):\penalty0 99--107, 1993.

\bibitem[Cagliari et~al.(2001)Cagliari, Ferri, and Pozzi]{cagliari2001size}
Francesca Cagliari, Massimo Ferri, and Paola Pozzi.
\newblock Size functions from a categorical viewpoint.
\newblock \emph{Acta Appl. Math.}, 67\penalty0 (3):\penalty0 225--235, 2001.

\bibitem[Edelsbrunner et~al.(2000)Edelsbrunner, Letscher, and
Zomorodian]{edelsbrunner2000topological}
Herbert Edelsbrunner, David Letscher, and Afra Zomorodian.
\newblock Topological persistence and simplification.
\newblock In \emph{Proceedings 41st Annual Symposium on Foundations of Computer
    Science}, pages 454--463. {IEEE}, 2000.

\bibitem[Zomorodian and Carlsson(2005)]{zomorodian2005computing}
Afra Zomorodian and Gunnar Carlsson.
\newblock Computing persistent homology.
\newblock \emph{Discrete Comput. Geom.}, 33\penalty0 (2):\penalty0 249--274,
2005.

\bibitem[Feng and Porter(2019)]{feng2019persistent}
Michelle Feng and Mason~A Porter.
\newblock Persistent homology of geospatial data: {{A}} case study with voting.
\newblock \emph{arXiv:1902.05911}, 2019.

\bibitem[Carlsson and De~Silva(2010)]{carlsson2010zigzag}
Gunnar Carlsson and Vin De~Silva.
\newblock Zigzag persistence.
\newblock \emph{Found. Comput. Math.}, 10\penalty0 (4):\penalty0 367--405,
2010.

\bibitem[Carlsson and Zomorodian(2009)]{carlsson2009theory}
Gunnar Carlsson and Afra Zomorodian.
\newblock The theory of multidimensional persistence.
\newblock \emph{Discrete Comput. Geom.}, 42\penalty0 (1):\penalty0 71--93,
2009.

\bibitem[Edelsbrunner and Morozov(2017)]{edelsbrunner2017persistent}
Herbert Edelsbrunner and Dmitriy Morozov.
\newblock Persistent homology.
\newblock In \emph{Handbook of Discrete and Computational Geometry}, pages
637--661. {Chapman and Hall/CRC}, 2017.

\bibitem[Otter et~al.(2017)Otter, Porter, Tillmann, Grindrod, and
Harrington]{otter2017roadmap}
Nina Otter, Mason~A Porter, Ulrike Tillmann, Peter Grindrod, and Heather~A
Harrington.
\newblock A roadmap for the computation of persistent homology.
\newblock \emph{EPJ Data Sci.}, 6\penalty0 (1):\penalty0 17, 2017.

\bibitem[Muldoon et~al.(1993)Muldoon, MacKay, Huke, and
Broomhead]{muldoon1993topology}
MR~Muldoon, RS~MacKay, JP~Huke, and DS~Broomhead.
\newblock Topology from time series.
\newblock \emph{Phys. D}, 65\penalty0 (1-2):\penalty0 1--16, 1993.

\bibitem[Adler et~al.(2017)Adler, Bartz, Kou, and Monod]{adler2017estimating}
Robert~J Adler, Kevin Bartz, Sam~C Kou, and Anthea Monod.
\newblock Estimating thresholding levels for random fields via {{Euler}}
characteristics.
\newblock \emph{arXiv:1704.08562}, 2017.

\bibitem[Pranav et~al.(2019)Pranav, {Van de Weygaert}, Vegter, Jones, Adler,
Feldbrugge, Park, Buchert, and Kerber]{pranav2019topology}
Pratyush Pranav, Rien {Van de Weygaert}, Gert Vegter, Bernard~JT Jones,
Robert~J Adler, Job Feldbrugge, Changbom Park, Thomas Buchert, and Michael
Kerber.
\newblock Topology and geometry of {{Gaussian}} random fields {{I}}: On
{{Betti}} numbers, {{Euler}} characteristic, and {{Minkowski}} functionals.
\newblock \emph{Mon. Not. R. Astron. Soc.}, 485\penalty0 (3):\penalty0
4167--4208, 2019.

\bibitem[Maleti{\'c} and Rajkovi{\'c}(2012)]{maletic2012combinatorial}
Slobodan Maleti{\'c} and Milan Rajkovi{\'c}.
\newblock Combinatorial {{Laplacian}} and entropy of simplicial complexes
associated with complex networks.
\newblock \emph{Eur Phys J ST}, \penalty0 (1):\penalty0 77--97, 2012.

\bibitem[Lim(2015)]{lim2015hodge}
Lek-Heng Lim.
\newblock Hodge {Laplacians} on graphs.
\newblock \emph{Proc. Symp. Appl. Math.}, 2015.

\bibitem[Parzanchevski and Rosenthal(2017)]{parzanchevski2017simplicial}
Ori Parzanchevski and Ron Rosenthal.
\newblock Simplicial complexes: Spectrum, homology and random walks.
\newblock \emph{Random Struc Algorithms}, 50\penalty0 (2):\penalty0 225--261,
2017.

\bibitem[Schaub et~al.(2020)Schaub, Benson, Horn, Lippner, and
Jadbabaie]{schaub2020random}
Michael~T Schaub, Austin~R Benson, Paul Horn, Gabor Lippner, and Ali Jadbabaie.
\newblock Random walks on simplicial complexes and the normalized {Hodge}
{Laplacian}.
\newblock \emph{SIAM Rev.}, 62\penalty0 (2):\penalty0 353--391, 2020.

\bibitem[Rodriguez(2009)]{rodriguez2009laplacian}
JA~Rodriguez.
\newblock Laplacian eigenvalues and partition problems in hypergraphs.
\newblock \emph{Appl. Math. Lett.}, 22\penalty0 (6):\penalty0 916--921, 2009.

\bibitem[Chung(1993)]{chung1993laplacian}
Fan Chung.
\newblock The {Laplacian} of a hypergraph.
\newblock \emph{Expand. Graphs DIMACS Ser.}, pages 21--36, 1993.

\bibitem[Saito et~al.(2018)Saito, Mandic, and Suzuki]{saito2018hypergraph}
Shota Saito, Danilo~P Mandic, and Hideyuki Suzuki.
\newblock Hypergraph p-{{Laplacian}}: {{A}} differential geometry view.
\newblock In \emph{Thirty-Second {{AAAI}} Conference on Artificial
    Intelligence}, 2018.

\bibitem[Cooper and Dutle(2012)]{cooper2012spectra}
Joshua Cooper and Aaron Dutle.
\newblock Spectra of uniform hypergraphs.
\newblock \emph{Linear Algebra Its Appl.}, 436\penalty0 (9):\penalty0
3268--3292, 2012.

\bibitem[Hu and Qi(2015)]{hu2015laplacian}
Shenglong Hu and Liqun Qi.
\newblock The {Laplacian} of a uniform hypergraph.
\newblock \emph{J. Comb. Optim.}, 29\penalty0 (2):\penalty0 331--366, 2015.

\bibitem[Li and Milenkovic(2018)]{li2018submodular}
Pan Li and Olgica Milenkovic.
\newblock Submodular hypergraphs: {P}-{Laplacians}, {Cheeger} inequalities and
spectral clustering.
\newblock In \emph{Proceedings of the 35th International Conference on Machine
    Learning}, pages 3014--3023, 2018.

\bibitem[Lucas et~al.(2020)Lucas, Cencetti, and Battiston]{lucas2020multiorder}
Maxime Lucas, Giulia Cencetti, and Federico Battiston.
\newblock A multi-order {Laplacian} for synchronization in higher-order
networks.
\newblock \emph{arXiv:2003.09734}, 2020.

\bibitem[Coolen et~al.(2017)Coolen, Annibale, and
Roberts]{coolen2017generating}
Anthony~CC Coolen, Alessia Annibale, and Ekaterina Roberts.
\newblock \emph{Generating Random Networks and Graphs}.
\newblock {Oxford university press}, 2017.

\bibitem[Krioukov and Ostilli(2013)]{krioukov2013duality}
Dmitri Krioukov and Massimo Ostilli.
\newblock Duality between equilibrium and growing networks.
\newblock \emph{Physical Review E}, 88\penalty0 (2):\penalty0 022808, 2013.

\bibitem[Bianconi and Capocci(2003)]{bianconi2003number}
Ginestra Bianconi and Andrea Capocci.
\newblock Number of loops of size h in growing scale-free networks.
\newblock \emph{Phys. Rev. Lett.}, 90\penalty0 (7):\penalty0 078701, 2003.

\bibitem[Bianconi and Marsili(2005)]{bianconi2005loops}
Ginestra Bianconi and Matteo Marsili.
\newblock Loops of any size and hamilton cycles in random scale-free networks.
\newblock \emph{Journal of Statistical Mechanics: Theory and Experiment},
2005\penalty0 (06):\penalty0 P06005, 2005.

\bibitem[Serrano and Bogun{\'a}(2005)]{serrano2005tuning}
M~Angeles Serrano and Mari{\'a}n Bogun{\'a}.
\newblock Tuning clustering in random networks with arbitrary degree
distributions.
\newblock \emph{Phys. Rev. E}, 72\penalty0 (3):\penalty0 036133, 2005.

\bibitem[Bollob{\'a}s and Erd{\"o}s(1976)]{bollobas1976cliques}
B{\'e}la Bollob{\'a}s and Paul Erd{\"o}s.
\newblock Cliques in random graphs.
\newblock In \emph{Mathematical Proceedings of the Cambridge Philosophical
    Society}, volume~80, pages 419--427. {Cambridge University Press}, 1976.

\bibitem[Bianconi and Marsili(2006)]{bianconi2006emergence}
Ginestra Bianconi and Matteo Marsili.
\newblock Emergence of large cliques in random scale-free networks.
\newblock \emph{EPL (Europhysics Letters)}, 74\penalty0 (4):\penalty0 740,
2006.

\bibitem[Fosdick et~al.(2018)Fosdick, Larremore, Nishimura, and
Ugander]{fosdick2018configuring}
Bailey~K Fosdick, Daniel~B Larremore, Joel Nishimura, and Johan Ugander.
\newblock Configuring random graph models with fixed degree sequences.
\newblock \emph{SIAM Rev.}, 60\penalty0 (2):\penalty0 315--355, 2018.

\bibitem[Diamond(1975)]{diamond1975assembly}
Jared~M Diamond.
\newblock Assembly of species communities.
\newblock \emph{Ecol. Evol. Communities}, pages 342--444, 1975.

\bibitem[Connor and Simberloff(1979)]{connor1979assembly}
Edward~F Connor and Daniel Simberloff.
\newblock The assembly of species communities: Chance or competition?
\newblock \emph{Ecology}, 60\penalty0 (6):\penalty0 1132--1140, 1979.

\bibitem[Gail and Mantel(1977)]{gail1977counting}
Mitchell Gail and Nathan Mantel.
\newblock Counting the number of r x c contingency tables with fixed
margins.
\newblock \emph{JASA}, 72\penalty0 (360a):\penalty0 859--862, 1977.

\bibitem[Verbeek and Kroonenberg(1985)]{verbeek1985survey}
Albert Verbeek and Pieter~M Kroonenberg.
\newblock A survey of algorithms for exact distributions of test statistics in
r x c contingency tables with fixed margins.
\newblock \emph{Comput. Stat. Data Anal.}, 3:\penalty0 159--185, 1985.

\bibitem[Saracco et~al.(2015)Saracco, Di~Clemente, Gabrielli, and
Squartini]{saracco2015randomizing}
Fabio Saracco, Riccardo Di~Clemente, Andrea Gabrielli, and Tiziano Squartini.
\newblock Randomizing bipartite networks: The case of the {{World Trade Web}}.
\newblock \emph{Sci. Rep.}, 5:\penalty0 10595, 2015.

\bibitem[Payrat{\'o}-Borr{\`a}s et~al.(2019)Payrat{\'o}-Borr{\`a}s,
Hern{\'a}ndez, and Moreno]{payrato2019breaking}
Cl{\`a}udia Payrat{\'o}-Borr{\`a}s, Laura Hern{\'a}ndez, and Yamir Moreno.
\newblock Breaking the spell of nestedness: The entropic origin of nestedness
in mutualistic systems.
\newblock \emph{Phys. Rev. X}, 9\penalty0 (3):\penalty0 031024, 2019.

\bibitem[Kitsak and Krioukov(2011)]{kitsak2011hidden}
Maksim Kitsak and Dmitri Krioukov.
\newblock Hidden variables in bipartite networks.
\newblock \emph{Phys. Rev. E}, 84\penalty0 (2):\penalty0 026114, 2011.

\bibitem[Boroojeni et~al.(2017)Boroojeni, Dewar, Wu, and
Hyman]{boroojeni2017generating}
Asma~Azizi Boroojeni, Jeremy Dewar, Tong Wu, and James~M Hyman.
\newblock Generating bipartite networks with a prescribed joint degree
distribution.
\newblock \emph{J. Complex Netw.}, 5\penalty0 (6):\penalty0 839--857, 2017.

\bibitem[S{\"o}derberg(2002)]{soderberg2002general}
Bo~S{\"o}derberg.
\newblock General formalism for inhomogeneous random graphs.
\newblock \emph{Phys. Rev. E}, 66\penalty0 (6):\penalty0 066121, 2002.

\bibitem[Allard et~al.(2009)Allard, No{\"e}l, Dub{\'e}, and
Pourbohloul]{allard2009heterogeneous}
Antoine Allard, Pierre-Andr{\'e} No{\"e}l, Louis~J Dub{\'e}, and Babak
Pourbohloul.
\newblock Heterogeneous bond percolation on multitype networks with an
application to epidemic dynamics.
\newblock \emph{Phys. Rev. E}, 79\penalty0 (3):\penalty0 036113, 2009.

\bibitem[Fu et~al.(2019)Fu, Yu, and Benson]{fu2019modeling}
Xiang Fu, Shangdi Yu, and Austin~R Benson.
\newblock Modeling and analysis of tagging networks in stack exchange
communities.
\newblock \emph{J. Complex Netw.}, 12 2019.
\newblock ISSN 2051-1329.

\bibitem[Wasserman and Pattison(1996)]{wasserman1996logit}
Stanley Wasserman and Philippa Pattison.
\newblock Logit models and logistic regressions for social networks: {{I}}.
{{An}} introduction to {{Markov}} graphs andp.
\newblock \emph{Psychometrika}, 61\penalty0 (3):\penalty0 401--425, 1996.

\bibitem[Snijders et~al.(2006)Snijders, Pattison, Robins, and
Handcock]{snijders2006new}
Tom~AB Snijders, Philippa~E Pattison, Garry~L Robins, and Mark~S Handcock.
\newblock New specifications for exponential random graph models.
\newblock \emph{Sociol. Methodol.}, 36\penalty0 (1):\penalty0 99--153, 2006.

\bibitem[Frank and Strauss(1986)]{frank1986markov}
Ove Frank and David Strauss.
\newblock Markov graphs.
\newblock \emph{J. Am. Stat. Assoc.}, 81\penalty0 (395):\penalty0 832--842,
1986.

\bibitem[Holland and Leinhardt(1981)]{holland1981exponential}
Paul~W Holland and Samuel Leinhardt.
\newblock An exponential family of probability distributions for directed
graphs.
\newblock \emph{J. Am. Stat. Assoc.}, 76\penalty0 (373):\penalty0 33--50, 1981.

\bibitem[Latapy et~al.(2008)Latapy, Magnien, and Del~Vecchio]{latapy2008basic}
Matthieu Latapy, Cl{\'e}mence Magnien, and Nathalie Del~Vecchio.
\newblock Basic notions for the analysis of large two-mode networks.
\newblock \emph{Soc Netw.}, 30\penalty0 (1):\penalty0 31--48, 2008.

\bibitem[Iacobucci and Wasserman(1990)]{iacobucci1990social}
Dawn Iacobucci and Stanley Wasserman.
\newblock Social networks with two sets of actors.
\newblock \emph{Psychometrika}, 55\penalty0 (4):\penalty0 707--720, 1990.

\bibitem[Skvoretz and Faust(1999)]{skvoretz1999logit}
John Skvoretz and Katherine Faust.
\newblock Logit models for affiliation networks.
\newblock \emph{Sociolo Methodol}, 29\penalty0 (1):\penalty0 253--280, 1999.

\bibitem[Robins and Alexander(2004)]{robins2004small}
Garry Robins and Malcolm Alexander.
\newblock Small worlds among interlocking directors: {{Network}} structure and
distance in bipartite graphs.
\newblock \emph{Comput. Math. Organ. Theory}, 10\penalty0 (1):\penalty0 69--94,
2004.

\bibitem[Agneessens et~al.(2004)Agneessens, Roose, and
Waege]{agneessens2004choices}
Filip Agneessens, Henk Roose, and Hans Waege.
\newblock Choices of theatre events: P* models for affiliation networks with
attributes.
\newblock \emph{Metod Zv}, 1\penalty0 (2):\penalty0 419, 2004.

\bibitem[Strauss(1986)]{strauss1986general}
David Strauss.
\newblock On a general class of models for interaction.
\newblock \emph{SIAM Rev.}, 28\penalty0 (4):\penalty0 513--527, 1986.

\bibitem[Handcock(2003)]{handcock2003statistical}
Mark~S Handcock.
\newblock Statistical models for social networks: {{Inference}} and degeneracy.
\newblock In R.~Breiger, K.~Carley, and P.~Pattison, editors, \emph{Dynamic
    Social Network Modeling and Analysis.}, pages 229--240. {National Academies
    Press, (Washington, DC)}, 2003.

\bibitem[Fischer et~al.(2015)Fischer, Leit{\~a}o, Peixoto, and
Altmann]{fischer2015sampling}
Rico Fischer, Jorge~C Leit{\~a}o, Tiago~P Peixoto, and Eduardo~G Altmann.
\newblock Sampling motif-constrained ensembles of networks.
\newblock \emph{Phys. Rev. Lett.}, 115\penalty0 (18):\penalty0 188701, 2015.

\bibitem[Wang et~al.(2009)Wang, Sharpe, Robins, and
Pattison]{wang2009exponential}
Peng Wang, Ken Sharpe, Garry~L Robins, and Philippa~E Pattison.
\newblock Exponential random graph (p*) models for affiliation networks.
\newblock \emph{Soc. Networks}, 31\penalty0 (1):\penalty0 12--25, 2009.

\bibitem[Wang et~al.(2013{\natexlab{a}})Wang, Pattison, and
Robins]{wang2013exponential}
Peng Wang, Philippa Pattison, and Garry Robins.
\newblock Exponential random graph model specifications for bipartite
networks A dependence hierarchy.
\newblock \emph{Soc. Networks}, 35\penalty0 (2):\penalty0 211--222,
2013{\natexlab{a}}.

\bibitem[Robins et~al.(2007)Robins, Pattison, Kalish, and
Lusher]{robins2007introduction}
Garry Robins, Pip Pattison, Yuval Kalish, and Dean Lusher.
\newblock An introduction to exponential random graph (p*) models for social
networks.
\newblock \emph{Soc Netw}, 29\penalty0 (2):\penalty0 173--191, 2007.

\bibitem[Smith(2012)]{smith2012macrostructure}
Jeffrey~A Smith.
\newblock Macrostructure from microstructure: {{Generating}} whole systems from
ego networks.
\newblock \emph{Sociol. Methodol.}, 42\penalty0 (1):\penalty0 155--205, 2012.

\bibitem[Jasny(2012)]{jasny2012baseline}
Lorien Jasny.
\newblock Baseline models for two-mode social network data.
\newblock \emph{Policy Stud. J.}, 40\penalty0 (3):\penalty0 458--491, 2012.

\bibitem[Faust et~al.(2002)Faust, Willert, Rowlee, and
Skvoretz]{faust2002scaling}
Katherine Faust, Karin~E Willert, David~D Rowlee, and John Skvoretz.
\newblock Scaling and statistical models for affiliation networks: Patterns of
participation among {{Soviet}} politicians during the {{Brezhnev}} era.
\newblock \emph{Soc Netw.}, 24\penalty0 (3):\penalty0 231--259, 2002.

\bibitem[Snijders(2002)]{snijders2002markov}
Tom~AB Snijders.
\newblock {Markov} chain {{Monte Carlo}} estimation of exponential random graph
models.
\newblock \emph{J Soc Struct}, 3\penalty0 (2):\penalty0 1--40, 2002.

\bibitem[Shalizi and Rinaldo(2013)]{shalizi2013consistency}
Cosma~Rohilla Shalizi and Alessandro Rinaldo.
\newblock Consistency under sampling of exponential random graph models.
\newblock \emph{Ann. Stat.}, 41\penalty0 (2):\penalty0 508, 2013.

\bibitem[Crane(2018)]{crane2018probabilistic}
Harry Crane.
\newblock \emph{Probabilistic Foundations of Statistical Network Analysis}.
\newblock {Chapman and Hall/CRC}, 2018.

\bibitem[Young et~al.(2018)Young, {St-Onge}, Desrosiers, and
Dub{\'e}]{young2018universality}
Jean-Gabriel Young, Guillaume {St-Onge}, Patrick Desrosiers, and Louis~J
Dub{\'e}.
\newblock Universality of the stochastic block model.
\newblock \emph{Phys. Rev. E}, 98\penalty0 (3):\penalty0 032309, 2018.

\bibitem[Newman(2012)]{newman2012communities}
M.~E.~J Newman.
\newblock Communities, modules and large-scale structure in networks.
\newblock \emph{Nat. Phys.}, 8\penalty0 (1):\penalty0 25--31, 2012.

\bibitem[Newman(2003{\natexlab{b}})]{newman2003mixing}
M.~E.~J Newman.
\newblock Mixing patterns in networks.
\newblock \emph{Phys. Rev. E}, 67\penalty0 (2):\penalty0 026126,
2003{\natexlab{b}}.

\bibitem[Borgatti and Everett(2000)]{borgatti2000models}
Stephen~P Borgatti and Martin~G Everett.
\newblock Models of core/periphery structures.
\newblock \emph{Soc Netw}, 21\penalty0 (4):\penalty0 375--395, 2000.

\bibitem[Holland et~al.(1983)Holland, Laskey, and
Leinhardt]{holland1983stochastic}
Paul~W. Holland, Kathryn~Blackmond Laskey, and Samuel Leinhardt.
\newblock Stochastic blockmodels: {{First}} steps.
\newblock \emph{Soc. Networks}, 5\penalty0 (2):\penalty0 109--137, 1983.

\bibitem[Doreian et~al.(2004)Doreian, Batagelj, and
Ferligoj]{doreian2004generalized}
Patrick Doreian, Vladimir Batagelj, and Anu{\v s}ka Ferligoj.
\newblock Generalized blockmodeling of two-mode network data.
\newblock \emph{Soc. Networks}, 26\penalty0 (1):\penalty0 29--53, 2004.

\bibitem[Rohe et~al.(2016)Rohe, Qin, and Yu]{rohe2016co}
Karl Rohe, Tai Qin, and Bin Yu.
\newblock Co-clustering directed graphs to discover asymmetries and directional
communities.
\newblock \emph{Proc. Natl. Acad. Sci. U. S. A.}, 113\penalty0 (45):\penalty0
12679--12684, 2016.

\bibitem[Larremore et~al.(2014)Larremore, Clauset, and
Jacobs]{larremore2014efficiently}
Daniel~B Larremore, Aaron Clauset, and Abigail~Z Jacobs.
\newblock Efficiently inferring community structure in bipartite networks.
\newblock \emph{Phys. Rev. E}, 90\penalty0 (1):\penalty0 012805, 2014.

\bibitem[Olhede and Wolfe(2014)]{olhede2014network}
Sofia~C Olhede and Patrick~J Wolfe.
\newblock Network histograms and universality of blockmodel approximation.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A.}, 111\penalty0 (41):\penalty0
14722--14727, 2014.

\bibitem[Peixoto(2012)]{peixoto2012entropy}
Tiago~P Peixoto.
\newblock Entropy of stochastic blockmodel ensembles.
\newblock \emph{Phys. Rev. E}, 85\penalty0 (5):\penalty0 056122, 2012.

\bibitem[Guimer{\`a} et~al.(2012)Guimer{\`a}, Llorente, Moro, and
{Sales-Pardo}]{guimera2012predicting}
Roger Guimer{\`a}, Alejandro Llorente, Esteban Moro, and Marta {Sales-Pardo}.
\newblock Predicting human preferences using the block structure of complex
social networks.
\newblock \emph{PLOS ONE}, 7\penalty0 (9):\penalty0 e44620, 2012.

\bibitem[Ball et~al.(2011)Ball, Karrer, and Newman]{ball2011efficient}
Brian Ball, Brian Karrer, and M.~E.~J Newman.
\newblock Efficient and principled method for detecting communities in
networks.
\newblock \emph{Phys. Rev. E}, 84\penalty0 (3):\penalty0 036103, 2011.

\bibitem[Hric et~al.(2016)Hric, Peixoto, and Fortunato]{hric2016network}
Darko Hric, Tiago~P Peixoto, and Santo Fortunato.
\newblock Network structure, metadata, and the prediction of missing nodes and
annotations.
\newblock \emph{Phys. Rev. X}, 6\penalty0 (3):\penalty0 031038, 2016.

\bibitem[Gerlach et~al.(2018)Gerlach, Peixoto, and Altmann]{gerlach2018network}
Martin Gerlach, Tiago~P Peixoto, and Eduardo~G Altmann.
\newblock A network approach to topic models.
\newblock \emph{Sci. Adv.}, 4\penalty0 (7):\penalty0 eaaq1360, 2018.

\bibitem[Blei et~al.(2003)Blei, Ng, and Jordan]{blei2003latent}
David~M Blei, Andrew~Y Ng, and Michael~I Jordan.
\newblock Latent dirichlet allocation.
\newblock \emph{J. Mach. Learn. Res.}, 3\penalty0 (Jan):\penalty0 993--1022,
2003.

\bibitem[Sheng et~al.(2003)Sheng, Moreau, and De~Moor]{sheng2003biclustering}
Qizheng Sheng, Yves Moreau, and Bart De~Moor.
\newblock Biclustering microarray data by {{Gibbs}} sampling.
\newblock \emph{Bioinformatics}, 19\penalty0 (suppl\_2):\penalty0 ii196--ii205,
2003.

\bibitem[Iyer and Yogeshwaran(2012)]{iyer2012percolation}
Srikanth~K Iyer and Dahandapani Yogeshwaran.
\newblock Percolation and connectivity in {{AB}} random geometric graphs.
\newblock \emph{Adv. Appl. Probab.}, 44\penalty0 (1):\penalty0 21--41, 2012.

\bibitem[Penrose et~al.(2003)]{penrose2003random}
Mathew Penrose et~al.
\newblock \emph{Random Geometric Graphs}, volume~5.
\newblock {Oxford university press}, 2003.

\bibitem[Waxman(1988)]{waxman1988routing}
Bernard~M Waxman.
\newblock Routing of multipoint connections.
\newblock \emph{IEEE J. Sel. Areas Commun.}, 6\penalty0 (9):\penalty0
1617--1622, 1988.

\bibitem[Serrano et~al.(2008)Serrano, Krioukov, and
Bogun{\'a}]{serrano2008self}
M~Angeles Serrano, Dmitri Krioukov, and Mari{\'a}n Bogun{\'a}.
\newblock Self-similarity of complex networks and hidden metric spaces.
\newblock \emph{Phys. Rev. Lett.}, 100\penalty0 (7):\penalty0 078701, 2008.

\bibitem[Kitsak et~al.(2017)Kitsak, Papadopoulos, and
Krioukov]{kitsak2017latent}
Maksim Kitsak, Fragkiskos Papadopoulos, and Dmitri Krioukov.
\newblock Latent geometry of bipartite networks.
\newblock \emph{Phys. Rev. E}, 95\penalty0 (3):\penalty0 032309, 2017.

\bibitem[Serrano et~al.(2012)Serrano, Bogun{\'a}, and
Sagu{\'e}s]{serrano2012uncovering}
M~{\'A}ngeles Serrano, Mari{\'a}n Bogun{\'a}, and Francesc Sagu{\'e}s.
\newblock Uncovering the hidden geometry behind metabolic networks.
\newblock \emph{Mol. Biosyst.}, 8\penalty0 (3):\penalty0 843--850, 2012.

\bibitem[Krioukov(2016)]{krioukov2016clustering}
Dmitri Krioukov.
\newblock Clustering implies geometry in networks.
\newblock \emph{Phys. Rev. Lett.}, 116\penalty0 (20):\penalty0 208302, 2016.

\bibitem[Newman(2003{\natexlab{c}})]{newman2003properties}
Mark E.~J. Newman.
\newblock Properties of highly clustered networks.
\newblock \emph{Phys. Rev. E}, 68\penalty0 (2):\penalty0 026121,
2003{\natexlab{c}}.

\bibitem[Davis and Leinhardt(1967)]{davis1967structure}
James~A Davis and Samuel Leinhardt.
\newblock The structure of positive interpersonal relations in small groups.
\newblock 1967.

\bibitem[Holland and Leinhardt(1976)]{holland1976local}
Paul~W Holland and Samuel Leinhardt.
\newblock Local structure in social networks.
\newblock \emph{Sociol. Methodol.}, 7:\penalty0 1--45, 1976.

\bibitem[Gleeson and Melnik(2009)]{gleeson2009analytical}
James~P Gleeson and Sergey Melnik.
\newblock Analytical results for bond percolation and k-core sizes on clustered
networks.
\newblock \emph{Phys. Rev. E}, 80\penalty0 (4):\penalty0 046121, 2009.

\bibitem[Trapman(2007)]{trapman2007analytical}
Pieter Trapman.
\newblock On analytical approaches to epidemics on networks.
\newblock \emph{Theor. Popul. Biol.}, 71\penalty0 (2):\penalty0 160--173, 2007.

\bibitem[Newman(2009)]{newman2009random}
M.~E.~J Newman.
\newblock Random graphs with clustering.
\newblock \emph{Phys. Rev. Lett.}, 103\penalty0 (5):\penalty0 058701, 2009.

\bibitem[Miller(2009{\natexlab{a}})]{miller2009percolation}
Joel~C Miller.
\newblock Percolation and epidemics in random clustered networks.
\newblock \emph{Phys. Rev. E}, 80\penalty0 (2):\penalty0 020901,
2009{\natexlab{a}}.

\bibitem[Gleeson(2009)]{gleeson2009bond}
James~P Gleeson.
\newblock Bond percolation on a class of clustered random networks.
\newblock \emph{Phys. Rev. E}, 80\penalty0 (3):\penalty0 036107, 2009.

\bibitem[Karrer and Newman(2010)]{karrer2010random}
Brian Karrer and M.~E.~J Newman.
\newblock Random graphs containing arbitrary distributions of subgraphs.
\newblock \emph{Phys. Rev. E}, 82\penalty0 (6):\penalty0 066118, 2010.

\bibitem[Allard et~al.(2012)Allard, {H{\'e}bert-Dufresne}, No{\"e}l, Marceau,
and Dub{\'e}]{allard2012bond}
Antoine Allard, Laurent {H{\'e}bert-Dufresne}, Pierre-Andr{\'e} No{\"e}l,
Vincent Marceau, and Louis~J Dub{\'e}.
\newblock Bond percolation on a class of correlated and clustered random
graphs.
\newblock \emph{J. Phys. Math. Theor.}, 45\penalty0 (40):\penalty0 405005,
2012.

\bibitem[Allard et~al.(2015)Allard, {H{\'e}bert-Dufresne}, Young, and
Dub{\'e}]{allard2015general}
Antoine Allard, Laurent {H{\'e}bert-Dufresne}, Jean-Gabriel Young, and Louis~J
Dub{\'e}.
\newblock General and exact approach to percolation on random graphs.
\newblock \emph{Phys. Rev. E}, 92\penalty0 (6):\penalty0 062807, 2015.

\bibitem[Wegner(2014)]{wegner2014subgraph}
Anatol~E Wegner.
\newblock Subgraph covers: An information-theoretic approach to motif analysis
in networks.
\newblock \emph{Phys. Rev. X}, 4\penalty0 (4):\penalty0 041026, 2014.

\bibitem[Bollob{\'a}s et~al.(2011)Bollob{\'a}s, Janson, and
Riordan]{bollobas2011sparse}
B{\'e}la Bollob{\'a}s, Svante Janson, and Oliver Riordan.
\newblock Sparse random graphs with clustering.
\newblock \emph{Random Struct Algorithms}, 38\penalty0 (3):\penalty0 269--323,
2011.

\bibitem[Newman and Peixoto(2015)]{newman2015generalized}
M.~E.~J Newman and Tiago~P Peixoto.
\newblock Generalized communities in networks.
\newblock \emph{Phys. Rev. Lett.}, 115\penalty0 (8):\penalty0 088701, 2015.

\bibitem[Devanny et~al.(2016)Devanny, Eppstein, and
Tillman]{devanny2016computational}
William Devanny, David Eppstein, and B{\'a}lint Tillman.
\newblock The computational hardness of dk-series.
\newblock In \emph{{{NetSci}} 2016}, 2016.

\bibitem[Pattison and Robins(2002)]{pattison2002}
Philippa Pattison and Garry Robins.
\newblock Neighborhood-based models for social networks.
\newblock \emph{Sociol. Methodol.}, 32\penalty0 (1):\penalty0 301--337, 2002.

\bibitem[Watts et~al.(2002)Watts, Dodds, and Newman]{watts2002identity}
Duncan~J Watts, Peter~Sheridan Dodds, and M.~E.~J Newman.
\newblock Identity and search in social networks.
\newblock \emph{Science}, 296\penalty0 (5571):\penalty0 1302--1305, 2002.

\bibitem[Yang and Leskovec(2012)]{yang2012community}
Jaewon Yang and Jure Leskovec.
\newblock Community-affiliation graph model for overlapping network community
detection.
\newblock In \emph{2012 {{IEEE}} 12th International Conference on Data Mining},
pages 1170--1175. {IEEE}, 2012.

\bibitem[{H{\'e}bert-Dufresne} et~al.(2010){H{\'e}bert-Dufresne}, No{\"e}l,
Marceau, Allard, and Dub{\'e}]{hebert2010propagation}
Laurent {H{\'e}bert-Dufresne}, Pierre-Andr{\'e} No{\"e}l, Vincent Marceau,
Antoine Allard, and Louis~J Dub{\'e}.
\newblock Propagation dynamics on networks featuring complex topologies.
\newblock \emph{Phys. Rev. E}, 82\penalty0 (3):\penalty0 036115, 2010.

\bibitem[Seshadhri et~al.(2012)Seshadhri, Kolda, and
Pinar]{seshadhri2012community}
Comandur Seshadhri, Tamara~G Kolda, and Ali Pinar.
\newblock Community structure and scale-free collections of {{Erd{\H
            o}s}}-{{R{\'e}nyi}} graphs.
\newblock \emph{Phys. Rev. E}, 85\penalty0 (5):\penalty0 056109, 2012.

\bibitem[Karo{\'n}ski et~al.(1999)Karo{\'n}ski, Scheinerman, and
{Singer-Cohen}]{karonski1999random}
Micha{\l} Karo{\'n}ski, Edward~R Scheinerman, and Karen~B {Singer-Cohen}.
\newblock On random intersection graphs: {{The}} subgraph problem.
\newblock \emph{Comb Probab Comput}, 8\penalty0 (1-2):\penalty0 131--159, 1999.

\bibitem[Erd{\"o}s et~al.(1966)Erd{\"o}s, Goodman, and
P{\'o}sa]{erdos1966representation}
Paul Erd{\"o}s, Adolph~W Goodman, and Louis P{\'o}sa.
\newblock The representation of a graph by set intersections.
\newblock \emph{Can. J. Math.}, 18:\penalty0 106--112, 1966.

\bibitem[Frieze and Karo{\'n}ski(2016)]{frieze2016introduction}
Alan Frieze and Micha{\l} Karo{\'n}ski.
\newblock \emph{Introduction to Random Graphs}.
\newblock {Cambridge University Press}, 2016.

\bibitem[Nikoletseas et~al.(2008)Nikoletseas, Raptopoulos, and
Spirakis]{nikoletseas2008large}
S~Nikoletseas, Christoforos Raptopoulos, and P~Spirakis.
\newblock Large independent sets in general random intersection graphs.
\newblock \emph{Theor Comput Sci}, 406\penalty0 (3):\penalty0 215--224, 2008.

\bibitem[Deijfen and Kets(2009)]{deijfen2009random}
Maria Deijfen and Willemien Kets.
\newblock Random intersection graphs with tunable degree distribution and
clustering.
\newblock \emph{Probab. Eng. Inf. Sci.}, 23\penalty0 (4):\penalty0 661--674,
2009.

\bibitem[Godehardt and Jaworski(2003)]{godehardt2003two}
Erhard Godehardt and Jerzy Jaworski.
\newblock Two models of random intersection graphs for classification.
\newblock In \emph{Exploratory Data Analysis in Empirical Research}, pages
67--81. {Springer}, 2003.

\bibitem[Davis and Carley(2008)]{davis2008clearing}
George~B Davis and Kathleen~M Carley.
\newblock Clearing the {{FOG}}: {{Fuzzy}}, overlapping groups for social
networks.
\newblock \emph{Soc Netw}, 30\penalty0 (3):\penalty0 201--212, 2008.

\bibitem[Barber(2008)]{barber2012clique}
David Barber.
\newblock Clique matrices for statistical graph decomposition and
parameterising restricted positive definite matrices.
\newblock \emph{Uncertain. Artif. Intell.}, pages 26--33, 2008.

\bibitem[Williamson and Tec(2018)]{williamson2018random}
Sinead~A Williamson and Mauricio Tec.
\newblock Random clique covers for graphs with local density and global
sparsity.
\newblock In \emph{Proceedings of the 2019 Conference on Uncertainty in
    Artificial Intelligence}, 2018.

\bibitem[Ball et~al.(2014)Ball, Sirl, Trapman, et~al.]{ball2014epidemics}
Frank~G Ball, David~J Sirl, Pieter Trapman, et~al.
\newblock Epidemics on random intersection graphs.
\newblock \emph{Ann. Appl. Probab.}, 24\penalty0 (3):\penalty0 1081--1128,
2014.

\bibitem[Xie et~al.(2013)Xie, Kelley, and Szymanski]{xie2013overlapping}
Jierui Xie, Stephen Kelley, and Boleslaw~K Szymanski.
\newblock Overlapping community detection in networks: {{The}} state-of-the-art
and comparative study.
\newblock \emph{Acm Comput. Surv. Csur}, 45\penalty0 (4):\penalty0 43, 2013.

\bibitem[De~La~Vega(1982)]{de1982cardinalite}
W~Fernandez De~La~Vega.
\newblock Sur la cardinalit{\'e} maximum des couplages d'hypergraphes
al{\'e}atoires uniformes.
\newblock \emph{Discrete Math.}, 40\penalty0 (2-3):\penalty0 315--318, 1982.

\bibitem[{Schmidt-Pruzan} and Shamir(1985)]{schmidt1985component}
Jeanette {Schmidt-Pruzan} and Eli Shamir.
\newblock Component structure in the evolution of random hypergraphs.
\newblock \emph{Combinatorica}, 5\penalty0 (1):\penalty0 81--94, 1985.

\bibitem[{de Arruda} et~al.(2020){de Arruda}, Petri, and Moreno]{de2020social}
Guilherme~Ferraz {de Arruda}, Giovanni Petri, and Yamir Moreno.
\newblock Social contagion models on hypergraphs.
\newblock \emph{Phys Rev Res}, 2\penalty0 (2):\penalty0 023032, 2020.

\bibitem[Darling et~al.(2005)Darling, Norris, et~al.]{darling2005structure}
Richard~WR Darling, James~R Norris, et~al.
\newblock Structure of large random hypergraphs.
\newblock \emph{Ann Appl Probab}, 15\penalty0 (1A):\penalty0 125--152, 2005.

\bibitem[Mezard et~al.(2009)Mezard, Mezard, and
Montanari]{mezard2009information}
Marc Mezard, Marc Mezard, and Andrea Montanari.
\newblock \emph{Information, Physics, and Computation}.
\newblock {Oxford University Press}, 2009.

\bibitem[Dembo et~al.(2008)Dembo, Montanari, et~al.]{dembo2008finite}
Amir Dembo, Andrea Montanari, et~al.
\newblock Finite size scaling for the core of large random hypergraphs.
\newblock \emph{Ann. Appl. Probab.}, 18\penalty0 (5):\penalty0 1993--2040,
2008.

\bibitem[Schmidt and Shamir(1983)]{schmidt1983threshold}
Jeanette Schmidt and Eli Shamir.
\newblock A threshold for perfect matchings in random d-pure hypergraphs.
\newblock \emph{Discrete Math.}, 45\penalty0 (2-3):\penalty0 287--295, 1983.

\bibitem[Chen and Frieze(1996)]{chen1996coloring}
Hui Chen and Alan Frieze.
\newblock Coloring bipartite hypergraphs.
\newblock In \emph{International Conference on Integer Programming and
    Combinatorial Optimization}, pages 345--358. {Springer}, 1996.

\bibitem[Demetrovics et~al.(1998)Demetrovics, Katona, Mikl{\'o}s, Seleznjev,
and Thalheim]{demetrovics1998asymptotic}
J{\'a}nos Demetrovics, Gyula~OH Katona, Dezs{\"o} Mikl{\'o}s, Oleg Seleznjev,
and Bernhard Thalheim.
\newblock Asymptotic properties of keys and functional dependencies in random
databases.
\newblock \emph{Theor. Comput. Sci.}, 190\penalty0 (2):\penalty0 151--166,
1998.

\bibitem[Bradde and Bianconi(2009)]{bradde2009percolation}
Serena Bradde and Ginestra Bianconi.
\newblock The percolation transition in correlated hypergraphs.
\newblock \emph{J. Stat. Mech.: Theory Exp.}, 2009\penalty0 (07):\penalty0
P07028, 2009.

\bibitem[Newman and Girvan(2004)]{newman2004finding}
Mark~EJ Newman and Michelle Girvan.
\newblock Finding and evaluating community structure in networks.
\newblock \emph{Phys. Rev. E}, 69\penalty0 (2):\penalty0 026113, 2004.

\bibitem[Chung and Lu(2002)]{chung2002connected}
Fan Chung and Linyuan Lu.
\newblock Connected components in random graphs with given expected degree
sequences.
\newblock \emph{Ann. Comb.}, 6\penalty0 (2):\penalty0 125--145, 2002.

\bibitem[Stasi et~al.(2014)Stasi, Sadeghi, Rinaldo, Petrovi{\'c}, and
Fienberg]{stasi2014beta}
Despina Stasi, Kayvan Sadeghi, Alessandro Rinaldo, Sonja Petrovi{\'c}, and
Stephen~E Fienberg.
\newblock {{$\beta$}} models for random hypergraphs with a given degree
sequence.
\newblock \emph{arXiv:1407.1004}, 2014.

\bibitem[Ghoshdastidar and Dukkipati(2014)]{ghoshdastidar2014consistency}
Debarghya Ghoshdastidar and Ambedkar Dukkipati.
\newblock Consistency of spectral partitioning of uniform hypergraphs under
planted partition model.
\newblock In \emph{Advances in Neural Information Processing Systems}, pages
397--405, 2014.

\bibitem[Ke et~al.(2019)Ke, Shi, and Xia]{ke2019community}
Zheng~Tracy Ke, Feng Shi, and Dong Xia.
\newblock Community detection for hypergraph networks via regularized tensor
power iteration.
\newblock \emph{arXiv:1909.06503}, 2019.

\bibitem[Ahn et~al.(2018)Ahn, Lee, and Suh]{ahn2018hypergraph}
Kwangjun Ahn, Kangwook Lee, and Changho Suh.
\newblock Hypergraph spectral clustering in the weighted stochastic block
model.
\newblock \emph{IEEE J. Sel. Top. Signal Process.}, 12\penalty0 (5):\penalty0
959--974, 2018.

\bibitem[Paul et~al.(2018)Paul, Milenkovic, and Chen]{paul2018higher}
Subhadeep Paul, Olgica Milenkovic, and Yuguo Chen.
\newblock Higher-order spectral clustering under superimposed stochastic block
model.
\newblock \emph{arXiv:1812.06515}, 2018.

\bibitem[Turnbull et~al.(2019)Turnbull, Lunag{\'o}mez, Nemeth, and
Airoldi]{turnbull2019latent}
Kathryn Turnbull, Sim{\'o}n Lunag{\'o}mez, Christopher Nemeth, and Edoardo
Airoldi.
\newblock Latent space representations of hypergraphs.
\newblock \emph{arXiv:1909.00472}, 2019.

\bibitem[Leskovec et~al.(2005)Leskovec, Chakrabarti, Kleinberg, and
Faloutsos]{leskovec2005realistic}
Jurij Leskovec, Deepayan Chakrabarti, Jon Kleinberg, and Christos Faloutsos.
\newblock Realistic, mathematically tractable graph generation and evolution,
using kronecker multiplication.
\newblock In \emph{European Conference on Principles of Data Mining and
    Knowledge Discovery}, pages 133--145. {Springer}, 2005.

\bibitem[Eikmeier et~al.(2018)Eikmeier, Ramani, and
Gleich]{eikmeier2018hyperkron}
Nicole Eikmeier, Arjun Ramani, and David Gleich.
\newblock The {{HyperKron Graph Model}} for higher-order features.
\newblock In \emph{2018 {{IEEE}} International Conference on Data Mining
    ({{ICDM}})}, pages 941--946. {IEEE}, 2018.

\bibitem[Kahle(2011)]{kahle2011random}
Matthew Kahle.
\newblock Random geometric complexes.
\newblock \emph{Discrete Comput. Geom.}, 45\penalty0 (3):\penalty0 553--573,
2011.

\bibitem[Linial and Meshulam(2006)]{linial2006homological}
Nathan Linial and Roy Meshulam.
\newblock Homological connectivity of random 2-complexes.
\newblock \emph{Combinatorica}, 26\penalty0 (4):\penalty0 475--487, 2006.

\bibitem[Kahle(2014)]{kahle2014topology}
Matthew Kahle.
\newblock Topology of random simplicial complexes: A survey.
\newblock \emph{AMS Contemp Math}, 620:\penalty0 201--222, 2014.

\bibitem[Meshulam and Wallach(2009)]{meshulam2009homological}
Roy Meshulam and Nathan Wallach.
\newblock Homological connectivity of random k-dimensional complexes.
\newblock \emph{Random Struct Algorithms}, 34\penalty0 (3):\penalty0 408--417,
2009.

\bibitem[Kahle(2009)]{kahle2009topology}
Matthew Kahle.
\newblock Topology of random clique complexes.
\newblock \emph{Discrete Math.}, 309\penalty0 (6):\penalty0 1658--1671, 2009.

\bibitem[Fowler(2015)]{fowler2015generalized}
Christopher~F Fowler.
\newblock Generalized random simplicial complexes.
\newblock \emph{arXiv:1503.01831}, 2015.

\bibitem[Iacopini et~al.(2019)Iacopini, Petri, Barrat, and
Latora]{iacopini2019simplicial}
Iacopo Iacopini, Giovanni Petri, Alain Barrat, and Vito Latora.
\newblock Simplicial models of social contagion.
\newblock \emph{Nat. Commun.}, 10\penalty0 (1):\penalty0 2485, 2019.

\bibitem[Alberici et~al.(2017)Alberici, Contucci, Mingione, and
Molari]{alberici2017aggregation}
Diego Alberici, Pierluigi Contucci, Emanuele Mingione, and Marco Molari.
\newblock Aggregation models on hypergraphs.
\newblock \emph{Ann. Phys.}, 376:\penalty0 412--424, 2017.

\bibitem[Zuev et~al.(2015)Zuev, Eisenberg, and Krioukov]{zuev2015exponential}
Konstantin Zuev, Or~Eisenberg, and Dmitri Krioukov.
\newblock Exponential random simplicial complexes.
\newblock \emph{J. Phys. A}, 48\penalty0 (46):\penalty0 465002, 2015.

\bibitem[Chazal and Michel(2017)]{chazal2017introduction}
Fr{\'e}d{\'e}ric Chazal and Bertrand Michel.
\newblock An introduction to {{Topological Data Analysis}}: Fundamental and
practical aspects for data scientists.
\newblock \emph{arXiv:1710.04019}, 2017.

\bibitem[Kahle et~al.(2013)Kahle, Meckes, et~al.]{kahle2013limit}
Matthew Kahle, Elizabeth Meckes, et~al.
\newblock Limit the theorems for {{Betti}} numbers of random simplicial
complexes.
\newblock \emph{Homol. Homotopy Appl.}, 15\penalty0 (1):\penalty0 343--374,
2013.

\bibitem[Bobrowski and Kahle(2018)]{bobrowski2018topology}
Omer Bobrowski and Matthew Kahle.
\newblock Topology of random geometric complexes: a survey.
\newblock \emph{J. Appl. Comput. Topol.}, 1\penalty0 (3-4):\penalty0 331--364,
2018.

\bibitem[Fasy et~al.(2014)Fasy, Lecci, Rinaldo, Wasserman, Balakrishnan, Singh,
et~al.]{fasy2014confidence}
Brittany~Terese Fasy, Fabrizio Lecci, Alessandro Rinaldo, Larry Wasserman,
Sivaraman Balakrishnan, Aarti Singh, et~al.
\newblock Confidence sets for persistence diagrams.
\newblock \emph{Ann. Stat.}, 42\penalty0 (6):\penalty0 2301--2339, 2014.

\bibitem[Bianconi and Ziff(2018)]{bianconi2018topological}
Ginestra Bianconi and Robert~M Ziff.
\newblock Topological percolation on hyperbolic simplicial complexes.
\newblock \emph{Physical Review E}, 98\penalty0 (5):\penalty0 052308, 2018.

\bibitem[Bianconi et~al.(2019)Bianconi, Kryven, and
Ziff]{bianconi2019percolation}
Ginestra Bianconi, Ivan Kryven, and Robert~M. Ziff.
\newblock Percolation on branching simplicial and cell complexes and its
relation to interdependent percolation.
\newblock \emph{Phys. Rev. E}, 100\penalty0 (6):\penalty0 062311, 2019.

\bibitem[Overgoor et~al.(2019)Overgoor, Benson, and
Ugander]{overgoor2019choosing}
Jan Overgoor, Austin Benson, and Johan Ugander.
\newblock Choosing to grow a graph: Modeling network formation as discrete
choice.
\newblock In \emph{The World Wide Web Conference}, pages 1409--1420. {ACM},
2019.

\bibitem[Barab{\'a}si and Albert(1999)]{barabasi1999emergence}
Albert-L{\'a}szl{\'o} Barab{\'a}si and R{\'e}ka Albert.
\newblock Emergence of scaling in random networks.
\newblock \emph{Science}, 286\penalty0 (5439):\penalty0 509--512, 1999.

\bibitem[Petri and Barrat(2018)]{petri2018simplicial}
Giovanni Petri and Alain Barrat.
\newblock Simplicial activity driven model.
\newblock \emph{Phys. Rev. Lett.}, 121\penalty0 (22):\penalty0 228301, 2018.

\bibitem[Erg{\"u}n(2002)]{ergun2002human}
G{\"u}ler Erg{\"u}n.
\newblock Human sexual contact network as a bipartite graph.
\newblock \emph{Phys. A}, 308\penalty0 (1-4):\penalty0 483--488, 2002.

\bibitem[Ramasco et~al.(2004)Ramasco, Dorogovtsev, and
{Pastor-Satorras}]{ramasco2004self}
Jos{\'e}~J Ramasco, Sergey~N Dorogovtsev, and Romualdo {Pastor-Satorras}.
\newblock Self-organization of collaboration networks.
\newblock \emph{Phys. Rev. E}, 70\penalty0 (3):\penalty0 036106, 2004.

\bibitem[Beguerisse~D{\'i}az et~al.(2010)Beguerisse~D{\'i}az, Porter, and
Onnela]{beguerisse2010competition}
Mariano Beguerisse~D{\'i}az, Mason~A Porter, and Jukka-Pekka Onnela.
\newblock Competition for popularity in bipartite networks.
\newblock \emph{Chaos}, 20\penalty0 (4):\penalty0 043101, 2010.

\bibitem[Sneppen et~al.(2004)Sneppen, Rosvall, Trusina, and
Minnhagen]{sneppen2004simple}
Kim Sneppen, Martin Rosvall, Ala Trusina, and Petter Minnhagen.
\newblock A simple model for self-organization of bipartite networks.
\newblock \emph{Europhys. Lett.}, 67\penalty0 (3):\penalty0 349, 2004.

\bibitem[Bak et~al.(1987)Bak, Tang, and Wiesenfeld]{bak1987self}
Per Bak, Chao Tang, and Kurt Wiesenfeld.
\newblock Self-organized criticality: {{An}} explanation of the 1/f noise.
\newblock \emph{Phys. Rev. Lett.}, 59\penalty0 (4):\penalty0 381, 1987.

\bibitem[Friel et~al.(2016)Friel, Rastelli, Wyse, and
Raftery]{friel2016interlocking}
Nial Friel, Riccardo Rastelli, Jason Wyse, and Adrian~E Raftery.
\newblock Interlocking directorates in {{Irish}} companies using a latent space
model for bipartite networks.
\newblock \emph{Proc Natl Acad Sci USA}, 113\penalty0 (24):\penalty0
6629--6634, 2016.

\bibitem[Evans(2007)]{evans2007exact}
TS~Evans.
\newblock Exact solutions for network rewiring models.
\newblock \emph{Eur. Phys. J. B}, 56\penalty0 (1):\penalty0 65--69, 2007.

\bibitem[Evans and Plato(2007)]{evans2007exact_b}
TS~Evans and ADK Plato.
\newblock Exact solution for the time evolution of network rewiring models.
\newblock \emph{Phys. Rev. E}, 75\penalty0 (5):\penalty0 056101, 2007.

\bibitem[Wu et~al.(2015)Wu, Menichetti, Rahmede, and Bianconi]{wu2015emergent}
Zhihao Wu, Giulia Menichetti, Christoph Rahmede, and Ginestra Bianconi.
\newblock Emergent complex network geometry.
\newblock \emph{Sci. Rep.}, 5:\penalty0 10073, 2015.

\bibitem[Pollner et~al.(2005)Pollner, Palla, and
Vicsek]{pollner2005preferential}
Peter Pollner, Gergely Palla, and Tamas Vicsek.
\newblock Preferential attachment of communities: {{The}} same principle, but a
higher level.
\newblock \emph{Europhys. Lett.}, 73\penalty0 (3):\penalty0 478, 2005.

\bibitem[Zhou et~al.(2008)Zhou, Xiang, and {Xiao-Fan}]{zhou2008weighted}
Xie Zhou, Li~Xiang, and Wang {Xiao-Fan}.
\newblock Weighted evolving networks with self-organized communities.
\newblock \emph{Commun. Theor. Phys.}, 50\penalty0 (1):\penalty0 261, 2008.

\bibitem[{H{\'e}bert-Dufresne} et~al.(2011){H{\'e}bert-Dufresne}, Allard,
Marceau, No{\"e}l, and Dub{\'e}]{hebert2011structural}
Laurent {H{\'e}bert-Dufresne}, Antoine Allard, Vincent Marceau,
Pierre-Andr{\'e} No{\"e}l, and Louis~J Dub{\'e}.
\newblock Structural preferential attachment: {{Network}} organization beyond
the link.
\newblock \emph{Phys. Rev. Lett.}, 107\penalty0 (15):\penalty0 158702, 2011.

\bibitem[{H{\'e}bert-Dufresne} et~al.(2012){H{\'e}bert-Dufresne}, Allard,
Marceau, No{\"e}l, and Dub{\'e}]{hebert2012structural}
Laurent {H{\'e}bert-Dufresne}, Antoine Allard, Vincent Marceau,
Pierre-Andr{\'e} No{\"e}l, and Louis~J Dub{\'e}.
\newblock Structural preferential attachment: {{Stochastic}} process for the
growth of scale-free, modular, and self-similar systems.
\newblock \emph{Phys. Rev. E}, 85\penalty0 (2):\penalty0 026108, 2012.

\bibitem[Young et~al.(2016)Young, {H{\'e}bert-Dufresne}, Allard, and
Dub{\'e}]{young2016growing}
Jean-Gabriel Young, Laurent {H{\'e}bert-Dufresne}, Antoine Allard, and Louis~J
Dub{\'e}.
\newblock Growing networks of overlapping communities with internal structure.
\newblock \emph{Phys. Rev. E}, 94\penalty0 (2):\penalty0 022317, 2016.

\bibitem[{H{\'e}bert-Dufresne} et~al.(2015){H{\'e}bert-Dufresne}, Laurence,
Allard, Young, and Dub{\'e}]{hebert2015complex}
Laurent {H{\'e}bert-Dufresne}, Edward Laurence, Antoine Allard, Jean-Gabriel
Young, and Louis~J Dub{\'e}.
\newblock Complex networks as an emerging property of hierarchical preferential
attachment.
\newblock \emph{Phys. Rev. E}, 92\penalty0 (6):\penalty0 062809, 2015.

\bibitem[Aldous(1985)]{aldous1985exchangeability}
David~J Aldous.
\newblock Exchangeability and related topics.
\newblock In \emph{{\'E}cole d'{{{\'E}t{\'e}}} de Probabilit{\'e}s de
    Saint-Flour {{XIII}}\textemdash{}1983}, pages 1--198. {Springer}, 1985.

\bibitem[Griffiths and Ghahramani(2011)]{griffiths2011indian}
Thomas~L Griffiths and Zoubin Ghahramani.
\newblock The indian buffet process: {{An}} introduction and review.
\newblock \emph{J Mach Learn Res}, 12\penalty0 (Apr):\penalty0 1185--1224,
2011.

\bibitem[Zhang and Liu(2010)]{zhang2010hypergraph}
Zi-Ke Zhang and Chuang Liu.
\newblock A hypergraph model of social tagging networks.
\newblock \emph{J. Stat. Mech.: Theory Exp.}, 2010\penalty0 (10):\penalty0
P10005, 2010.

\bibitem[Wang et~al.(2010)Wang, Rong, Deng, and Zhang]{wang2010evolving}
Jian-Wei Wang, Li-Li Rong, Qiu-Hong Deng, and Ji-Yong Zhang.
\newblock Evolving hypernetwork model.
\newblock \emph{Eur. Phys. J. B}, 77\penalty0 (4):\penalty0 493--498, 2010.

\bibitem[Liu et~al.(2012)Liu, Blenn, and Van~Mieghem]{liu2012social}
Dajie Liu, Norbert Blenn, and Piet Van~Mieghem.
\newblock A social network model exhibiting tunable overlapping community
structure.
\newblock \emph{Procedia Comput. Sci.}, 9:\penalty0 1400--1409, 2012.

\bibitem[Hu et~al.(2019)Hu, Guo, Li, Zhao, et~al.]{hu2019hypernetwork}
Feng Hu, Jin-Li Guo, Fa-Xu Li, Hai-Xing Zhao, et~al.
\newblock Hypernetwork models based on random hypergraphs.
\newblock \emph{Int. J. Mod. Phys. C IJMPC}, 30\penalty0 (08):\penalty0 1--15,
2019.

\bibitem[{Guang-Yong} and {Jian-Guo}(2013)]{guang2013local}
Yang {Guang-Yong} and Liu {Jian-Guo}.
\newblock A local-world evolving hypernetwork model.
\newblock \emph{Chin Phys B}, 23\penalty0 (1):\penalty0 018901, 2013.

\bibitem[Wu et~al.(2014)Wu, Duan, and Fu]{wu2014synchronization}
Zhaoyan Wu, Jinqiao Duan, and Xinchu Fu.
\newblock Synchronization of an evolving complex hyper-network.
\newblock \emph{Appl. Math. Model.}, 38\penalty0 (11-12):\penalty0 2961--2968,
2014.

\bibitem[Guo et~al.(2016)Guo, Zhu, Suo, and Forrest]{guo2016non}
Jin-Li Guo, Xin-Yun Zhu, Qi~Suo, and Jeffrey Forrest.
\newblock Non-uniform evolving hypergraphs and weighted evolving hypergraphs.
\newblock \emph{Sci. Rep.}, 6:\penalty0 36648, 2016.

\bibitem[Krapivsky et~al.(2000)Krapivsky, Redner, and
Leyvraz]{krapivsky2000connectivity}
Paul~L Krapivsky, Sidney Redner, and Francois Leyvraz.
\newblock Connectivity of growing random networks.
\newblock \emph{Phys. Rev. Lett.}, 85\penalty0 (21):\penalty0 4629, 2000.

\bibitem[Guo and Suo(2015)]{guo2015brand}
Jin-Li Guo and Qi~Suo.
\newblock Brand effect versus competitiveness in hypernetworks.
\newblock \emph{Chaos}, 25\penalty0 (2):\penalty0 023102, 2015.

\bibitem[Bianconi(2015)]{bianconi2015interdisciplinary}
Ginestra Bianconi.
\newblock Interdisciplinary and physics challenges of network theory.
\newblock \emph{Europhys. Lett.}, 111\penalty0 (5):\penalty0 56001, 2015.

\bibitem[Bianconi and Rahmede(2015)]{bianconi2015complexa}
Ginestra Bianconi and Christoph Rahmede.
\newblock Complex quantum network manifolds in dimension d 2
are scale-free.
\newblock \emph{Sci. Rep.}, 5:\penalty0 13979, 2015.

\bibitem[Bianconi et~al.(2015)Bianconi, Rahmede, and Wu]{bianconi2015complexb}
Ginestra Bianconi, Christoph Rahmede, and Zhihao Wu.
\newblock Complex quantum network geometries: {{Evolution}} and phase
transitions.
\newblock \emph{Phys. Rev. E}, 92\penalty0 (2):\penalty0 022815, 2015.

\bibitem[Courtney and Bianconi(2017)]{courtney2017weighted}
Owen~T Courtney and Ginestra Bianconi.
\newblock Weighted growing simplicial complexes.
\newblock \emph{Phys. Rev. E}, 95\penalty0 (6):\penalty0 062301, 2017.

\bibitem[Fountoulakis et~al.(2019)Fountoulakis, Iyer, Mailler, and
Sulzbach]{fountoulakis2019dynamical}
Nikolaos Fountoulakis, Tejas Iyer, C{\'e}cile Mailler, and Henning Sulzbach.
\newblock Dynamical models for random simplicial complexes.
\newblock \emph{arXiv:1910.12715}, 2019.

\bibitem[Sizemore et~al.(2018{\natexlab{a}})Sizemore, Karuza, Giusti, and
Bassett]{sizemore2018knowledge}
Ann~E Sizemore, Elisabeth~A Karuza, Chad Giusti, and Danielle~S Bassett.
\newblock Knowledge gaps in the early growth of semantic feature networks.
\newblock \emph{Nat Hum Behav}, 2\penalty0 (9):\penalty0 682,
2018{\natexlab{a}}.

\bibitem[Blevins and Bassett(2020)]{blevins2020reorderability}
Ann~Sizemore Blevins and Danielle~S Bassett.
\newblock On the reorderability of node-filtered order complexes.
\newblock \emph{Phys. Rev. E}, 101:\penalty0 052311, 2020.

\bibitem[{da Silva} et~al.(2018){da Silva}, Bianconi, {da Costa}, Dorogovtsev,
and Mendes]{da2018complex}
Diamantino~C {da Silva}, Ginestra Bianconi, Rui~A {da Costa}, Sergey~N
Dorogovtsev, and Jos{\'e}~FF Mendes.
\newblock Complex network view of evolving manifolds.
\newblock \emph{Phys. Rev. E}, 97\penalty0 (3):\penalty0 032316, 2018.

\bibitem[Courtney and Bianconi(2018)]{courtney2018dense}
Owen~T Courtney and Ginestra Bianconi.
\newblock Dense power-law networks and simplicial complexes.
\newblock \emph{Phys. Rev. E}, 97\penalty0 (5):\penalty0 052303, 2018.

\bibitem[Kim et~al.(2018)Kim, Schein, Desmarais, and Wallach]{kim2018hyperedge}
Bomin Kim, Aaron Schein, Bruce~A Desmarais, and Hanna Wallach.
\newblock The hyperedge event model.
\newblock \emph{arXiv:1807.08225}, 2018.

\bibitem[Masuda et~al.(2017)Masuda, Porter, and Lambiotte]{masuda2017random}
Naoki Masuda, Mason~A Porter, and Renaud Lambiotte.
\newblock Random walks and diffusion on networks.
\newblock \emph{Phys. Rep.}, 2017.

\bibitem[Aldous and Fill(2002)]{aldous2002reversible}
David Aldous and Jim Fill.
\newblock Reversible {{Markov}} chains and random walks on graphs.
\newblock \emph{Unfinished Monogr.}, 2002.

\bibitem[Samukhin et~al.(2008)Samukhin, Dorogovtsev, and
Mendes]{samukhin2008laplacian}
AN~Samukhin, SN~Dorogovtsev, and JFF Mendes.
\newblock Laplacian spectra of, and random walks on, complex networks: {{Are}}
scale-free architectures really important?
\newblock \emph{Phys. Rev. E}, 77\penalty0 (3):\penalty0 036115, 2008.

\bibitem[Hoffmann et~al.(2012)Hoffmann, Porter, and
Lambiotte]{hoffman2012generalized}
Till Hoffmann, Mason~A. Porter, and Renaud Lambiotte.
\newblock Generalized master equations for non-{{Poisson}} dynamics on
networks.
\newblock \emph{Phys. Rev. E}, 86\penalty0 (4):\penalty0 046102, 2012.

\bibitem[DeGroot(1974)]{degroot74reaching}
Morris~H DeGroot.
\newblock Reaching a consensus.
\newblock \emph{J. Am. Stat. Assoc.}, 69\penalty0 (345):\penalty0 118--121,
1974.

\bibitem[Boltzmann(1964)]{boltzmann1964lectures}
Ludwig Boltzmann.
\newblock Lectures on gas theory, translated by s.
\newblock \emph{Brush Univ. Calif. Los Angel. Calif}, 1964.

\bibitem[Tolman(1979)]{tolman1979principles}
Richard~Chace Tolman.
\newblock \emph{The Principles of Statistical Mechanics}.
\newblock {Courier Corporation}, 1979.

\bibitem[Chung and Graham(1997)]{chung1997spectral}
Fan~RK Chung and Fan~Chung Graham.
\newblock \emph{Spectral Graph Theory}.
\newblock Number~92. {American Mathematical Soc.}, 1997.

\bibitem[Neuh{\"a}user et~al.(2020)Neuh{\"a}user, Mellor, and
Lambiotte]{neuhauser2019multi}
Leonie Neuh{\"a}user, Andrew Mellor, and Renaud Lambiotte.
\newblock Multibody interactions and nonlinear consensus dynamics on networked
systems.
\newblock \emph{Phys. Rev. E}, 101\penalty0 (3):\penalty0 032310, 2020.

\bibitem[Torres and Bianconi(2020)]{torres2020simplicial}
Joaqu{\'i}n~J. Torres and Ginestra Bianconi.
\newblock Simplicial complexes: Higher-order spectral dimension and dynamics.
\newblock \emph{J. Phys.: Complex.}, 1:\penalty0 015002, 2020.

\bibitem[Burioni and Cassi(1996)]{burioni1996universal}
Raffaella Burioni and Davide Cassi.
\newblock Universal properties of spectral dimension.
\newblock \emph{Phys. Rev. Lett.}, 76\penalty0 (7):\penalty0 1091, 1996.

\bibitem[Mill{\'a}n et~al.(2019)Mill{\'a}n, Torres, and
Bianconi]{millan2019synchronization}
Ana~P Mill{\'a}n, Joaqu{\'i}n~J Torres, and Ginestra Bianconi.
\newblock Synchronization in network geometries with finite spectral dimension.
\newblock \emph{Phys. Rev. E}, 99\penalty0 (2):\penalty0 022307, 2019.

\bibitem[Jia et~al.(2019)Jia, Schaub, Segarra, and Benson]{jia2019graph}
Junteng Jia, Michael~T Schaub, Santiago Segarra, and Austin~R Benson.
\newblock Graph-based semi-supervised \& active learning for edge flows.
\newblock In \emph{Proceedings of the 25th {{ACM SIGKDD}} International
    Conference on Knowledge Discovery \& Data Mining}, pages 761--771, 2019.

\bibitem[Mukherjee and Steenbergen(2016)]{mukherjee2016random}
Sayan Mukherjee and John Steenbergen.
\newblock Random walks on simplicial complexes and harmonics.
\newblock \emph{Random Struc Algorithms}, 49\penalty0 (2):\penalty0 379--405,
2016.

\bibitem[Dua and Graff(2017)]{dua2019UCI}
Dheeru Dua and Casey Graff.
\newblock {{UCI}} machine learning repository.
\newblock 2017.

\bibitem[Carletti et~al.(2020)Carletti, Battiston, Cencetti, and
Fanelli]{carletti2020random}
Timoteo Carletti, Federico Battiston, Giulia Cencetti, and Duccio Fanelli.
\newblock Random walks on hypergraphs.
\newblock \emph{Phys. Rev. E}, 101\penalty0 (2):\penalty0 022308, 2020.

\bibitem[Chitra and Raphael(2019)]{chitra2019random}
Uthsav Chitra and Benjamin~J Raphael.
\newblock Random walks on hypergraphs with edge-dependent vertex weights.
\newblock In \emph{Proceedings of the 36th International Conference on Machine
    Learning}, pages 1172--1181, 2019.

\bibitem[Agarwal et~al.(2006)Agarwal, Branson, and Belongie]{agarwal2006higher}
Sameer Agarwal, Kristin Branson, and Serge Belongie.
\newblock Higher order learning with graphs.
\newblock In \emph{Proceedings of the 23rd International Conference on
    {{Machine}} Learning}, pages 17--24. {ACM}, 2006.

\bibitem[Li and Milenkovic(2017)]{li2017inhomogeneous}
Pan Li and Olgica Milenkovic.
\newblock Inhomogeneous hypergraph clustering with applications.
\newblock In \emph{Advances in Neural Information Processing Systems}, pages
2308--2318, 2017.

\bibitem[Li et~al.(2018)Li, He, and Zhu]{li2018tail}
Jianbo Li, Jingrui He, and Yada Zhu.
\newblock E-tail product return prediction via hypergraph-based local graph
cut.
\newblock In \emph{Proceedings of the 24th {{ACM SIGKDD}} International
    Conference on Knowledge Discovery \& Data Mining}, pages 519--527. {ACM},
2018.

\bibitem[Ding and Yilmaz(2010)]{ding2010interactive}
Lei Ding and Alper Yilmaz.
\newblock Interactive image segmentation using probabilistic hypergraphs.
\newblock \emph{Pattern Recognit.}, 43\penalty0 (5):\penalty0 1863--1873, 2010.

\bibitem[Huang et~al.(2010)Huang, Liu, Zhang, and Metaxas]{huang2010image}
Yuchi Huang, Qingshan Liu, Shaoting Zhang, and Dimitris~N Metaxas.
\newblock Image retrieval via probabilistic hypergraph ranking.
\newblock In \emph{2010 {{IEEE}} Computer Society Conference on Computer Vision
    and Pattern Recognition}, pages 3376--3383. {IEEE}, 2010.

\bibitem[Ducournau and Bretto(2014)]{ducournau2014random}
Aur{\'e}lien Ducournau and Alain Bretto.
\newblock Random walks in directed hypergraphs and application to
semi-supervised image segmentation.
\newblock \emph{Comput. Vis. Image Underst.}, 120:\penalty0 91--102, 2014.

\bibitem[Zeng et~al.(2016)Zeng, Wu, Sargolzaei, and Yen]{zeng2016learn}
Kaiman Zeng, Nansong Wu, Arman Sargolzaei, and Kang Yen.
\newblock Learn to rank images: {{A}} unified probabilistic hypergraph model
for visual search.
\newblock \emph{Math. Probl. Eng.}, 2016, 2016.

\bibitem[Zhang et~al.(2018)Zhang, Lin, Gao, and BNRist]{zhang2018dynamic}
Zizhao Zhang, Haojie Lin, Yue Gao, and KLISS BNRist.
\newblock Dynamic hypergraph structure learning.
\newblock In \emph{{{IJCAI}}}, pages 3162--3169, 2018.

\bibitem[Chan et~al.(2015)Chan, Tang, and Zhang]{chan2015spectral}
TH~Chan, Zhihao~Gavin Tang, and Chenzi Zhang.
\newblock Spectral properties of {Laplacian} and stochastic diffusion process
for edge expansion in hypergraphs.
\newblock \emph{arXiv:1510.01520}, 2015.

\bibitem[Chan et~al.(2019)Chan, Tang, Wu, and Zhang]{chan2019diffusion}
T-H~Hubert Chan, Zhihao~Gavin Tang, Xiaowei Wu, and Chenzi Zhang.
\newblock Diffusion operator and spectral analysis for directed hypergraph
{{Laplacian}}.
\newblock \emph{Theor. Comput. Sci.}, 784:\penalty0 46--64, 2019.

\bibitem[Billings et~al.(2019)Billings, Hu, Lerda, Medvedev, Mottes, Onicas,
Santoro, and Petri]{billings2019simplex2vec}
Jacob Charles~Wright Billings, Mirko Hu, Giulia Lerda, Alexey~N Medvedev,
Francesco Mottes, Adrian Onicas, Andrea Santoro, and Giovanni Petri.
\newblock {{Simplex2Vec}} embeddings for community detection in simplicial
complexes.
\newblock \emph{arXiv:1906.09068}, 2019.

\bibitem[Salnikov et~al.(2018)Salnikov, Cassese, and
Lambiotte]{salnikov2018simplicial}
Vsevolod Salnikov, Daniele Cassese, and Renaud Lambiotte.
\newblock Simplicial complexes and complex systems.
\newblock \emph{Eur. J. Phys.}, 40\penalty0 (1):\penalty0 014001, 2018.

\bibitem[Tran et~al.(2015)Tran, Tran, Trang, et~al.]{tran2015combinatorial}
Loc~Hoang Tran, Linh~Hoang Tran, Hoang Trang, et~al.
\newblock Combinatorial and random walk hypergraph {Laplacian} eigenmaps.
\newblock \emph{Int. J. Mach. Learn. Comput.}, 5\penalty0 (6):\penalty0 462,
2015.

\bibitem[Satchidanand et~al.(2015)Satchidanand, Ananthapadmanaban, and
Ravindran]{satchidanand2015extended}
Sai~Nageswar Satchidanand, Harini Ananthapadmanaban, and Balaraman Ravindran.
\newblock Extended discriminative random walk: A hypergraph approach to
multi-view multi-relational transductive learning.
\newblock In \emph{Twenty-Fourth International Joint Conference on Artificial
    Intelligence}, 2015.

\bibitem[Liu et~al.(2018)Liu, Yuan, Duan, and Li]{liu2018quantum}
Ying Liu, Jiabin Yuan, Bojia Duan, and Dan Li.
\newblock Quantum walks on regular uniform hypergraphs.
\newblock \emph{Sci. Rep.}, 8\penalty0 (1):\penalty0 9548, 2018.

\bibitem[Cooper et~al.(2011)Cooper, Frieze, and Radzik]{cooper2011cover}
Colin Cooper, Alan Frieze, and Tomasz Radzik.
\newblock The cover times of random walks on hypergraphs.
\newblock In \emph{International Colloquium on Structural Information and
    Communication Complexity}, pages 210--221. {Springer}, 2011.

\bibitem[Turing(1952)]{turing1952chemical}
Alan~Mathison Turing.
\newblock The chemical basis of morphogenesis.
\newblock \emph{Philos. Trans. R. Soc. Lond. B Biol. Sci.}, 237\penalty0
(641):\penalty0 37--72, 1952.

\bibitem[Nakao and Mikhailov(2010)]{nakao2010turing}
Hiroya Nakao and Alexander~S Mikhailov.
\newblock Turing patterns in network-organized activator--inhibitor systems.
\newblock \emph{Nat. Phys.}, 6\penalty0 (7):\penalty0 544--550, 2010.

\bibitem[Asllani et~al.(2014)Asllani, Challenger, Pavone, Sacconi, and
Fanelli]{asllani2014theory}
Malbor Asllani, Joseph~D Challenger, Francesco~Saverio Pavone, Leonardo
Sacconi, and Duccio Fanelli.
\newblock The theory of pattern formation on directed networks.
\newblock \emph{Nat. Commun.}, 5\penalty0 (1):\penalty0 1--9, 2014.

\bibitem[Cencetti et~al.(2018)Cencetti, Clusella, and
Fanelli]{cencetti2018pattern}
Giulia Cencetti, Pau Clusella, and Duccio Fanelli.
\newblock Pattern invariance for reaction-diffusion systems on complex
networks.
\newblock \emph{Sci. Rep.}, 8\penalty0 (1):\penalty0 1--9, 2018.

\bibitem[Harush and Barzel(2017)]{harush2017dynamic}
Uzi Harush and Baruch Barzel.
\newblock Dynamic patterns of information flow in complex networks.
\newblock \emph{Nat. Commun.}, 8\penalty0 (1):\penalty0 2181, 2017.

\bibitem[Huygens and Oscillatorium(1986)]{huygens1986pendulum}
Christiaan Huygens and Horologium Oscillatorium.
\newblock The pendulum clock.
\newblock \emph{Trans RJ Blackwell Iowa State Univ. Press Ames}, 1986.

\bibitem[N{\'e}da et~al.(2000)N{\'e}da, Ravasz, Brechet, Vicsek, and
Barab{\'a}si]{neda2000sound}
Zolt{\'a}n N{\'e}da, Erzs{\'e}bet Ravasz, Yves Brechet, Tam{\'a}s Vicsek, and
A-L Barab{\'a}si.
\newblock The sound of many hands clapping.
\newblock \emph{Nature}, 403\penalty0 (6772):\penalty0 849--850, 2000.

\bibitem[Buck(1988)]{buck1988synchronous}
John Buck.
\newblock Synchronous rhythmic flashing of fireflies. {{II}}.
\newblock \emph{Q. Rev. Biol.}, 63\penalty0 (3):\penalty0 265--289, 1988.

\bibitem[Boccaletti et~al.(2002)Boccaletti, Kurths, Osipov, Valladares, and
Zhou]{boccaletti2002synchro}
S.~Boccaletti, J.~Kurths, G.~Osipov, D.L. Valladares, and C.S. Zhou.
\newblock The synchronization of chaotic systems.
\newblock \emph{Phys. Rep.}, 366\penalty0 (1):\penalty0 1--101, 2002.

\bibitem[Pikovsky et~al.(2003)Pikovsky, Rosenblum, and
Kurths]{pikovsky2003synchronization}
A.~Pikovsky, M.~Rosenblum, and J.~Kurths.
\newblock \emph{Synchronization: {{A}} Universal Concept in Nonlinear
    Sciences}, volume~12.
\newblock {Cambridge University Press}, {Cambridge}, 2003.

\bibitem[Strogatz(2004)]{strogatz2004sync}
S.~H. Strogatz.
\newblock \emph{Sync: {{The}} Emerging Science of Spontaneous Order}.
\newblock {Penguin UK}, 2004.

\bibitem[Boccaletti et~al.(2018)Boccaletti, Pisarchik, Del~Genio, and
Amann]{boccaletti2018synchronization}
Stefano Boccaletti, Alexander~N Pisarchik, Charo~I Del~Genio, and Andreas
Amann.
\newblock \emph{Synchronization: From Coupled Systems to Complex Networks}.
\newblock {Cambridge University Press}, 2018.

\bibitem[Kuramoto(1984)]{kuramoto1984chemical}
Y.~Kuramoto.
\newblock \emph{Chemical Oscillations, Waves, and Turbulence}.
\newblock {Springer-Verlag}, {Tokyo}, 1984.

\bibitem[Acebr{\'o}n et~al.(2005)Acebr{\'o}n, Bonilla, Vicente, Ritort, and
Spigler]{acebron2005kuramoto}
Juan~A Acebr{\'o}n, Luis~L Bonilla, Conrad J~P{\'e}rez Vicente, F{\'e}lix
Ritort, and Renato Spigler.
\newblock The {{Kuramoto}} model: {{A}} simple paradigm for synchronization
phenomena.
\newblock \emph{Rev. Mod. Phys.}, 77\penalty0 (1):\penalty0 137, 2005.

\bibitem[Arenas et~al.(2008)Arenas, {D{\'i}az-Guilera}, Kurths, Moreno, and
Zhou]{arenas2008synchronization}
A.~Arenas, A.~{D{\'i}az-Guilera}, J.~Kurths, Y.~Moreno, and C.~Zhou.
\newblock Synchronization in complex networks.
\newblock \emph{Phys. Rep.}, 469\penalty0 (3):\penalty0 93--153, 2008.

\bibitem[Rodrigues et~al.(2016)Rodrigues, Peron, Ji, and
Kurths]{rodrigues2016kuramoto}
F.~A. Rodrigues, T.~K. D.~M. Peron, P.~Ji, and J.~Kurths.
\newblock The {{Kuramoto}} model in complex networks.
\newblock \emph{Phys. Rep.}, 610:\penalty0 1--98, 2016.

\bibitem[Barahona and Pecora(2002)]{barahona2002synchronization}
Mauricio Barahona and Louis~M Pecora.
\newblock Synchronization in small-world systems.
\newblock \emph{Phys. Rev. Lett.}, 89\penalty0 (5):\penalty0 054101, 2002.

\bibitem[{G{\'o}mez-Gardenes} et~al.(2011){G{\'o}mez-Gardenes}, G{\'o}mez,
Arenas, and Moreno]{gomez2011explosive}
Jes{\'u}s {G{\'o}mez-Gardenes}, Sergio G{\'o}mez, Alex Arenas, and Yamir
Moreno.
\newblock Explosive synchronization transitions in scale-free networks.
\newblock \emph{Phys. Rev. Lett.}, 106\penalty0 (12):\penalty0 128701, 2011.

\bibitem[Boccaletti et~al.(2016)Boccaletti, Almendral, Guan, Leyva, Liu,
{Sendi{\~n}a-Nadal}, Wang, and Zou]{boccaletti2016explosive}
S~Boccaletti, JA~Almendral, S~Guan, I~Leyva, Z~Liu, I~{Sendi{\~n}a-Nadal},
Z~Wang, and Y~Zou.
\newblock Explosive transitions in complex networks' structure and dynamics:
{{Percolation}} and synchronization.
\newblock \emph{Phys. Rep.}, 660:\penalty0 1--94, 2016.

\bibitem[Nicosia et~al.(2013)Nicosia, Valencia, Chavez, {D{\'i}az-Guilera}, and
Latora]{nicosia2013remote}
Vincenzo Nicosia, Miguel Valencia, Mario Chavez, Albert {D{\'i}az-Guilera}, and
Vito Latora.
\newblock Remote synchronization reveals network symmetries and functional
modules.
\newblock \emph{Phys. Rev. Lett.}, 110\penalty0 (17):\penalty0 174102, 2013.

\bibitem[Pecora et~al.(2014)Pecora, Sorrentino, Hagerstrom, Murphy, and
Roy]{pecora2014cluster}
Louis~M Pecora, Francesco Sorrentino, Aaron~M Hagerstrom, Thomas~E Murphy, and
Rajarshi Roy.
\newblock Cluster synchronization and isolated desynchronization in complex
networks with symmetries.
\newblock \emph{Nat. Commun.}, 5\penalty0 (1):\penalty0 1--8, 2014.

\bibitem[Abrams and Strogatz(2004)]{abrams2004chimera}
Daniel~M Abrams and Steven~H Strogatz.
\newblock Chimera states for coupled oscillators.
\newblock \emph{Phys. Rev. Lett.}, 93\penalty0 (17):\penalty0 174102, 2004.

\bibitem[Bi et~al.(2016)Bi, Hu, Boccaletti, Wang, Zou, Liu, and
Guan]{bi2016coexistence}
Hongjie Bi, Xin Hu, S~Boccaletti, Xingang Wang, Yong Zou, Zonghua Liu, and
Shuguang Guan.
\newblock Coexistence of quantized, time dependent, clusters in globally
coupled oscillators.
\newblock \emph{Phys. Rev. Lett.}, 117\penalty0 (20):\penalty0 204101, 2016.

\bibitem[Watanabe and Strogatz(1993)]{watanabe1993integrability}
S.~Watanabe and S.~H. Strogatz.
\newblock Integrability of a globally coupled oscillator array.
\newblock \emph{Phys. Rev. Lett.}, 70\penalty0 (16):\penalty0 2391, 1993.

\bibitem[Watanabe and Strogatz(1994)]{watanabe1994constants}
S.~Watanabe and S.~H. Strogatz.
\newblock Constants of motion for superconducting {{Josephson}} arrays.
\newblock \emph{Phys. D}, 74\penalty0 (3-4):\penalty0 197--253, 1994.

\bibitem[Ott and Antonsen(2008)]{ott2008low}
Edward Ott and Thomas~M Antonsen.
\newblock Low dimensional behavior of large systems of globally coupled
oscillators.
\newblock \emph{Chaos Interdiscip. J. Nonlinear Sci.}, 18\penalty0
(3):\penalty0 037113, 2008.

\bibitem[Vega et~al.(2004)Vega, {V{\'a}zquez-Prada}, and
Pacheco]{moreno2004fitness}
Yamir~Moreno Vega, Miguel {V{\'a}zquez-Prada}, and Amalio~F Pacheco.
\newblock Fitness for synchronization of network motifs.
\newblock \emph{Phys. A}, 343:\penalty0 279--287, 2004.

\bibitem[D'Huys et~al.(2008)D'Huys, Vicente, Erneux, Danckaert, and
Fischer]{dhuys2008synchronization}
Otti D'Huys, Raul Vicente, Thomas Erneux, Jan Danckaert, and Ingo Fischer.
\newblock Synchronization properties of network motifs: {{Influence}} of
coupling delay and symmetry.
\newblock \emph{Chaos}, 18\penalty0 (3):\penalty0 037116, 2008.

\bibitem[Skardal and Arenas(2019{\natexlab{a}})]{skardal2019abrupt}
Per~Sebastian Skardal and Alex Arenas.
\newblock Abrupt desynchronization and extensive multistability in globally
coupled oscillator simplexes.
\newblock \emph{Phys. Rev. Lett.}, 122\penalty0 (24):\penalty0 248301,
2019{\natexlab{a}}.

\bibitem[Xu et~al.(2020)Xu, Wang, and Skardal]{xu2020bifurcation}
Can Xu, Xuebin Wang, and Per~Sebastian Skardal.
\newblock Bifurcation and structural stability of simplicial oscillator
populations: {{Exact}} results.
\newblock \emph{arXiv:2002.03166}, 2020.

\bibitem[Tanaka and Aoyagi(2011)]{tanaka2011multistable}
Takuma Tanaka and Toshio Aoyagi.
\newblock Multistable attractors in a network of phase oscillators with
three-body interactions.
\newblock \emph{Phys. Rev. Lett.}, 106\penalty0 (22):\penalty0 224101, 2011.

\bibitem[Ashwin and Rodrigues(2016)]{ashwin2016hopf}
Peter Ashwin and Ana Rodrigues.
\newblock Hopf normal form with S N symmetry and reduction
to systems of nonlinearly coupled phase oscillators.
\newblock \emph{Phys. D}, 325:\penalty0 14--24, 2016.

\bibitem[Komarov and Pikovsky(2015)]{komarov2015finitesizeinduced}
Maxim Komarov and Arkady Pikovsky.
\newblock Finite-size-induced transitions to synchrony in oscillator ensembles
with nonlinear global coupling.
\newblock \emph{Phys. Rev. E}, 92\penalty0 (2):\penalty0 020901, 2015.

\bibitem[Skardal and Arenas(2019{\natexlab{b}})]{skardal2019higher}
Per~Sebastian Skardal and Alex Arenas.
\newblock Higher-order interactions in complex networks of phase oscillators
promote abrupt synchronization switching.
\newblock \emph{arXiv:1909.08057}, 2019{\natexlab{b}}.

\bibitem[Paz{\'o}(2005)]{pazo2005thermodynamic}
Diego Paz{\'o}.
\newblock Thermodynamic limit of the first-order phase transition in the
{{Kuramoto}} model.
\newblock \emph{Phys. Rev. E}, 72\penalty0 (4):\penalty0 046211, 2005.

\bibitem[Nicosia et~al.(2017)Nicosia, Skardal, Arenas, and
Latora]{nicosia2017intertwined}
Vincenzo Nicosia, Per~Sebastian Skardal, Alex Arenas, and Vito Latora.
\newblock Collective phenomena emerging from the interactions between dynamical
processes in multiplex networks.
\newblock \emph{Phys. Rev. Lett.}, 118\penalty0 (13):\penalty0 138302, 2017.

\bibitem[D'Souza et~al.(2019)D'Souza, {G{\'o}mez-Garde{\~n}es}, Nagler, and
Arenas]{dsouza2019explosive}
Raissa~M D'Souza, Jesus {G{\'o}mez-Garde{\~n}es}, Jan Nagler, and Alex Arenas.
\newblock Explosive phenomena in complex networks.
\newblock \emph{Adv. Phys.}, 68\penalty0 (3):\penalty0 123--223, 2019.

\bibitem[Berec(2016{\natexlab{a}})]{berec2016chimera}
Vesna Berec.
\newblock Chimera state and route to explosive synchronization.
\newblock \emph{Chaos}, 86:\penalty0 75--81, 2016{\natexlab{a}}.

\bibitem[Berec(2016{\natexlab{b}})]{berec2016explosive}
V~Berec.
\newblock Explosive synchronization in clustered scale-free networks:
{{Revealing}} the existence of chimera state.
\newblock \emph{Eur Phys J ST}, 225\penalty0 (1):\penalty0 7--15,
2016{\natexlab{b}}.

\bibitem[Stankovski et~al.(2015)Stankovski, Ticcinelli, McClintock, and
Stefanovska]{stankovski2015coupling}
Tomislav Stankovski, Valentina Ticcinelli, Peter~VE McClintock, and Aneta
Stefanovska.
\newblock Coupling functions in networks of oscillators.
\newblock \emph{New J. Phys.}, 17\penalty0 (3):\penalty0 035002, 2015.

\bibitem[Le{\'o}n and Paz{\'o}(2019)]{leon2019phase}
Iv{\'a}n Le{\'o}n and Diego Paz{\'o}.
\newblock Phase reduction beyond the first order: The case of the mean-field
complex {{Ginzburg}}-{{Landau}} equation.
\newblock \emph{Phys. Rev. E}, 100\penalty0 (1):\penalty0 012211, 2019.

\bibitem[Mill\'an et~al.(2020)Mill\'an, Torres, and
Bianconi]{millan2019explosive}
Ana~P. Mill\'an, Joaqu\'{\i}n~J. Torres, and Ginestra Bianconi.
\newblock Explosive higher-order {Kuramoto} dynamics on simplicial complexes.
\newblock \emph{Phys. Rev. Lett.}, 124:\penalty0 218301, May 2020.

\bibitem[Mill{\'a}n et~al.(2018)Mill{\'a}n, Torres, and
Bianconi]{millan2018complex}
Ana~P. Mill{\'a}n, Joaqu{\'i}n~J. Torres, and Ginestra Bianconi.
\newblock Complex network geometry and frustrated synchronization.
\newblock \emph{Sci. Rep.}, 8\penalty0 (1):\penalty0 9910, 2018.

\bibitem[Gong and Pikovsky(2019)]{gong2019low}
Chen~Chris Gong and Arkady Pikovsky.
\newblock Low-dimensional dynamics for higher-order harmonic, globally coupled
phase-oscillator ensembles.
\newblock \emph{Phys. Rev. E}, 100\penalty0 (6):\penalty0 062210, 2019.

\bibitem[Rosenblum and Pikovsky(2007)]{rosenblum2007self}
Michael Rosenblum and Arkady Pikovsky.
\newblock Self-organized quasiperiodicity in oscillator ensembles with global
nonlinear coupling.
\newblock \emph{Phys. Rev. Lett.}, 98\penalty0 (6):\penalty0 064101, 2007.

\bibitem[Pikovsky and Rosenblum(2009)]{pikovsky2009self}
Arkady Pikovsky and Michael Rosenblum.
\newblock Self-organized partially synchronous dynamics in populations of
nonlinearly coupled oscillators.
\newblock \emph{Phys. D}, 238\penalty0 (1):\penalty0 27--37, 2009.

\bibitem[Burylko and Pikovsky(2011)]{burylko2011desynchronization}
Oleksandr Burylko and Arkady Pikovsky.
\newblock Desynchronization transitions in nonlinearly coupled phase
oscillators.
\newblock \emph{Phys. D}, 240\penalty0 (17):\penalty0 1352--1361, 2011.

\bibitem[Nakao(2016)]{nakao2016phase}
Hiroya Nakao.
\newblock Phase reduction approach to synchronisation of nonlinear oscillators.
\newblock \emph{Contemp. Phys.}, 57\penalty0 (2):\penalty0 188--214, 2016.

\bibitem[Pietras and Daffertshofer(2019)]{pietras2019network}
Bastian Pietras and Andreas Daffertshofer.
\newblock Network dynamics of coupled oscillators and phase reduction
techniques.
\newblock \emph{Phys. Rep.}, 2019.

\bibitem[Ashwin et~al.(2016)Ashwin, Bick, and Burylko]{ashwin2016identical}
Peter Ashwin, Christian Bick, and Oleksandr Burylko.
\newblock Identical phase oscillator networks: Bifurcations, symmetry and
reversibility for generalized coupling.
\newblock \emph{Front Appl Math Stat}, 2:\penalty0 7, 2016.

\bibitem[Matheny et~al.(2019)Matheny, Emenheiser, Fon, Chapman, Salova, Rohden,
Li, {de Badyn}, P{\'o}sfai, {Duenas-Osorio}, et~al.]{matheny2019exotic}
Matthew~H Matheny, Jeffrey Emenheiser, Warren Fon, Airlie Chapman, Anastasiya
Salova, Martin Rohden, Jarvis Li, Mathias~Hudoba {de Badyn}, M{\'a}rton
P{\'o}sfai, Leonardo {Duenas-Osorio}, et~al.
\newblock Exotic states in a simple network of nanoelectromechanical
oscillators.
\newblock \emph{Science}, 363\penalty0 (6431):\penalty0 eaav7932, 2019.

\bibitem[Bick et~al.(2016)Bick, Ashwin, and Rodrigues]{bick2016chaos}
Christian Bick, Peter Ashwin, and Ana Rodrigues.
\newblock Chaos in generically coupled phase oscillator networks with
nonpairwise interactions.
\newblock \emph{Chaos}, 26\penalty0 (9):\penalty0 094814, 2016.

\bibitem[Bick(2018)]{bick2018heteroclinic}
Christian Bick.
\newblock Heteroclinic switching between chimeras.
\newblock \emph{Phys. Rev. E}, 97\penalty0 (5):\penalty0 050201, 2018.

\bibitem[Bick(2019)]{bick2019heteroclinic}
Christian Bick.
\newblock Heteroclinic dynamics of localized frequency synchrony:
{{Heteroclinic}} cycles for small populations.
\newblock \emph{J Nonlin Sci}, 2019.

\bibitem[Bick and Lohse(2019)]{bick2019heteroclinic2}
Christian Bick and Alexander Lohse.
\newblock Heteroclinic dynamics of localized frequency synchrony: {{Stability}}
of heteroclinic cycles and networks.
\newblock \emph{J Nonlin Sci}, 2019.

\bibitem[Bick and Ashwin(2016)]{bick2016chaotic}
Christian Bick and Peter Ashwin.
\newblock Chaotic weak chimeras and their persistence in coupled populations of
phase oscillators.
\newblock \emph{Nonlinearity}, 29\penalty0 (5):\penalty0 1468, 2016.

\bibitem[Komarov and Pikovsky(2013)]{komarov2013dynamics}
Maxim Komarov and Arkady Pikovsky.
\newblock Dynamics of multifrequency oscillator communities.
\newblock \emph{Phys. Rev. Lett.}, 110\penalty0 (13):\penalty0 134101, 2013.

\bibitem[Rosenblum and Pikovsky(2019)]{rosenblum2019numerical}
Michael Rosenblum and Arkady Pikovsky.
\newblock Numerical phase reduction beyond the first order approximation.
\newblock \emph{Chaos}, 29\penalty0 (1):\penalty0 011105, 2019.

\bibitem[Pecora and Carroll(1990)]{pecora1990synchronization}
Louis~M Pecora and Thomas~L Carroll.
\newblock Synchronization in chaotic systems.
\newblock \emph{Phys. Rev. Lett.}, 64\penalty0 (8):\penalty0 821, 1990.

\bibitem[Rosenblum et~al.(1996)Rosenblum, Pikovsky, and
Kurths]{rosenblum1996phase}
Michael~G Rosenblum, Arkady~S Pikovsky, and J{\"u}rgen Kurths.
\newblock Phase synchronization of chaotic oscillators.
\newblock \emph{Phys. Rev. Lett.}, 76\penalty0 (11):\penalty0 1804, 1996.

\bibitem[Wu(1998)]{wu1998synchronization}
Chai~Wah Wu.
\newblock Synchronization in arrays of chaotic circuits coupled via
hypergraphs: {{Static}} and dynamic coupling.
\newblock In \emph{{{ISCAS}}'98. {{Proceedings}} of the 1998 {{IEEE}}
    International Symposium on Circuits and Systems (Cat. {{No}}.
    {{98CH36187}})}, volume~3, pages 287--290. {IEEE}, 1998.

\bibitem[Krawiecki(2014)]{krawiecki2014chaotic}
A~Krawiecki.
\newblock Chaotic synchronization on complex hypergraphs.
\newblock \emph{Chaos Solitons Fractals}, 65:\penalty0 44--50, 2014.

\bibitem[Gambuzza et~al.(2020)Gambuzza, Di~Patti, Gallo, Lepri, Romance,
Criado, Frasca, Latora, and Boccaletti]{gambuzza2020master}
LV~Gambuzza, F~Di~Patti, L~Gallo, S~Lepri, M~Romance, R~Criado, M~Frasca,
V~Latora, and S~Boccaletti.
\newblock The master stability function for synchronization in simplicial
complexes.
\newblock \emph{arXiv:2004.03913}, 2020.

\bibitem[Lodato et~al.(2007)Lodato, Boccaletti, and
Latora]{lodato2007synchronization}
Ivano Lodato, Stefano Boccaletti, and Vito Latora.
\newblock Synchronization properties of network motifs.
\newblock \emph{Europhys. Lett.}, 78\penalty0 (2):\penalty0 28001, 2007.

\bibitem[Soriano et~al.(2012)Soriano, {Van der Sande}, Fischer, and
Mirasso]{soriano2012synchronization}
Miguel~C Soriano, Guy {Van der Sande}, Ingo Fischer, and Claudio~R Mirasso.
\newblock Synchronization in simple network motifs with negligible correlation
and mutual information measures.
\newblock \emph{Phys. Rev. Lett.}, 108\penalty0 (13):\penalty0 134101, 2012.

\bibitem[Krishnagopal et~al.(2017)Krishnagopal, Lehnert, Poel, Zakharova, and
Sch{\"o}ll]{krishnagopal2017synchronization}
Sanjukta Krishnagopal, Judith Lehnert, Winnie Poel, Anna Zakharova, and
Eckehard Sch{\"o}ll.
\newblock Synchronization patterns: From network motifs to hierarchical
networks.
\newblock \emph{Philos. Trans. Royal Soc. A}, 375\penalty0 (2088):\penalty0
20160216, 2017.

\bibitem[Amritkar et~al.(2005)Amritkar, Jalan, and
Hu]{amritkar2005synchronized}
RE~Amritkar, Sarika Jalan, and Chin-Kun Hu.
\newblock Synchronized clusters in coupled map networks. {{II}}. {{Stability}}
analysis.
\newblock \emph{Phys. Rev. E}, 72\penalty0 (1):\penalty0 016212, 2005.

\bibitem[Pecora and Carroll(1998)]{pecora1998master}
Louis~M Pecora and Thomas~L Carroll.
\newblock Master stability functions for synchronized coupled systems.
\newblock \emph{Phys. Rev. Lett.}, 80\penalty0 (10):\penalty0 2109, 1998.

\bibitem[Englert et~al.(2011)Englert, Heiligenthal, Kinzel, and
Kanter]{englert2011synchronization}
A~Englert, S~Heiligenthal, W~Kinzel, and I~Kanter.
\newblock Synchronization of chaotic networks with time-delayed couplings:
{{An}} analytic study.
\newblock \emph{Phys. Rev. E}, 83\penalty0 (4):\penalty0 046222, 2011.

\bibitem[Sorrentino and Ott(2007)]{sorrentino2007network}
Francesco Sorrentino and Edward Ott.
\newblock Network synchronization of groups.
\newblock \emph{Phys Rev E}, 76\penalty0 (5):\penalty0 056114, 2007.

\bibitem[Koseska et~al.(2013)Koseska, Volkov, and
Kurths]{koseska2013oscillation}
Aneta Koseska, Evgeny Volkov, and J{\"u}rgen Kurths.
\newblock Oscillation quenching mechanisms: {{Amplitude}} vs. oscillation
death.
\newblock \emph{Phys. Rep.}, 531\penalty0 (4):\penalty0 173--199, 2013.

\bibitem[Mulas et~al.(2020)Mulas, Kuehn, and Jost]{mulas2020coupled}
Raffaella Mulas, Christian Kuehn, and J{\"u}rgen Jost.
\newblock Coupled dynamics on hypergraphs: {{Master}} stability of steady
states and synchronization.
\newblock \emph{arXiv:2003.13775}, 2020.

\bibitem[Dayan et~al.(2001)Dayan, Abbott, and Abbott]{dayan2001theoretical}
Peter Dayan, Laurence~F Abbott, and L~Abbott.
\newblock Theoretical neuroscience: Computational and mathematical modeling of
neural systems.
\newblock 2001.

\bibitem[Gerstner and Kistler(2002)]{gerstner2002spiking}
Wulfram Gerstner and Werner~M Kistler.
\newblock \emph{Spiking Neuron Models: {{Single}} Neurons, Populations,
    Plasticity}.
\newblock {Cambridge university press}, 2002.

\bibitem[Bian and Yao(2011)]{bian2011adaptive}
Qiuxiang Bian and Hongxing Yao.
\newblock Adaptive synchronization of bipartite dynamical networks with
distributed delays and nonlinear derivative coupling.
\newblock \emph{Commun Nonlinear Sci Numer Simulat}, 16\penalty0 (10):\penalty0
4089--4098, 2011.

\bibitem[Shilnikov et~al.(2008)Shilnikov, Gordon, and
Belykh]{shilnikov2008polyrhythmic}
Andrey Shilnikov, Ren{\'e} Gordon, and Igor Belykh.
\newblock Polyrhythmic synchronization in bursting networking motifs.
\newblock \emph{Chaos}, 18\penalty0 (3):\penalty0 037120, 2008.

\bibitem[Matias et~al.(2011)Matias, Carelli, Mirasso, and
Copelli]{matias2011anticipated}
Fernanda~S Matias, Pedro~V Carelli, Claudio~R Mirasso, and Mauro Copelli.
\newblock Anticipated synchronization in a biologically plausible model of
neuronal motifs.
\newblock \emph{Phys. Rev. E}, 84\penalty0 (2):\penalty0 021922, 2011.

\bibitem[Gollo et~al.(2014)Gollo, Mirasso, Sporns, and
Breakspear]{gollo2014mechanisms}
Leonardo~L Gollo, Claudio Mirasso, Olaf Sporns, and Michael Breakspear.
\newblock Mechanisms of zero-lag synchronization in cortical motifs.
\newblock \emph{PLoS Comput. Biol.}, 10\penalty0 (4):\penalty0 e1003548, 2014.

\bibitem[Smirnov and Andrzejak(2005)]{smirnov2005detection}
Dmitry~A. Smirnov and Ralph~G. Andrzejak.
\newblock Detection of weak directional coupling: {{Phase}}-{{Dynamics}}
approach versus state-space approach.
\newblock \emph{Phys. Rev. E}, 71\penalty0 (3):\penalty0 036207, 2005.

\bibitem[Frenzel and Pompe(2007)]{frenzel2007partial}
Stefan Frenzel and Bernd Pompe.
\newblock Partial {{Mutual Information}} for {{Coupling Analysis}} of
{{Multivariate Time Series}}.
\newblock \emph{Phys. Rev. Lett.}, 99\penalty0 (20):\penalty0 204101, 2007.

\bibitem[Rosenblum and Pikovsky(2001)]{rosenblum2001detecting}
Michael~G. Rosenblum and Arkady~S. Pikovsky.
\newblock Detecting direction of coupling in interacting oscillators.
\newblock \emph{Phys. Rev. E}, 64\penalty0 (4):\penalty0 045202, 2001.

\bibitem[Kralemann et~al.(2011)Kralemann, Pikovsky, and
Rosenblum]{kralemann2011reconstructing}
Bj{\"o}rn Kralemann, Arkady Pikovsky, and Michael Rosenblum.
\newblock Reconstructing phase dynamics of oscillator networks.
\newblock \emph{Chaos}, 21\penalty0 (2):\penalty0 025104, 2011.

\bibitem[Kralemann et~al.(2014)Kralemann, Pikovsky, and
Rosenblum]{kralemann2014reconstructing}
Bj{\"o}rn Kralemann, Arkady Pikovsky, and Michael Rosenblum.
\newblock Reconstructing effective phase connectivity of oscillator networks
from observations.
\newblock \emph{New J. Phys.}, 16\penalty0 (8):\penalty0 085013, 2014.

\bibitem[Kralemann et~al.(2008)Kralemann, Cimponeriu, Rosenblum, Pikovsky, and
Mrowka]{kralemann2008phase}
Bj{\"o}rn Kralemann, Laura Cimponeriu, Michael Rosenblum, Arkady Pikovsky, and
Ralf Mrowka.
\newblock Phase dynamics of coupled oscillators reconstructed from data.
\newblock \emph{Phys. Rev. E}, 77\penalty0 (6):\penalty0 066205, 2008.

\bibitem[Tass et~al.(1998)Tass, Rosenblum, Weule, Kurths, Pikovsky, Volkmann,
Schnitzler, and Freund]{tass1998detection}
P.~Tass, M.~G. Rosenblum, J.~Weule, J.~Kurths, A.~Pikovsky, J.~Volkmann,
A.~Schnitzler, and H.-J. Freund.
\newblock Detection of n:m {{Phase Locking}} from {{Noisy Data}}:
{{Application}} to {{Magnetoencephalography}}.
\newblock \emph{Phys. Rev. Lett.}, 81\penalty0 (15):\penalty0 3291--3294, 1998.

\bibitem[Kralemann et~al.(2013)Kralemann, Pikovsky, and
Rosenblum]{kralemann2013detecting}
Bj{\"o}rn Kralemann, Arkady Pikovsky, and Michael Rosenblum.
\newblock Detecting triplet locking by triplet synchronization indices.
\newblock \emph{Phys. Rev. E}, 87\penalty0 (5):\penalty0 052904, 2013.

\bibitem[Jia et~al.(2015)Jia, Song, Liu, Kurths, and Xiao]{jia2015experimental}
Ji~Jia, Zhiwen Song, Weiqing Liu, J{\"u}rgen Kurths, and Jinghua Xiao.
\newblock Experimental study of the triplet synchronization of coupled
nonidentical mechanical metronomes.
\newblock \emph{Sci. Rep.}, 5:\penalty0 17008, 2015.

\bibitem[Duggento et~al.(2012)Duggento, Stankovski, McClintock, and
Stefanovska]{duggento2012dynamical}
Andrea Duggento, Tomislav Stankovski, Peter~VE McClintock, and Aneta
Stefanovska.
\newblock Dynamical {{Bayesian}} inference of time-evolving interactions:
{{From}} a pair of coupled oscillators to networks of oscillators.
\newblock \emph{Phys. Rev. E}, 86\penalty0 (6):\penalty0 061126, 2012.

\bibitem[{Pastor-Satorras} and Vespignani(2001)]{pastor2001epidemic}
Romualdo {Pastor-Satorras} and Alessandro Vespignani.
\newblock Epidemic spreading in scale-free networks.
\newblock \emph{Phys. Rev. Lett.}, 86\penalty0 (14):\penalty0 3200, 2001.

\bibitem[{Pastor-Satorras} et~al.(2015){Pastor-Satorras}, Castellano,
Van~Mieghem, and Vespignani]{pastor2015epidemic}
Romualdo {Pastor-Satorras}, Claudio Castellano, Piet Van~Mieghem, and
Alessandro Vespignani.
\newblock Epidemic processes in complex networks.
\newblock \emph{Rev. Mod. Phys.}, 87\penalty0 (3):\penalty0 925, 2015.

\bibitem[Centola(2018)]{centola2018behavior}
Damon Centola.
\newblock \emph{How behavior spreads: The science of complex contagions},
volume~3.
\newblock Princeton University Press, 2018.

\bibitem[Sen and Chakrabarti(2014)]{sen2014sociophysics}
Parongama Sen and Bikas~K Chakrabarti.
\newblock \emph{Sociophysics: An Introduction}.
\newblock {Oxford University Press}, 2014.

\bibitem[Castellano et~al.(2009)Castellano, Fortunato, and
Loreto]{castellano2009statistical}
Claudio Castellano, Santo Fortunato, and Vittorio Loreto.
\newblock Statistical physics of social dynamics.
\newblock \emph{Rev. Mod. Phys.}, 81\penalty0 (2):\penalty0 591, 2009.

\bibitem[Baronchelli(2018)]{baronchelli2018emergence}
Andrea Baronchelli.
\newblock The emergence of consensus: A primer.
\newblock \emph{R. Soc Open Sci}, 5\penalty0 (2):\penalty0 172189, 2018.

\bibitem[Kermack and McKendrick(1927)]{kermack1927contribution}
William~Ogilvy Kermack and Anderson~G McKendrick.
\newblock A contribution to the mathematical theory of epidemics.
\newblock \emph{Proc. R. Soc. Lond. A}, 115\penalty0 (772):\penalty0 700--721,
1927.

\bibitem[Anderson and May(1992)]{anderson1992infectious}
Roy~M Anderson and Robert~M May.
\newblock \emph{Infectious Diseases of Humans: Dynamics and Control}.
\newblock {Oxford university press}, 1992.

\bibitem[Hethcote(2000)]{hethcote2000mathematics}
Herbert~W Hethcote.
\newblock The mathematics of infectious diseases.
\newblock \emph{SIAM Rev.}, 42\penalty0 (4):\penalty0 599--653, 2000.

\bibitem[Zhang et~al.(2017{\natexlab{a}})Zhang, Sun, Chinazzi, {y Piontti},
Dean, Rojas, Merler, Mistry, Poletti, Rossi, et~al.]{zhang2017spread}
Qian Zhang, Kaiyuan Sun, Matteo Chinazzi, Ana~Pastore {y Piontti}, Natalie~E
Dean, Diana~Patricia Rojas, Stefano Merler, Dina Mistry, Piero Poletti, Luca
Rossi, et~al.
\newblock Spread of {{Zika}} virus in the {{Americas}}.
\newblock \emph{Proc. Natl. Acad. Sci. U. S. A.}, 114\penalty0 (22):\penalty0
E4334--E4343, 2017{\natexlab{a}}.

\bibitem[{y Piontti} et~al.(2018){y Piontti}, Perra, Rossi, Samay, and
Vespignani]{y2018charting}
Ana~Pastore {y Piontti}, Nicola Perra, Luca Rossi, Nicole Samay, and Alessandro
Vespignani.
\newblock \emph{Charting the next Pandemic: {{Modeling}} Infectious Disease
    Spreading in the Data Science Age}.
\newblock {Springer}, 2018.

\bibitem[Viboud and Vespignani(2019)]{viboud2019future}
C{\'e}cile Viboud and Alessandro Vespignani.
\newblock The future of influenza forecasts.
\newblock \emph{Proc. Natl. Acad. Sci. U. S. A.}, 116\penalty0 (8):\penalty0
2802--2804, 2019.

\bibitem[Kucharski et~al.(2020)Kucharski, Russell, Diamond, Liu, Edmunds, Funk,
Eggo, Sun, Jit, Munday, et~al.]{kucharski2020early}
Adam~J Kucharski, Timothy~W Russell, Charlie Diamond, Yang Liu, John Edmunds,
Sebastian Funk, Rosalind~M Eggo, Fiona Sun, Mark Jit, James~D Munday, et~al.
\newblock Early dynamics of transmission and control of {{COVID}}-19: A
mathematical modelling study.
\newblock \emph{Lancet Infect. Dis.}, 2020.

\bibitem[Kraemer et~al.(2020)Kraemer, Yang, Gutierrez, Wu, Klein, Pigott, {du
    Plessis}, Faria, Li, Hanage, Brownstein, Layan, Vespignani, Tian, Dye, Pybus,
and Scarpino]{Kraemereabb4218}
Moritz U.~G. Kraemer, Chia-Hung Yang, Bernardo Gutierrez, Chieh-Hsi Wu, Brennan
Klein, David~M. Pigott, Louis {du Plessis}, Nuno~R. Faria, Ruoran Li,
William~P. Hanage, John~S. Brownstein, Maylis Layan, Alessandro Vespignani,
Huaiyu Tian, Christopher Dye, Oliver~G. Pybus, and Samuel~V. Scarpino.
\newblock The effect of human mobility and control measures on the {{COVID}}-19
epidemic in {{China}}.
\newblock \emph{Science}, 2020.

\bibitem[Gleeson(2011)]{gleeson2011high}
James~P Gleeson.
\newblock High-accuracy approximation of binary-state dynamics on networks.
\newblock \emph{Phys. Rev. Lett.}, 107\penalty0 (6):\penalty0 068701, 2011.

\bibitem[Gleeson(2013)]{gleeson2013binary}
James~P Gleeson.
\newblock Binary-state dynamics on complex networks: {{Pair}} approximation and
beyond.
\newblock \emph{Phys. Rev. X}, 3\penalty0 (2):\penalty0 021004, 2013.

\bibitem[Wang et~al.(2017)Wang, Tang, Stanley, and
Braunstein]{wang2017unification}
Wei Wang, Ming Tang, H~Eugene Stanley, and Lidia~A Braunstein.
\newblock Unification of theoretical approaches for epidemic spreading on
complex networks.
\newblock \emph{Rep. Prog. Phys.}, 80\penalty0 (3):\penalty0 036603, 2017.

\bibitem[Kiss et~al.(2017)Kiss, Miller, Simon, et~al.]{kiss2017mathematics}
Istv{\'a}n~Z Kiss, Joel~C Miller, P{\'e}ter~L Simon, et~al.
\newblock Mathematics of epidemics on networks.
\newblock \emph{Cham Springer}, 2017.

\bibitem[Daley and Kendall(1964)]{daley1964epidemics}
Daryl~J Daley and David~G Kendall.
\newblock Epidemics and rumours.
\newblock \emph{Nature}, 204\penalty0 (4963):\penalty0 1118--1118, 1964.

\bibitem[Bass(1969)]{bass1969new}
Frank~M Bass.
\newblock A new product growth for model consumer durables.
\newblock \emph{Manag Sci}, 15\penalty0 (5):\penalty0 215--227, 1969.

\bibitem[Bikhchandani et~al.(1992)Bikhchandani, Hirshleifer, and
Welch]{bikhchandani1992theory}
Sushil Bikhchandani, David Hirshleifer, and Ivo Welch.
\newblock A theory of fads, fashion, custom, and cultural change as
informational cascades.
\newblock \emph{J Polit. Econ}, 100\penalty0 (5):\penalty0 992--1026, 1992.

\bibitem[Rogers(2010)]{rogers2010diffusion}
Everett~M Rogers.
\newblock \emph{Diffusion of Innovations}.
\newblock {Simon and Schuster}, 2010.

\bibitem[Centola and Macy(2007)]{centola2007complex}
Damon Centola and Michael Macy.
\newblock Complex contagions and the weakness of long ties.
\newblock \emph{Am. J. Sociol.}, 113\penalty0 (3):\penalty0 702--734, 2007.

\bibitem[Guilbeault et~al.(2018)Guilbeault, Becker, and
Centola]{guilbeault2018complex}
Douglas Guilbeault, Joshua Becker, and Damon Centola.
\newblock Complex contagions: {{A}} decade in review.
\newblock In \emph{Complex Spreading Phenomena in Social Systems}, pages 3--25.
{Springer}, 2018.

\bibitem[Kee et~al.(2013)Kee, Sparks, Struppa, and Mannucci]{kee2013social}
Kerk~F Kee, Lisa Sparks, Daniele~C Struppa, and Mirco Mannucci.
\newblock Social groups, social media, and higher dimensional social
structures: {{A}} simplicial model of social aggregation for computational
communication research.
\newblock \emph{Commun Q}, 61\penalty0 (1):\penalty0 35--58, 2013.

\bibitem[{TfL}(2008)]{sociopatterns}
{TfL}.
\newblock {{SocioPatterns}} collaboration.
\newblock 2008.

\bibitem[Cisneros-Velarde and Bullo(2020)]{cisneros2020multi}
Pedro Cisneros-Velarde and Francesco Bullo.
\newblock Multi-group sis epidemics with simplicial and higher-order
interactions.
\newblock \emph{arXiv:2005.11404}, 2020.

\bibitem[G{\'o}mez et~al.(2010)G{\'o}mez, Arenas, {Borge-Holthoefer}, Meloni,
and Moreno]{gomez2010discrete}
Sergio G{\'o}mez, Alexandre Arenas, J~{Borge-Holthoefer}, Sandro Meloni, and
Yamir Moreno.
\newblock Discrete-time {{Markov}} chain approach to contact-based disease
spreading in complex networks.
\newblock \emph{Europhys. Lett.}, 89\penalty0 (3):\penalty0 38009, 2010.

\bibitem[Matamalas et~al.(2018)Matamalas, Arenas, and
G{\'o}mez]{matamalas2018effective}
Joan~T Matamalas, Alex Arenas, and Sergio G{\'o}mez.
\newblock Effective approach to epidemic containment using link equations in
complex networks.
\newblock \emph{Sci. Adv.}, 4\penalty0 (12):\penalty0 eaau4212, 2018.

\bibitem[Matamalas et~al.(2020)Matamalas, G{\'o}mez, and
Arenas]{matamalas2020abrupt}
Joan~T. Matamalas, Sergio G{\'o}mez, and Alex Arenas.
\newblock Abrupt phase transition of epidemic spreading in simplicial
complexes.
\newblock \emph{Phys. Rev. Research}, 2\penalty0 (1):\penalty0 012049, 2020.

\bibitem[Girvan and Newman(2002)]{girvan2002community}
Michelle Girvan and M.~E.~J Newman.
\newblock Community structure in social and biological networks.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A.}, 99\penalty0 (12):\penalty0
7821--7826, 2002.

\bibitem[Newman and Park(2003)]{newman2003social}
M.~E.~J Newman and Juyong Park.
\newblock Why social networks are different from other types of networks.
\newblock \emph{Phys. Rev. E}, 68\penalty0 (3):\penalty0 036122, 2003.

\bibitem[Miller(2009{\natexlab{b}})]{miller2009spread}
Joel~C Miller.
\newblock Spread of infectious disease through clustered populations.
\newblock \emph{J R. Soc Interface}, 6\penalty0 (41):\penalty0 1121--1134,
2009{\natexlab{b}}.

\bibitem[Ritchie et~al.(2014)Ritchie, Berthouze, House, and
Kiss]{ritchie2014higher}
Martin Ritchie, Luc Berthouze, Thomas House, and Istvan~Z Kiss.
\newblock Higher-order structure and epidemic dynamics in clustered networks.
\newblock \emph{J. Theor. Biol.}, 348:\penalty0 21--32, 2014.

\bibitem[O'Sullivan et~al.(2015)O'Sullivan, O'Keeffe, Fennell, and
Gleeson]{o2015mathematical}
David~JP O'Sullivan, Gary~James O'Keeffe, Peter~G Fennell, and James~P Gleeson.
\newblock Mathematical modeling of complex contagion on clustered networks.
\newblock \emph{Front. Phys.}, 3:\penalty0 71, 2015.

\bibitem[H{\'e}bert-Dufresne and Althouse(2015)]{hebert2015complexPNAS}
Laurent H{\'e}bert-Dufresne and Benjamin~M Althouse.
\newblock Complex dynamics of synergistic coinfections on realistically
clustered networks.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A}, 112\penalty0 (33):\penalty0
10551--10556, 2015.

\bibitem[{St-Onge} et~al.(2020){St-Onge}, Thibeault, Allard, Dub{\'e}, and
{H{\'e}bert-Dufresne}]{stonge2020master}
Guillaume {St-Onge}, Vincent Thibeault, Antoine Allard, Louis~J. Dub{\'e}, and
Laurent {H{\'e}bert-Dufresne}.
\newblock Master equation analysis of mesoscopic localization in contagion
dynamics on higher-order networks.
\newblock 2020.

\bibitem[H{\'e}bert-Dufresne et~al.(2020)H{\'e}bert-Dufresne, Mistry, and
Althouse]{hebert2020spread}
Laurent H{\'e}bert-Dufresne, Dina Mistry, and Benjamin~M Althouse.
\newblock Spread of infectious disease and social awareness as parasitic
contagions on clustered networks.
\newblock \emph{arXiv:2003.10604}, 2020.

\bibitem[Yang et~al.(2015)Yang, Hu, and Liu]{yang2015knowledge}
Guang-Yong Yang, Zhao-Long Hu, and Jian-Guo Liu.
\newblock Knowledge diffusion in the collaboration hypernetwork.
\newblock \emph{Physica A}, 419:\penalty0 429--436, 2015.

\bibitem[Wang et~al.(2015{\natexlab{a}})Wang, Guo, Yang, and
Liu]{wang2015improved}
Jiang-Pan Wang, Qiang Guo, Guang-Yong Yang, and Jian-Guo Liu.
\newblock Improved knowledge diffusion model based on the collaboration
hypernetwork.
\newblock \emph{Physica A}, 428:\penalty0 250--256, 2015{\natexlab{a}}.

\bibitem[Peng et~al.(2019)Peng, Wang, Zhang, and Huang]{peng2019hypernetwork}
Gongzhuang Peng, Hongwei Wang, Heming Zhang, and Keke Huang.
\newblock A hypernetwork-based approach to collaborative retrieval and
reasoning of engineering design knowledge.
\newblock \emph{Adv. Eng. Software}, 42:\penalty0 100956, 2019.

\bibitem[Bod{\'o} et~al.(2016)Bod{\'o}, Katona, and Simon]{bodo2016sis}
{\'A}gnes Bod{\'o}, Gyula~Y Katona, and P{\'e}ter~L Simon.
\newblock {{SIS}} epidemic propagation on hypergraphs.
\newblock \emph{Bull. Math. Biol.}, 78\penalty0 (4):\penalty0 713--735, 2016.

\bibitem[Ghoshal et~al.(2004)Ghoshal, Sander, and Sokolov]{ghoshal2004sis}
G~Ghoshal, LM~Sander, and IM~Sokolov.
\newblock Sis epidemics with household structure: the self-consistent field
method.
\newblock \emph{Math. Bio.}, 190\penalty0 (1):\penalty0 71--85, 2004.

\bibitem[House and Keeling(2008)]{house2008deterministic}
Thomas House and Matt~J Keeling.
\newblock Deterministic epidemic models with explicit household structure.
\newblock \emph{Math. Biosci.}, 213\penalty0 (1):\penalty0 29--39, 2008.

\bibitem[Ball et~al.(2015)Ball, Britton, House, Isham, Mollison, Pellis, and
Tomba]{ball2015seven}
Frank Ball, Tom Britton, Thomas House, Valerie Isham, Denis Mollison, Lorenzo
Pellis, and Gianpaolo~Scalia Tomba.
\newblock Seven challenges for metapopulation models of epidemics, including
households models.
\newblock \emph{Epidemics}, 10:\penalty0 63--67, 2015.

\bibitem[Granovetter(1978)]{granovetter1978threshold}
Mark Granovetter.
\newblock Threshold models of collective behavior.
\newblock \emph{Am. J. Sociol.}, 83\penalty0 (6):\penalty0 1420--1443, 1978.

\bibitem[Karsai et~al.(2014)Karsai, Iniguez, Kaski, and
Kert{\'e}sz]{karsai2014complex}
M{\'a}rton Karsai, Gerardo Iniguez, Kimmo Kaski, and J{\'a}nos Kert{\'e}sz.
\newblock Complex contagion process in spreading of online innovation.
\newblock \emph{J. R. Soc. Interface}, 11\penalty0 (101):\penalty0 20140694,
2014.

\bibitem[Suo et~al.(2018)Suo, Guo, and Shen]{suo2018information}
Qi~Suo, Jin-Li Guo, and Ai-Zhong Shen.
\newblock Information spreading dynamics in hypernetworks.
\newblock \emph{Phys. A}, 495:\penalty0 475--487, 2018.

\bibitem[Jhun et~al.(2019)Jhun, Jo, and Kahng]{jhun2019simplicial}
Bukyoung Jhun, Minjae Jo, and B~Kahng.
\newblock Simplicial {{SIS}} model in scale-free uniform hypergraph.
\newblock \emph{J. Stat. Mech.: Theory Exp.}, 2019\penalty0 (12):\penalty0
123207, 2019.

\bibitem[L{\"u}beck(2004)]{lubeck2004universal}
Sven L{\"u}beck.
\newblock Universal scaling behavior of non-equilibrium phase transitions.
\newblock \emph{Int. J. Mod. Phys. B}, 18\penalty0 (31n32):\penalty0
3977--4118, 2004.

\bibitem[Ferreira et~al.(2012)Ferreira, Castellano, and
{Pastor-Satorras}]{ferreira2012epidemic}
Silvio~C Ferreira, Claudio Castellano, and Romualdo {Pastor-Satorras}.
\newblock Epidemic thresholds of the susceptible-infected-susceptible model on
networks: {{A}} comparison of numerical and theoretical results.
\newblock \emph{Phys. Rev. E}, 86\penalty0 (4):\penalty0 041125, 2012.

\bibitem[de~Arruda et~al.(2020)de~Arruda, Tizzani, and Moreno]{de2020phase}
Guilherme~Ferraz de~Arruda, Michele Tizzani, and Yamir Moreno.
\newblock Phase transitions and stability of dynamical processes on
hypergraphs.
\newblock \emph{arXiv:2005.10891}, 2020.

\bibitem[Dahlerup(1988)]{dahlerup1988small}
Drude Dahlerup.
\newblock From a small to a large minority: Women in {{Scandinavian}} politics.
\newblock \emph{Scand Polit. Stud}, 11\penalty0 (4):\penalty0 275--298, 1988.

\bibitem[Grey(2006)]{grey2006numbers}
Sandra Grey.
\newblock Numbers and beyond: {{The}} relevance of critical mass in gender
research.
\newblock \emph{Polit. Gend.}, 2\penalty0 (4):\penalty0 492--502, 2006.

\bibitem[Centola et~al.(2018)Centola, Becker, Brackbill, and
Baronchelli]{centola2018experimental}
Damon Centola, Joshua Becker, Devon Brackbill, and Andrea Baronchelli.
\newblock Experimental evidence for tipping points in social convention.
\newblock \emph{Science}, 360\penalty0 (6393):\penalty0 1116--1119, 2018.

\bibitem[Ma and Guo(2018)]{ma2018study}
Tao Ma and Jinli Guo.
\newblock Study on information transmission model of enterprise informal
organizations based on the hypernetwork.
\newblock \emph{Chin. J. Phys.}, 56\penalty0 (5):\penalty0 2424--2438, 2018.

\bibitem[Dietz(1967)]{dietz1967epidemics}
Klaus Dietz.
\newblock Epidemics and rumours: {{A}} survey.
\newblock \emph{J R. Stat Soc}, 130\penalty0 (4):\penalty0 505--528, 1967.

\bibitem[Moreno et~al.(2004)Moreno, Nekovee, and Pacheco]{moreno2004dynamics}
Yamir Moreno, Maziar Nekovee, and Amalio~F Pacheco.
\newblock Dynamics of rumor spreading in complex networks.
\newblock \emph{Phys. Rev. E}, 69\penalty0 (6):\penalty0 066130, 2004.

\bibitem[Liggett(2012)]{liggett2012interacting}
Thomas~Milton Liggett.
\newblock \emph{Interacting Particle Systems}, volume 276.
\newblock {Springer Science \& Business Media}, 2012.

\bibitem[Shao et~al.(2009)Shao, Havlin, and Stanley]{shao2009dynamic}
Jia Shao, Shlomo Havlin, and H~Eugene Stanley.
\newblock Dynamic opinion model and invasion percolation.
\newblock \emph{Phys. Rev. Lett.}, 103\penalty0 (1):\penalty0 018701, 2009.

\bibitem[Suchecki et~al.(2004)Suchecki, Eguiluz, and
San~Miguel]{suchecki2004conservation}
Krzysztof Suchecki, Victor~M Eguiluz, and Maxi San~Miguel.
\newblock Conservation laws for the voter model in complex networks.
\newblock \emph{Europhys. Lett.}, 69\penalty0 (2):\penalty0 228, 2004.

\bibitem[Suchecki et~al.(2005)Suchecki, Egu{\'i}luz, and
San~Miguel]{suchecki2005voter}
Krzysztof Suchecki, V{\'i}ctor~M Egu{\'i}luz, and Maxi San~Miguel.
\newblock Voter model dynamics in complex networks: {{Role}} of dimensionality,
disorder, and degree distribution.
\newblock \emph{Phys. Rev. E}, 72\penalty0 (3):\penalty0 036132, 2005.

\bibitem[Diakonova et~al.(2016)Diakonova, Nicosia, Latora, and
San~Miguel]{diakonova2016irreducibility}
Marina Diakonova, Vincenzo Nicosia, Vito Latora, and Maxi San~Miguel.
\newblock Irreducibility of multilayer network dynamics: The case of the voter
model.
\newblock \emph{New J. Phys.}, 18\penalty0 (2):\penalty0 023010, 2016.

\bibitem[{Fern{\'a}ndez-Gracia} et~al.(2014){Fern{\'a}ndez-Gracia}, Suchecki,
Ramasco, San~Miguel, and Egu{\'i}luz]{fernandez2014voter}
Juan {Fern{\'a}ndez-Gracia}, Krzysztof Suchecki, Jos{\'e}~J Ramasco, Maxi
San~Miguel, and V{\'i}ctor~M Egu{\'i}luz.
\newblock Is the voter model a model for voters?
\newblock \emph{Phys. Rev. Lett.}, 112\penalty0 (15):\penalty0 158701, 2014.

\bibitem[Kearns et~al.(2006)Kearns, Suri, and Montfort]{kearns2006experimental}
Michael Kearns, Siddharth Suri, and Nick Montfort.
\newblock An experimental study of the coloring problem on human subject
networks.
\newblock \emph{Science}, 313\penalty0 (5788):\penalty0 824--827, 2006.

\bibitem[Judd et~al.(2010)Judd, Kearns, and Vorobeychik]{judd2010behavioral}
Stephen Judd, Michael Kearns, and Yevgeniy Vorobeychik.
\newblock Behavioral dynamics and influence in networked coloring and
consensus.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A.}, 107\penalty0 (34):\penalty0
14978--14982, 2010.

\bibitem[Chung and Tsiatas(2014)]{chung2014hypergraph}
Fan Chung and Alexander Tsiatas.
\newblock Hypergraph coloring games and voter models.
\newblock \emph{Internet Math.}, 10\penalty0 (1-2):\penalty0 66--86, 2014.

\bibitem[Redner(2019)]{redner2019reality}
Sidney Redner.
\newblock Reality-inspired voter models: {{A}} mini-review.
\newblock \emph{Comptes Rendus Phys.}, 2019.

\bibitem[Vazquez et~al.(2008)Vazquez, Egu{\'i}luz, and
San~Miguel]{vazquez2008generic}
Federico Vazquez, V{\'i}ctor~M Egu{\'i}luz, and Maxi San~Miguel.
\newblock Generic absorbing transition in coevolution dynamics.
\newblock \emph{Phys. Rev. Lett.}, 100\penalty0 (10):\penalty0 108702, 2008.

\bibitem[Horstmeyer and Kuehn(2020)]{horstmeyer2020adaptive}
Leonhard Horstmeyer and Christian Kuehn.
\newblock Adaptive voter model on simplicial complexes.
\newblock \emph{Phys. Rev. E}, 101\penalty0 (2):\penalty0 022305, 2020.

\bibitem[Galam(2002)]{galam2002minority}
Serge Galam.
\newblock Minority opinion spreading in random geometry.
\newblock \emph{Eur. Phys. J. B}, 25\penalty0 (4):\penalty0 403--406, 2002.

\bibitem[Watts(2002)]{watts2002simple}
Duncan~J Watts.
\newblock A simple model of global cascades on random networks.
\newblock \emph{Proc. Natl. Acad. Sci. U.S.A.}, 99\penalty0 (9):\penalty0
5766--5771, 2002.

\bibitem[Lanchier and Neufer(2013)]{lanchier2013stochastic}
Nicolas Lanchier and Jared Neufer.
\newblock Stochastic dynamics on hypergraphs and the spatial majority rule
model.
\newblock \emph{J. Stat. Phys.}, 151\penalty0 (1-2):\penalty0 21--45, 2013.

\bibitem[{de Oliveira}(1992)]{de1992isotropic}
Mario~J {de Oliveira}.
\newblock Isotropic majority-vote model on a square lattice.
\newblock \emph{J. Stat. Phys.}, 66\penalty0 (1-2):\penalty0 273--281, 1992.

\bibitem[Pereira and Moreira(2005)]{pereira2005majority}
Luiz~FC Pereira and FG~Brady Moreira.
\newblock Majority-vote model on random graphs.
\newblock \emph{Phys. Rev. E}, 71\penalty0 (1):\penalty0 016123, 2005.

\bibitem[Campos et~al.(2003)Campos, {de Oliveira}, and
Moreira]{campos2003small}
Paulo~RA Campos, Viviane~M {de Oliveira}, and FG~Brady Moreira.
\newblock Small-world effects in the majority-vote model.
\newblock \emph{Phys. Rev. E}, 67\penalty0 (2):\penalty0 026104, 2003.

\bibitem[Luz and Lima(2007)]{luz2007majority}
Edina~MS Luz and FWS Lima.
\newblock Majority-vote on directed small-world networks.
\newblock \emph{Int. J. Mod. Phys. C}, 18\penalty0 (08):\penalty0 1251--1261,
2007.

\bibitem[Lima(2006)]{lima2006majority}
FWS Lima.
\newblock Majority-vote on directed Barabasi-Albert networks.
\newblock \emph{Int. J. Mod. Phys. C}, 17\penalty0 (09):\penalty0 1257--1265,
2006.

\bibitem[Lima(2007)]{lima2007majority}
FWS Lima.
\newblock Majority-vote on undirected {{Barab{\'a}si}}-{{Albert}} networks.
\newblock \emph{Commun. Comput. Phys.}, 2\penalty0 (2):\penalty0 358--366,
2007.

\bibitem[Gradowski and Krawiecki(2015)]{gradowski2015majority}
Tomasz Gradowski and Andrzej Krawiecki.
\newblock Majority-vote model on scale-free hypergraphs.
\newblock \emph{Acta Phys Pol}, 127\penalty0 (3A):\penalty0 1--4, 2015.

\bibitem[Hong et~al.(2007)Hong, Ha, and Park]{hong2007finite}
Hyunsuk Hong, Meesoon Ha, and Hyunggyu Park.
\newblock Finite-size scaling in complex networks.
\newblock \emph{Phys. Rev. Lett.}, 98\penalty0 (25):\penalty0 258701, 2007.

\bibitem[Deffuant et~al.(2000)Deffuant, Neau, Amblard, and
Weisbuch]{deffuant2000mixing}
Guillaume Deffuant, David Neau, Frederic Amblard, and G{\'e}rard Weisbuch.
\newblock Mixing beliefs among interacting agents.
\newblock \emph{Adv. Complex Syst.}, 3\penalty0 (01n04):\penalty0 87--98, 2000.

\bibitem[Lorenz(2007)]{lorenz2007continuous}
Jan Lorenz.
\newblock Continuous opinion dynamics under bounded confidence: {{A}} survey.
\newblock \emph{Int. J. Mod. Phys. C}, 18\penalty0 (12):\penalty0 1819--1838,
2007.

\bibitem[Asch and Guetzkow(1951)]{asch1951effects}
Solomon~E Asch and Harold Guetzkow.
\newblock Effects of group pressure upon the modification and distortion of
judgments.
\newblock \emph{Doc. Gestalt Psychol.}, pages 222--236, 1951.

\bibitem[Axelrod(1997)]{axelrod1997dissemination}
Robert Axelrod.
\newblock The dissemination of culture: {{A}} model with local convergence and
global polarization.
\newblock \emph{J Confl Resolut}, 41\penalty0 (2):\penalty0 203--226, 1997.

\bibitem[Battiston et~al.(2017{\natexlab{b}})Battiston, Nicosia, Latora, and
San~Miguel]{battiston2017layered}
Federico Battiston, Vincenzo Nicosia, Vito Latora, and Maxi San~Miguel.
\newblock Layered social influence promotes multiculturality in the {{Axelrod}}
model.
\newblock \emph{Sci. Rep.}, 7\penalty0 (1):\penalty0 1809, 2017{\natexlab{b}}.

\bibitem[Maleti{\'c} and Rajkovi{\'c}(2014)]{maletic2014consensus}
Slobodan Maleti{\'c} and Milan Rajkovi{\'c}.
\newblock Consensus formation on a simplicial complex of opinions.
\newblock \emph{Phys. A}, 397:\penalty0 111--120, 2014.

\bibitem[Maleti{\'c} and Zhao(2018)]{maletic2018hidden}
Slobodan Maleti{\'c} and Yi~Zhao.
\newblock Hidden multidimensional social structure modeling applied to biased
social perception.
\newblock \emph{Phys. A}, 492:\penalty0 1419--1430, 2018.

\bibitem[Roca et~al.(2009)Roca, Cuesta, and S{\'a}nchez]{roca2009evolutionary}
Carlos~P Roca, Jos{\'e}~A Cuesta, and Angel S{\'a}nchez.
\newblock Evolutionary game theory: Temporal and spatial effects beyond
replicator dynamics.
\newblock \emph{Physics of life reviews}, 6\penalty0 (4):\penalty0 208--249,
2009.

\bibitem[Szab{\'o} et~al.(2004)Szab{\'o}, Szolnoki, and
Izs{\'a}k]{szabo2004rock}
Gy{\"o}rgy Szab{\'o}, Attila Szolnoki, and Rudolf Izs{\'a}k.
\newblock Rock-scissors-paper game on regular small-world networks.
\newblock \emph{J. Phys. Math. Gen.}, 37\penalty0 (7):\penalty0 2599, 2004.

\bibitem[Szolnoki et~al.(2014)Szolnoki, Mobilia, Jiang, Szczesny, Rucklidge,
and Perc]{szolnoki2014cyclic}
Attila Szolnoki, Mauro Mobilia, Luo-Luo Jiang, Bartosz Szczesny, Alastair~M
Rucklidge, and Matja{\v{z}} Perc.
\newblock Cyclic dominance in evolutionary games: a review.
\newblock \emph{Journal of the Royal Society Interface}, 11\penalty0
(100):\penalty0 20140735, 2014.

\bibitem[Axelrod and Axelrod(1984)]{axelrod1984evolution}
R.~Axelrod and R.M. Axelrod.
\newblock \emph{The Evolution of Cooperation}.
\newblock Basic Books. {Basic Books}, 1984.
\newblock ISBN 978-0-465-02121-5.

\bibitem[Rapoport and Guyer(1966)]{rapoport1966taxonomy}
A.~Rapoport and M.~Guyer.
\newblock \emph{A Taxonomy of 2 x 2 Games, by Anatol Rapoport and Melvin
    Guyer}.
\newblock Bobbs-Merrill Reprint Series in the Social Sciences, {{S617}}. 1966.

\bibitem[Rousseau(1997)]{rousseau1997discourses}
Jean-Jacques Rousseau.
\newblock The discourses and other political writings.
\newblock 1997.

\bibitem[Luce and Raiffa(1957)]{luce1957games}
RD~Luce and H~Raiffa.
\newblock Games and decisions: {{Introduction}} and critical survey, 2012 ed.
\newblock 1957.

\bibitem[Gui and Sugden(2005)]{gui2005economics}
Benedetto Gui and Robert Sugden.
\newblock \emph{Economics and Social Interaction: {{Accounting}} for
    Interpersonal Relations}.
\newblock {Cambridge University Press}, 2005.

\bibitem[Smith(1982)]{smith1982evolution}
John~Maynard Smith.
\newblock \emph{Evolution and the Theory of Games}.
\newblock {Cambridge university press}, 1982.

\bibitem[Smith and Parker(1976)]{smith1976logic}
John~Maynard Smith and Geoffrey~A Parker.
\newblock The logic of asymmetric contests.
\newblock \emph{Anim. Behav.}, 24\penalty0 (1):\penalty0 159--175, 1976.

\bibitem[Cressman(1995)]{cressman1995evolutionary}
R~Cressman.
\newblock Evolutionary stability for two-stage hawk-dove games.
\newblock \emph{Rocky Mt. J. Math.}, pages 145--155, 1995.

\bibitem[Smith(1972)]{smith1972game}
J~Maynard Smith.
\newblock Game theory and the evolution of fighting.
\newblock \emph{Evol.}, pages 8--28, 1972.

\bibitem[Diederich and Opper(1989)]{diederich1989replicators}
Sigurd Diederich and Manfred Opper.
\newblock Replicators with random interactions: {{A}} solvable model.
\newblock \emph{Phys. Rev. A}, 39\penalty0 (8):\penalty0 4333, 1989.

\bibitem[Hofbauer and Sigmund(1998)]{hofbauer1998evolutionary}
Josef Hofbauer and Karl Sigmund.
\newblock \emph{Evolutionary Games and Population Dynamics}.
\newblock {Cambridge university press}, 1998.

\bibitem[Opper and Diederich(1999)]{opper1999replicator}
Manfred Opper and Sigurd Diederich.
\newblock Replicator dynamics.
\newblock \emph{Comput. Phys. Commun.}, 121:\penalty0 141--144, 1999.

\bibitem[Chawanya and Tokita(2002)]{chawanya2002large}
Tsuyoshi Chawanya and Kei Tokita.
\newblock Large-dimensional replicator equations with antisymmetric random
interactions.
\newblock \emph{J. Phys. Soc. Jpn.}, 71\penalty0 (2):\penalty0 429--431, 2002.

\bibitem[Perc and Szolnoki(2010)]{perc2010coevolutionary}
Matja{\v{z}} Perc and Attila Szolnoki.
\newblock Coevolutionary gamesa mini review.
\newblock \emph{BioSystems}, 99\penalty0 (2):\penalty0 109--125, 2010.

\bibitem[Hardin(1968)]{hardin1968tragedy}
Garrett Hardin.
\newblock The tragedy of the commons.
\newblock \emph{science}, 162\penalty0 (3859):\penalty0 1243--1248, 1968.

\bibitem[Nowak and May(1992)]{nowak1992evolutionary}
Martin~A Nowak and Robert~M May.
\newblock Evolutionary games and spatial chaos.
\newblock \emph{Nature}, 359\penalty0 (6398):\penalty0 826--829, 1992.

\bibitem[Santos and Pacheco(2005)]{santos2005scale}
Francisco~C Santos and Jorge~M Pacheco.
\newblock Scale-free networks provide a unifying framework for the emergence of
cooperation.
\newblock \emph{Phys. Rev. Lett.}, 95\penalty0 (9):\penalty0 098104, 2005.

\bibitem[{G{\'o}mez-Gardenes} et~al.(2007){G{\'o}mez-Gardenes}, Campillo,
Flor{\'i}a, and Moreno]{gomez2007dynamical}
Jes{\'u}s {G{\'o}mez-Gardenes}, M~Campillo, LM~Flor{\'i}a, and Yamir Moreno.
\newblock Dynamical organization of cooperation in complex topologies.
\newblock \emph{Phys. Rev. Lett.}, 98\penalty0 (10):\penalty0 108103, 2007.

\bibitem[Assenza et~al.(2008)Assenza, {G{\'o}mez-Garde{\~n}es}, and
Latora]{assenza2008enhancement}
Salvatore Assenza, Jes{\'u}s {G{\'o}mez-Garde{\~n}es}, and Vito Latora.
\newblock Enhancement of cooperation in highly clustered scale-free networks.
\newblock \emph{Phys. Rev. E}, 78\penalty0 (1):\penalty0 017101, 2008.

\bibitem[Hauert and Doebeli(2004)]{hauert2004spatial}
Christoph Hauert and Michael Doebeli.
\newblock Spatial structure often inhibits the evolution of cooperation in the
snowdrift game.
\newblock \emph{Nature}, 428\penalty0 (6983):\penalty0 643--646, 2004.

\bibitem[Nowak(2006)]{nowak2006five}
Martin~A Nowak.
\newblock Five rules for the evolution of cooperation.
\newblock \emph{Science}, 314\penalty0 (5805):\penalty0 1560--1563, 2006.

\bibitem[Szab{\'o} and Fath(2007)]{szabo2007evolutionary}
Gy{\"o}rgy Szab{\'o} and Gabor Fath.
\newblock Evolutionary games on graphs.
\newblock \emph{Phys. Rep.}, 446\penalty0 (4-6):\penalty0 97--216, 2007.

\bibitem[Wang et~al.(2015{\natexlab{b}})Wang, Wang, Szolnoki, and
Perc]{wang2015evolutionary}
Zhen Wang, Lin Wang, Attila Szolnoki, and Matja{\v{z}} Perc.
\newblock Evolutionary games on multilayer networks: a colloquium.
\newblock \emph{The European physical journal B}, 88\penalty0 (5):\penalty0
124, 2015{\natexlab{b}}.

\bibitem[Sigmund(2010)]{sigmund2010calculus}
Karl Sigmund.
\newblock \emph{The Calculus of Selfishness}, volume~6.
\newblock {Princeton University Press}, 2010.

\bibitem[Archetti and Scheuring(2012)]{archetti2012review}
M~Archetti and I~Scheuring.
\newblock Review: {{Evolution}} of cooperation in one-shot social dilemmas
without assortment.
\newblock \emph{J Theor Biol}, 299:\penalty0 9--20, 2012.

\bibitem[Perc et~al.(2013)Perc, {G{\'o}mez-Garde{\~n}es}, Szolnoki, Flor{\'i}a,
and Moreno]{perc2013evolutionary}
Matja{\v z} Perc, Jes{\'u}s {G{\'o}mez-Garde{\~n}es}, Attila Szolnoki, Luis~M
Flor{\'i}a, and Yamir Moreno.
\newblock Evolutionary dynamics of group interactions on structured
populations: A review.
\newblock \emph{J. R. Soc. Interface}, 10\penalty0 (80):\penalty0 20120997,
2013.

\bibitem[Perc et~al.(2017)Perc, Jordan, Rand, Wang, Boccaletti, and
Szolnoki]{perc2017statistical}
Matja{\v{z}} Perc, Jillian~J Jordan, David~G Rand, Zhen Wang, Stefano
Boccaletti, and Attila Szolnoki.
\newblock Statistical physics of human cooperation.
\newblock \emph{Physics Reports}, 687:\penalty0 1--51, 2017.

\bibitem[Pe{\~n}a et~al.(2016)Pe{\~n}a, Wu, Arranz, and
Traulsen]{pena2016evolutionary}
Jorge Pe{\~n}a, Bin Wu, Jordi Arranz, and Arne Traulsen.
\newblock Evolutionary games of multiplayer cooperation on graphs.
\newblock \emph{PLoS Comput. Biol.}, 12\penalty0 (8), 2016.

\bibitem[Szab{\'o} and Hauert(2002)]{szabo2002phase}
Gy{\"o}rgy Szab{\'o} and Christoph Hauert.
\newblock Phase transitions and volunteering in spatial public goods games.
\newblock \emph{Phys. Rev. Lett.}, 89\penalty0 (11):\penalty0 118101, 2002.

\bibitem[Brandt et~al.(2003)Brandt, Hauert, and Sigmund]{brandt2003punishment}
Hannelore Brandt, Christoph Hauert, and Karl Sigmund.
\newblock Punishment and reputation in spatial public goods games.
\newblock \emph{Proc R Soc Lond B}, 270\penalty0 (1519):\penalty0 1099--1104,
2003.

\bibitem[Santos et~al.(2008)Santos, Santos, and Pacheco]{santos2008social}
Francisco~C Santos, Marta~D Santos, and Jorge~M Pacheco.
\newblock Social diversity promotes the emergence of cooperation in public
goods games.
\newblock \emph{Nature}, 454\penalty0 (7201):\penalty0 213--216, 2008.

\bibitem[Rong and Wu(2009)]{rong2009effect}
Zhihai Rong and Zhi-Xi Wu.
\newblock Effect of the degree correlation in public goods game on scale-free
networks.
\newblock \emph{Europhys. Lett.}, 87\penalty0 (3):\penalty0 30001, 2009.

\bibitem[Rong et~al.(2010)Rong, Yang, Wang, et~al.]{rong2010feedback}
Zhihai Rong, Han-Xin Yang, Wen-Xu Wang, et~al.
\newblock Feedback reciprocity mechanism promotes the cooperation of highly
clustered scale-free networks.
\newblock \emph{Phys. Rev. E}, 82\penalty0 (4):\penalty0 047101, 2010.

\bibitem[Gao et~al.(2010)Gao, Li, Wu, and Wang]{gao2010diversity}
Jia Gao, Zhi Li, Te~Wu, and Long Wang.
\newblock Diversity of contribution promotes cooperation in public goods games.
\newblock \emph{Phys. A}, 389\penalty0 (16):\penalty0 3166--3171, 2010.

\bibitem[Vukov et~al.(2011)Vukov, Santos, and Pacheco]{vukov2011escaping}
Jeromos Vukov, Francisco~C Santos, and Jorge~M Pacheco.
\newblock Escaping the tragedy of the commons via directed investments.
\newblock \emph{J. Theor. Biol.}, 287:\penalty0 37--41, 2011.

\bibitem[Szolnoki and Perc(2011)]{szolnoki2011group}
Attila Szolnoki and Matja{\v z} Perc.
\newblock Group-size effects on the evolution of cooperation in the spatial
public goods game.
\newblock \emph{Phys. Rev. E}, 84\penalty0 (4):\penalty0 047102, 2011.

\bibitem[Perc and Grigolini(2013)]{perc2013collective}
Matja Perc and Paolo Grigolini.
\newblock Collective behavior and evolutionary games  an introduction.
\newblock \emph{Chaos, Solitons \& Fractals}, 56:\penalty0 1 -- 5, 2013.
\newblock ISSN 0960-0779.
\newblock Collective Behavior and Evolutionary Games.

\bibitem[Szolnoki et~al.(2009)Szolnoki, Perc, and
Szab{\'o}]{szolnoki2009topology}
Attila Szolnoki, Matja{\v z} Perc, and Gy{\"o}rgy Szab{\'o}.
\newblock {Topology-independent impact of noise on cooperation in spatial
    public goods games}.
\newblock \emph{Physical Review E}, 80:\penalty0 056109, 2009.
\newblock \doi{10.1103/PhysRevE.80.056109}.

\bibitem[Szolnoki and Perc(2013)]{szolnoki2013correlation}
Attila Szolnoki and Matja{\v z} Perc.
\newblock {Correlation of positive and negative reciprocity fails to confer an
    evolutionary advantage: Phase transitions to elementary strategies}.
\newblock \emph{Physical Review X}, 3:\penalty0 041021, 2013.
\newblock \doi{10.1103/PhysRevX.3.041021}.

\bibitem[Helbing et~al.(2010)Helbing, Szolnoki, Perc, and
Szab{\'o}]{helbing2010evolutionary}
Dirk Helbing, Attila Szolnoki, Matja{\v z} Perc, and Gy{\"o}rgy Szab{\'o}.
\newblock {Evolutionary establishment of moral and double moral standards
    through spatial interactions}.
\newblock \emph{PLoS Computational Biology}, 6:\penalty0 e1000758, 2010.
\newblock \doi{10.1371/journal.pcbi.1000758}.

\bibitem[Wang et~al.(2012)Wang, Szolnoki, and Perc]{wang2012evolution}
Zhen Wang, Attila Szolnoki, and Matja{\v z} Perc.
\newblock Evolution of public cooperation on interdependent networks: {{The}}
impact of biased utility functions.
\newblock \emph{Europhys. Lett.}, 97\penalty0 (4):\penalty0 48001, 2012.

\bibitem[Wang et~al.(2013{\natexlab{b}})Wang, Szolnoki, and
Perc]{wang2013interdependent}
Zhen Wang, Attila Szolnoki, and Matja{\v z} Perc.
\newblock Interdependent network reciprocity in evolutionary games.
\newblock \emph{Sci. Rep.}, 3:\penalty0 1183, 2013{\natexlab{b}}.

\bibitem[Battiston et~al.(2014)Battiston, Nicosia, and
Latora]{battiston2014structural}
Federico Battiston, Vincenzo Nicosia, and Vito Latora.
\newblock Structural measures for multiplex networks.
\newblock \emph{Phys. Rev. E}, 89\penalty0 (3):\penalty0 032804, 2014.

\bibitem[Battiston et~al.(2017{\natexlab{c}})Battiston, Perc, and
Latora]{battiston2017determinants}
Federico Battiston, Matja{\v z} Perc, and Vito Latora.
\newblock Determinants of public cooperation in multiplex networks.
\newblock \emph{New J. Phys.}, 19\penalty0 (7):\penalty0 073017,
2017{\natexlab{c}}.

\bibitem[Roca and Helbing(2011)]{roca2011emergence}
Carlos~P Roca and Dirk Helbing.
\newblock Emergence of social cohesion in a model society of greedy, mobile
individuals.
\newblock \emph{Proceedings of the National Academy of Sciences}, 108\penalty0
(28):\penalty0 11370--11374, 2011.

\bibitem[Pichler and Shapiro(2017)]{pichler2017public}
Elgar Pichler and Avi~M Shapiro.
\newblock Public goods games on adaptive coevolutionary networks.
\newblock \emph{Chaos: An Interdisciplinary Journal of Nonlinear Science},
27\penalty0 (7):\penalty0 073107, 2017.

\bibitem[Ren et~al.(2018)Ren, Liu, Feng, and He]{ren2018coevolution}
Guangming Ren, Lan Liu, Mingku Feng, and Yingji He.
\newblock Coevolution of public goods game and networks based on survival of
the fittest.
\newblock \emph{PloS one}, 13\penalty0 (9), 2018.

\bibitem[Shen et~al.(2018{\natexlab{a}})Shen, Chu, Shi, Jusup, Perc, and
Wang]{shen2018coevolutionary}
Chen Shen, Chen Chu, Lei Shi, Marko Jusup, Matja{\v{z}} Perc, and Zhen Wang.
\newblock Coevolutionary resolution of the public goods dilemma in
interdependent structured populations.
\newblock \emph{EPL (Europhysics Letters)}, 124\penalty0 (4):\penalty0 48003,
2018{\natexlab{a}}.

\bibitem[Perc(2018)]{perc2018stability}
Matja{\v z} Perc.
\newblock {Stability of subsystem solutions in agent-based models}.
\newblock \emph{European Journal of Physics}, 39:\penalty0 014001, 2018.
\newblock \doi{10.1088/1361-6404/aa903d}.

\bibitem[Javarone and Battiston(2016)]{javarone2016role}
Marco~Alberto Javarone and Federico Battiston.
\newblock The role of noise in the spatial public goods game.
\newblock \emph{Journal of Statistical Mechanics: Theory and Experiment},
2016\penalty0 (7):\penalty0 073404, 2016.

\bibitem[Zheng et~al.(2007)Zheng, Yin, Chan, and Hui]{zheng2007cooperative}
Da-Fang Zheng, HP~Yin, Chun-Him Chan, and PM~Hui.
\newblock Cooperative behavior in a model of evolutionary snowdrift games with
{{N}}-person interactions.
\newblock \emph{Europhys. Lett.}, 80\penalty0 (1):\penalty0 18002, 2007.

\bibitem[Santos et~al.(2012)Santos, Pinheiro, Santos, and
Pacheco]{santos2012dynamics}
Marta~D Santos, Flavio~L Pinheiro, Francisco~C Santos, and Jorge~M Pacheco.
\newblock Dynamics of {{N}}-person snowdrift games in structured populations.
\newblock \emph{J. Theor. Biol.}, 315:\penalty0 81--86, 2012.

\bibitem[Ji et~al.(2011)Ji, Kim, Jung, Park, Choi, Kim, Hwang, Lee, Hwang, and
Jeong]{ji2011effect}
Kwang~Hwan Ji, Ji-In Kim, Hong~Yoon Jung, Se~Yeob Park, Rino Choi, Un~Ki Kim,
Cheol~Seong Hwang, Daeseok Lee, Hyungsang Hwang, and Jae~Kyeong Jeong.
\newblock Effect of high-pressure oxygen annealing on negative bias
illumination stress-induced instability of {{InGaZnO}} thin film transistors.
\newblock \emph{Appl. Phys. Lett.}, 98\penalty0 (10):\penalty0 103509, 2011.

\bibitem[Pacheco et~al.(2009)Pacheco, Santos, Souza, and
Skyrms]{pacheco2009evolutionary}
Jorge~M Pacheco, Francisco~C Santos, Max~O Souza, and Brian Skyrms.
\newblock Evolutionary dynamics of collective action in {{N}}-person stag hunt
dilemmas.
\newblock \emph{Proc. R. Soc. B Biol. Sci.}, 276\penalty0 (1655):\penalty0
315--321, 2009.

\bibitem[Souza et~al.(2009)Souza, Pacheco, and Santos]{souza2009evolution}
Max~O Souza, Jorge~M Pacheco, and Francisco~C Santos.
\newblock Evolution of cooperation under {{N}}-person snowdrift games.
\newblock \emph{J. Theor. Biol.}, 260\penalty0 (4):\penalty0 581--588, 2009.

\bibitem[Santos and Pacheco(2011)]{santos2011risk}
Francisco~C Santos and Jorge~M Pacheco.
\newblock Risk of collective failure provides an escape from the tragedy of the
commons.
\newblock \emph{Proc. Natl. Acad. Sci.}, 108\penalty0 (26):\penalty0
10421--10425, 2011.

\bibitem[Chen et~al.(2017)Chen, {Gracia-L{\'a}zaro}, Li, Wang, and
Moreno]{chen2017evolutionary}
Wei Chen, Carlos {Gracia-L{\'a}zaro}, Zhiwu Li, Long Wang, and Yamir Moreno.
\newblock Evolutionary dynamics of n-person hawk-dove games.
\newblock \emph{Sci. Rep.}, 7\penalty0 (1):\penalty0 1--10, 2017.

\bibitem[G{\"u}th et~al.(1982)G{\"u}th, Schmittberger, and
Schwarze]{guth1982experimental}
Werner G{\"u}th, Rolf Schmittberger, and Bernd Schwarze.
\newblock An experimental analysis of ultimatum bargaining.
\newblock \emph{Journal of economic behavior \& organization}, 3\penalty0
(4):\penalty0 367--388, 1982.

\bibitem[Sinatra et~al.(2009)Sinatra, Iranzo, Gomez-Gardenes, Floria, Latora,
and Moreno]{sinatra2009ultimatum}
Roberta Sinatra, Jaime Iranzo, Jesus Gomez-Gardenes, Luis~M Floria, Vito
Latora, and Yamir Moreno.
\newblock The ultimatum game in complex networks.
\newblock \emph{Journal of Statistical Mechanics: Theory and Experiment},
2009\penalty0 (09):\penalty0 P09012, 2009.

\bibitem[Santos et~al.(2015)Santos, Santos, Paiva, and
Pacheco]{santos2015evolutionary}
Fernando~P Santos, Francisco~C Santos, Ana Paiva, and Jorge~M Pacheco.
\newblock Evolutionary dynamics of group fairness.
\newblock \emph{Journal of theoretical biology}, 378:\penalty0 96--102, 2015.

\bibitem[{Gomez-Gardenes} et~al.(2011){Gomez-Gardenes}, Romance, Criado,
Vilone, and S{\'a}nchez]{gomez2011evolutionary}
Jesus {Gomez-Gardenes}, Miguel Romance, Regino Criado, Daniele Vilone, and
Angel S{\'a}nchez.
\newblock Evolutionary games defined at the network mesoscale: {{The}} public
goods game.
\newblock \emph{Chaos Interdiscip. J. Nonlinear Sci.}, 21\penalty0
(1):\penalty0 016113, 2011.

\bibitem[{G{\'o}mez-Garde{\~n}es} et~al.(2011){G{\'o}mez-Garde{\~n}es}, Vilone,
and S{\'a}nchez]{gomez2011disentangling}
Jes{\'u}s {G{\'o}mez-Garde{\~n}es}, Daniele Vilone, and Angel S{\'a}nchez.
\newblock Disentangling social and group heterogeneities: {{Public}} goods
games on complex networks.
\newblock \emph{Europhys. Lett.}, 95\penalty0 (6):\penalty0 68003, 2011.

\bibitem[Pe{\~n}a and Rochat(2012)]{pena2012bipartite}
Jorge Pe{\~n}a and Yannick Rochat.
\newblock Bipartite graphs as models of population structures in evolutionary
multiplayer games.
\newblock \emph{PLOS ONE}, 7\penalty0 (9), 2012.

\bibitem[{Gracia-Lazaro} et~al.(2014){Gracia-Lazaro}, {Gomez-Gardenes}, Floria,
and Moreno]{gracia2014intergroup}
Carlos {Gracia-Lazaro}, Jesus {Gomez-Gardenes}, Luis~Mario Floria, and Yamir
Moreno.
\newblock Intergroup information exchange drives cooperation in the public
goods game.
\newblock \emph{Phys. Rev. E}, 90\penalty0 (4):\penalty0 042808, 2014.

\bibitem[{Alvarez-Rodriguez} et~al.(2020){Alvarez-Rodriguez}, Battiston, {de
    Arruda}, Moreno, Perc, and Latora]{alvarez2020evolutionary}
Unai {Alvarez-Rodriguez}, Federico Battiston, Guilherme~Ferraz {de Arruda},
Yamir Moreno, Matjaz Perc, and Vito Latora.
\newblock Evolutionary dynamics of higher-order interactions.
\newblock \emph{arXiv:2001.10313}, 2020.

\bibitem[Baronchelli et~al.(2006{\natexlab{a}})Baronchelli, Felici, Loreto,
Caglioti, and Steels]{baronchelli2006sharp}
Andrea Baronchelli, Maddalena Felici, Vittorio Loreto, Emanuele Caglioti, and
Luc Steels.
\newblock Sharp transition towards shared vocabularies in multi-agent systems.
\newblock \emph{Journal of Statistical Mechanics: Theory and Experiment},
2006\penalty0 (06):\penalty0 P06014, 2006{\natexlab{a}}.

\bibitem[Baronchelli et~al.(2006{\natexlab{b}})Baronchelli, DallAsta,
Barrat, and Loreto]{baronchelli2006topology}
Andrea Baronchelli, Luca DallAsta, Alain Barrat, and Vittorio Loreto.
\newblock Topology-induced coarsening in language games.
\newblock \emph{Physical Review E}, 73\penalty0 (1):\penalty0 015102,
2006{\natexlab{b}}.

\bibitem[Gneezy(2005)]{gneezy2005deception}
Uri Gneezy.
\newblock Deception: The role of consequences.
\newblock \emph{American Economic Review}, 95\penalty0 (1):\penalty0 384--394,
2005.

\bibitem[Capraro et~al.(2019)Capraro, Perc, and Vilone]{capraro2019evolution}
Valerio Capraro, Matja{\v z} Perc, and Daniele Vilone.
\newblock {The evolution of lying in well-mixed populations}.
\newblock \emph{Journal of the Royal Society Interface}, 16:\penalty0 20190211,
2019.
\newblock \doi{10.1098/rsif.2019.0211}.

\bibitem[Capraro et~al.(2020)Capraro, Perc, and Vilone]{capraro2020lying}
Valerio Capraro, Matja{\v z} Perc, and Daniele Vilone.
\newblock {Lying on networks: The role of structure and topology in promoting
    honesty}.
\newblock \emph{Physical Review E}, 101:\penalty0 032305, 2020.
\newblock \doi{10.1103/PhysRevE.101.032305}.

\bibitem[Milinski et~al.(2008)Milinski, Sommerfeld, Krambeck, Reed, and
Marotzke]{milinski2008collective}
Manfred Milinski, Ralf~D Sommerfeld, Hans-J{\"u}rgen Krambeck, Floyd~A Reed,
and Jochem Marotzke.
\newblock The collective-risk social dilemma and the prevention of simulated
dangerous climate change.
\newblock \emph{Proceedings of the National Academy of Sciences}, 105\penalty0
(7):\penalty0 2291--2294, 2008.

\bibitem[Freeman(1980)]{freeman1980qanalysis}
Linton~C. Freeman.
\newblock Q-analysis and the structure of friendship networks.
\newblock \emph{Int. J. Man-Mach. Stud.}, 12\penalty0 (4):\penalty0 367--378,
1980.

\bibitem[Andjelkovi{\'c} et~al.(2015)Andjelkovi{\'c}, Tadi{\'c}, Maleti{\'c},
and Rajkovi{\'c}]{andjelkovic2015hierarchical}
Miroslav Andjelkovi{\'c}, Bosiljka Tadi{\'c}, Slobodan Maleti{\'c}, and Milan
Rajkovi{\'c}.
\newblock Hierarchical sequencing of online social graphs.
\newblock \emph{Phys. A}, 436:\penalty0 582--595, 2015.

\bibitem[Mangan and Alon(2003)]{mangan2003feedforward}
S.~Mangan and U.~Alon.
\newblock Structure and function of the feed-forward loop network motif.
\newblock \emph{Proc. Natl. Acad. Sci.}, 100\penalty0 (21):\penalty0
11980--11985, 2003.

\bibitem[Kuzmin et~al.(2018)Kuzmin, VanderSluis, Wang, Tan, Deshpande, Chen,
Usaj, Balint, Mattiazzi~Usaj, {van Leeuwen}, Koch, Pons, Dagilis, Pryszlak,
Wang, Hanchard, Riggi, Xu, Heydari, San~Luis, Shuteriqi, Zhu, Van~Dyk,
Sharifpoor, Costanzo, Loewith, Caudy, Bolnick, Brown, Andrews, Boone, and
Myers]{kuzmin2018threegenic}
Elena Kuzmin, Benjamin VanderSluis, Wen Wang, Guihong Tan, Raamesh Deshpande,
Yiqun Chen, Matej Usaj, Attila Balint, Mojca Mattiazzi~Usaj, Jolanda {van
    Leeuwen}, Elizabeth~N. Koch, Carles Pons, Andrius~J. Dagilis, Michael
Pryszlak, Jason Zi~Yang Wang, Julia Hanchard, Margot Riggi, Kaicong Xu, Hamed
Heydari, Bryan-Joseph San~Luis, Ermira Shuteriqi, Hongwei Zhu, Nydia Van~Dyk,
Sara Sharifpoor, Michael Costanzo, Robbie Loewith, Amy Caudy, Daniel Bolnick,
Grant~W. Brown, Brenda~J. Andrews, Charles Boone, and Chad~L. Myers.
\newblock Systematic analysis of complex genetic interactions.
\newblock \emph{Science}, 360\penalty0 (6386), 2018.

\bibitem[Schneidman et~al.(2003)Schneidman, Still, Berry, Bialek,
et~al.]{schneidman2003network}
Elad Schneidman, Susanne Still, Michael~J Berry, William Bialek, et~al.
\newblock Network information and connected correlations.
\newblock \emph{Phys. Rev. Lett.}, 91\penalty0 (23):\penalty0 238701, 2003.

\bibitem[Petri et~al.(2014)Petri, Expert, Turkheimer, {Carhart-Harris}, Nutt,
Hellyer, and Vaccarino]{petri2014homological}
Giovanni Petri, Paul Expert, Federico Turkheimer, Robin {Carhart-Harris}, David
Nutt, Peter~J Hellyer, and Francesco Vaccarino.
\newblock Homological scaffolds of brain functional networks.
\newblock \emph{J. R. Soc. Interface}, 11\penalty0 (101):\penalty0 20140873,
2014.

\bibitem[{Ib{\'a}{\~n}ez-Marcelo}
et~al.(2019{\natexlab{a}}){Ib{\'a}{\~n}ez-Marcelo}, Campioni, Phinyomark,
Petri, and Santarcangelo]{ibanez2019topology}
Esther {Ib{\'a}{\~n}ez-Marcelo}, Lisa Campioni, Angkoon Phinyomark, Giovanni
Petri, and Enrica~L Santarcangelo.
\newblock Topology highlights mesoscopic functional equivalence between imagery
and perception: {{The}} case of hypnotizability.
\newblock \emph{NeuroImage}, 200:\penalty0 437--449, 2019{\natexlab{a}}.

\bibitem[McPherson(1982)]{mcpherson1982_hyper}
J.Miller McPherson.
\newblock Hypernetwork sampling: {{Duality}} and differentiation among
voluntary organizations.
\newblock \emph{Soc. Netw.}, 3\penalty0 (4):\penalty0 225--249, 1982.

\bibitem[Foster and Seidman(1982)]{foster1982urban}
Brian Foster and Stephen Seidman.
\newblock Urban structures derived from collections of overlapping subsets.
\newblock \emph{Urban Anthropol.}, 11:\penalty0 177--192, 1982.

\bibitem[Foster and Seidman(1984)]{foster1984thai}
B.L. Foster and Stephen Seidman.
\newblock Overlap structure of ceremonial events in two {{Thai}} villages.
\newblock \emph{Thai J. Dev. Adm.}, 24:\penalty0 143--157, 1984.

\bibitem[Faust(1997)]{faust1997centralityaff}
Katherine Faust.
\newblock Centrality in affiliation networks.
\newblock \emph{Soc. Netw.}, 19\penalty0 (2):\penalty0 157--191, 1997.

\bibitem[Bonacich(1987)]{bonacich1987power}
Phillip Bonacich.
\newblock Power and centrality: {{A}} family of measures.
\newblock \emph{Am. J. Sociol.}, 92\penalty0 (5):\penalty0 1170--1182, 1987.

\bibitem[Wylie(1976)]{wylie_1976}
S.~Wylie.
\newblock Mathematical structure in human affairs, by {{R}}. {{H}}. {{Atkin}}.
\newblock \emph{Math. Gaz.}, 60\penalty0 (411):\penalty0 69--70, 1976.

\bibitem[Doreian(1979)]{doreian1979evolution}
Patrick Doreian.
\newblock On the evolution of group and network structure.
\newblock \emph{Soc. Netw.}, 2\penalty0 (3):\penalty0 235--252, 1979.

\bibitem[Gould and Gatrell(1979)]{gould1977liverpool}
Peter Gould and Anthony Gatrell.
\newblock A structural analysis of a game: {{The Liverpool}} v {{Manchester}}
united cup final of 1977.
\newblock \emph{Soc. Netw.}, 2\penalty0 (3):\penalty0 253--273, 1979.

\bibitem[Pappalardo et~al.(2019)Pappalardo, Cintia, Rossi, Massucco, Ferragina,
Pedreschi, and Giannotti]{pappalardo2019soccer}
Luca Pappalardo, Paolo Cintia, Alessio Rossi, Emanuele Massucco, Paolo
Ferragina, Dino Pedreschi, and Fosca Giannotti.
\newblock A public data set of spatio-temporal match events in soccer
competitions.
\newblock \emph{Sci. Data}, 6\penalty0 (1):\penalty0 236, 2019.

\bibitem[Gao and Li(2018)]{gao2019privacy}
Tianchong Gao and Feng Li.
\newblock Studying the utility preservation in social network anonymization via
persistent homology.
\newblock \emph{Comput. Secur.}, 77:\penalty0 49--64, 2018.

\bibitem[Catutto et~al.(2007)Catutto, Schmitz, Baldassarri, Servedio, Loreto,
Hotho, Grahl, and Stumme]{cattuto2007folksonomies}
Ciro Catutto, Christoph Schmitz, Andrea Baldassarri, Vito D.~P. Servedio,
Vittorio Loreto, {and}~Andreas Hotho, Miranda Grahl, and Gerd Stumme.
\newblock Network properties of folksonomies.
\newblock \emph{AI Commun. J. Spec. Issue Netw. Anal. Nat. Sci. Eng.}, 2007.

\bibitem[Latora et~al.(2013)Latora, Nicosia, and
Panzarasa]{latora2013simmelian}
Vito Latora, Vincenzo Nicosia, and Pietro Panzarasa.
\newblock Social cohesion, structural holes, and a tale of two measures.
\newblock \emph{J Stat Phys}, \penalty0 (151):\penalty0 745--764, 2013.

\bibitem[Milojevi{\'c}(2014)]{milojevic2014teams}
Sta{\v s}a Milojevi{\'c}.
\newblock Principles of scientific research team formation and evolution.
\newblock \emph{Proc. Natl. Acad. Sci.}, 111\penalty0 (11):\penalty0
3984--3989, 2014.

\bibitem[Xiao(2016)]{xiao2016node}
Quan Xiao.
\newblock Node importance measure for scientific research collaboration from
hypernetwork perspective.
\newblock \emph{Teh. Vjesn.}, 23\penalty0 (2):\penalty0 397--404, 2016.

\bibitem[Newman(2001{\natexlab{a}})]{newman2001ascientific}
M.~E.~J. Newman.
\newblock Scientific collaboration networks. {{I}}. {{Network}} construction
and fundamental results.
\newblock \emph{Phys. Rev. E}, 64\penalty0 (1):\penalty0 016131,
2001{\natexlab{a}}.

\bibitem[Newman(2001{\natexlab{b}})]{newman2001bscientific}
M.~E.~J. Newman.
\newblock Scientific collaboration networks. {{II}}. {{Shortest}} paths,
weighted networks, and centrality.
\newblock \emph{Phys. Rev. E}, 64\penalty0 (1):\penalty0 016132,
2001{\natexlab{b}}.

\bibitem[Newman(2001{\natexlab{c}})]{newman2001structure}
M.~E.~J. Newman.
\newblock The structure of scientific collaboration networks.
\newblock \emph{Proc. Natl. Acad. Sci.}, 98\penalty0 (2):\penalty0 404--409,
2001{\natexlab{c}}.

\bibitem[Bianconi et~al.(2014)Bianconi, Darst, Iacovacci, and
Fortunato]{bianconi2014triadic}
Ginestra Bianconi, Richard~K Darst, Jacopo Iacovacci, and Santo Fortunato.
\newblock Triadic closure as a basic generating mechanism of communities in
complex networks.
\newblock \emph{Phys. Rev. E}, 90\penalty0 (4):\penalty0 042806, 2014.

\bibitem[Schneidman et~al.(2006)Schneidman, Berry~II, Segev, and
Bialek]{schneidman2006weak}
Elad Schneidman, Michael~J Berry~II, Ronen Segev, and William Bialek.
\newblock Weak pairwise correlations imply strongly correlated network states
in a neural population.
\newblock \emph{Nature}, 440\penalty0 (7087):\penalty0 1007, 2006.

\bibitem[Ganmor et~al.(2011)Ganmor, Segev, and Schneidman]{ganmor2011sparse}
Elad Ganmor, Ronen Segev, and Elad Schneidman.
\newblock Sparse low-order interaction network underlies a highly correlated
and learnable neural population code.
\newblock \emph{Proc. Natl. Acad. Sci.}, 108\penalty0 (23):\penalty0
9679--9684, 2011.

\bibitem[Yu et~al.(2011)Yu, Yang, Nakahara, Santos, Nikoli{\'c}, and
Plenz]{yu2011higher}
Shan Yu, Hongdian Yang, Hiroyuki Nakahara, Gustavo~S Santos, Danko Nikoli{\'c},
and Dietmar Plenz.
\newblock Higher-order interactions characterized in cortical activity.
\newblock \emph{J. Neurosci.}, 31\penalty0 (48):\penalty0 17514--17526, 2011.

\bibitem[Shimazaki et~al.(2012)Shimazaki, Amari, Brown, and
Gr{\"u}n]{shimazaki2012state}
Hideaki Shimazaki, Shun-ichi Amari, Emery~N Brown, and Sonja Gr{\"u}n.
\newblock State-space analysis of time-varying higher-order spike correlation
for multiple neural spike train data.
\newblock \emph{PLoS Comput. Biol.}, 8\penalty0 (3):\penalty0 e1002385, 2012.

\bibitem[K{\"o}ster et~al.(2014)K{\"o}ster, {Sohl-Dickstein}, Gray, and
Olshausen]{koster2014modeling}
Urs K{\"o}ster, Jascha {Sohl-Dickstein}, Charles~M Gray, and Bruno~A Olshausen.
\newblock Modeling higher-order correlations within cortical microcolumns.
\newblock \emph{PLoS Comput. Biol.}, 10\penalty0 (7):\penalty0 e1003684, 2014.

\bibitem[Shimazaki et~al.(2015)Shimazaki, Sadeghi, Ishikawa, Ikegaya, and
Toyoizumi]{shimazaki2015simultaneous}
Hideaki Shimazaki, Kolia Sadeghi, Tomoe Ishikawa, Yuji Ikegaya, and Taro
Toyoizumi.
\newblock Simultaneous silence organizes structured higher-order interactions
in neural populations.
\newblock \emph{Sci. Rep.}, 5:\penalty0 9821, 2015.

\bibitem[{Cayco-Gajic} et~al.(2015){Cayco-Gajic}, Zylberberg, and
{Shea-Brown}]{cayco2015triplet}
Natasha~A {Cayco-Gajic}, Joel Zylberberg, and Eric {Shea-Brown}.
\newblock Triplet correlations among similarly tuned cells impact population
coding.
\newblock \emph{Front. Comput. Neurosci.}, 9:\penalty0 57, 2015.

\bibitem[Giusti et~al.(2015)Giusti, Pastalkova, Curto, and
Itskov]{giusti2015clique}
Chad Giusti, Eva Pastalkova, Carina Curto, and Vladimir Itskov.
\newblock Clique topology reveals intrinsic geometric structure in neural
correlations.
\newblock \emph{Proc. Natl. Acad. Sci.}, 112\penalty0 (44):\penalty0
13455--13460, 2015.

\bibitem[Dabaghian et~al.(2012)Dabaghian, M{\'e}moli, Frank, and
Carlsson]{dabaghian2012topological}
Yuri Dabaghian, Facundo M{\'e}moli, Loren Frank, and Gunnar Carlsson.
\newblock A topological paradigm for hippocampal spatial map formation using
persistent homology.
\newblock \emph{PLoS Comput. Biol.}, 8\penalty0 (8):\penalty0 e1002581, 2012.

\bibitem[Dabaghian et~al.(2014)Dabaghian, Brandt, and
Frank]{dabaghian2014reconceiving}
Yuri Dabaghian, Vicky~L Brandt, and Loren~M Frank.
\newblock Reconceiving the hippocampal map as a topological template.
\newblock \emph{Elife}, 3:\penalty0 e03476, 2014.

\bibitem[Babichev et~al.(2018)Babichev, Morozov, and
Dabaghian]{babichev2018robust}
Andrey Babichev, Dmitriy Morozov, and Yuri Dabaghian.
\newblock Robust spatial memory maps encoded by networks with transient
connections.
\newblock \emph{PLoS Comput. Biol.}, 14\penalty0 (9):\penalty0 e1006433, 2018.

\bibitem[Reimann et~al.(2017)Reimann, Nolte, Scolamiero, Turner, Perin,
Chindemi, D{\l}otko, Levi, Hess, and Markram]{reimann2017cliques}
Michael~W Reimann, Max Nolte, Martina Scolamiero, Katharine Turner, Rodrigo
Perin, Giuseppe Chindemi, Pawe{\l} D{\l}otko, Ran Levi, Kathryn Hess, and
Henry Markram.
\newblock Cliques of neurons bound into cavities provide a missing link between
structure and function.
\newblock \emph{Front. Comput. Neurosci.}, 11:\penalty0 48, 2017.

\bibitem[Huang et~al.(2017)Huang, Xu, Chu, Jiang, and Yu]{huang2017weak}
Xuhui Huang, Kaibin Xu, Congying Chu, Tianzi Jiang, and Shan Yu.
\newblock Weak higher-order interactions in macroscopic functional networks of
the resting brain.
\newblock \emph{J. Neurosci.}, 37\penalty0 (43):\penalty0 10481--10497, 2017.

\bibitem[Zhang et~al.(2017{\natexlab{b}})Zhang, Chen, Zhang, and
Shen]{zhang2017test}
Han Zhang, Xiaobo Chen, Yu~Zhang, and Dinggang Shen.
\newblock Test-retest reliability of ``high-order'' functional connectivity in
young healthy adults.
\newblock \emph{Front. Neurosci.}, 11:\penalty0 439, 2017{\natexlab{b}}.

\bibitem[Plis et~al.(2014)Plis, Sui, Lane, Roy, Clark, Potluru, Huster,
Michael, Sponheim, Weisend, et~al.]{plis2014high}
Sergey~M Plis, Jing Sui, Terran Lane, Sushmita Roy, Vincent~P Clark, Vamsi~K
Potluru, Rene~J Huster, Andrew Michael, Scott~R Sponheim, Michael~P Weisend,
et~al.
\newblock High-order interactions observed in multi-task intrinsic networks are
dominant indicators of aberrant brain function in schizophrenia.
\newblock \emph{Neuroimage}, 102:\penalty0 35--48, 2014.

\bibitem[Zhang et~al.(2016)Zhang, Chen, Shi, Li, Kim, Giannakopoulos, Haller,
and Shen]{zhang2016topographical}
Han Zhang, Xiaobo Chen, Feng Shi, Gang Li, Minjeong Kim, Panteleimon
Giannakopoulos, Sven Haller, and Dinggang Shen.
\newblock Topographical information-based high-order functional connectivity
and its application in abnormality detection for mild cognitive impairment.
\newblock \emph{J. Alzheimers Dis.}, 54\penalty0 (3):\penalty0 1095--1112,
2016.

\bibitem[Lee et~al.(2017)Lee, Kang, Chung, Lim, Kim, and
Lee]{lee2017integrated}
Hyekyoung Lee, Hyejin Kang, Moo~K Chung, Seonhee Lim, Bung-Nyun Kim, and
Dong~Soo Lee.
\newblock Integrated multimodal network approach to {{PET}} and {{MRI}} based
on multidimensional persistent homology.
\newblock \emph{Hum. Brain Mapp.}, 38\penalty0 (3):\penalty0 1387--1402, 2017.

\bibitem[Lee et~al.(2014)Lee, Chung, Kang, and Lee]{lee2014hole}
Hyekyoung Lee, Moo~K Chung, Hyejin Kang, and Dong~Soo Lee.
\newblock Hole detection in metabolic connectivity of {{Alzheimer}}'s disease
using k- {{Laplacian}}.
\newblock In \emph{International Conference on Medical Image Computing and
    Computer-Assisted Intervention}, pages 297--304. {Springer}, 2014.

\bibitem[Sizemore et~al.(2018{\natexlab{b}})Sizemore, Giusti, Kahn, Vettel,
Betzel, and Bassett]{sizemore2018cliques}
Ann~E Sizemore, Chad Giusti, Ari Kahn, Jean~M Vettel, Richard~F Betzel, and
Danielle~S Bassett.
\newblock Cliques and cavities in the human connectome.
\newblock \emph{J. Comput. Neurosci.}, 44\penalty0 (1):\penalty0 115--145,
2018{\natexlab{b}}.

\bibitem[Bendich et~al.(2016)Bendich, Marron, Miller, Pieloch, and
Skwerer]{bendich2016persistent}
Paul Bendich, James~S Marron, Ezra Miller, Alex Pieloch, and Sean Skwerer.
\newblock Persistent homology analysis of brain artery trees.
\newblock \emph{Ann. Appl. Stat.}, 10\penalty0 (1):\penalty0 198, 2016.

\bibitem[Lee et~al.(2012)Lee, Kang, Chung, Kim, and Lee]{lee2012persistent}
Hyekyoung Lee, Hyejin Kang, Moo~K Chung, Bung-Nyun Kim, and Dong~Soo Lee.
\newblock Persistent brain network homology from the perspective of dendrogram.
\newblock \emph{IEEE Trans. Med. Imaging}, 31\penalty0 (12):\penalty0
2267--2277, 2012.

\bibitem[Lee et~al.(2011)Lee, Chung, Kang, Kim, and Lee]{lee2011discriminative}
Hyekyoung Lee, Moo~K Chung, Hyejin Kang, Bung-Nyun Kim, and Dong~Soo Lee.
\newblock Discriminative persistent homology of brain networks.
\newblock In \emph{2011 {{IEEE}} International Symposium on Biomedical Imaging:
    {{From}} Nano to Macro}, pages 841--844. {IEEE}, 2011.

\bibitem[Chung et~al.(2017)Chung, {Villalta-Gil}, Lee, Rathouz, Lahey, and
Zald]{chung2017exact}
Moo~K Chung, Victoria {Villalta-Gil}, Hyekyoung Lee, Paul~J Rathouz, Benjamin~B
Lahey, and David~H Zald.
\newblock Exact topological inference for paired brain networks via persistent
homology.
\newblock In \emph{International Conference on Information Processing in
    Medical Imaging}, pages 299--310. {Springer}, 2017.

\bibitem[Rybakken et~al.(2019)Rybakken, Baas, and Dunn]{rybakken2019decoding}
Erik Rybakken, Nils Baas, and Benjamin Dunn.
\newblock Decoding of neural data using cohomological feature extraction.
\newblock \emph{Neural Comput.}, 31\penalty0 (1):\penalty0 68--93, 2019.

\bibitem[Lord et~al.(2016)Lord, Expert, Fernandes, Petri, Van~Hartevelt,
Vaccarino, Deco, Turkheimer, and Kringelbach]{lord2016insights}
Louis-David Lord, Paul Expert, Henrique~M Fernandes, Giovanni Petri, Tim~J
Van~Hartevelt, Francesco Vaccarino, Gustavo Deco, Federico Turkheimer, and
Morten~L Kringelbach.
\newblock Insights into brain architectures from the homological scaffolds of
functional connectivity networks.
\newblock \emph{Front. Syst. Neurosci.}, 10:\penalty0 85, 2016.

\bibitem[Lee et~al.(2019)Lee, Chung, Choi, Kang, Ha, Kim, and
Lee]{lee2019harmonic}
Hyekyoung Lee, Moo~K Chung, Hongyoon Choi, Hyejin Kang, Seunggyun Ha, Yu~Kyeong
Kim, and Dong~Soo Lee.
\newblock Harmonic holes as the submodules of brain network and network
dissimilarity.
\newblock In \emph{International Workshop on Computational Topology in Image
    Context}, pages 110--122. {Springer}, 2019.

\bibitem[Chung et~al.(2019)Chung, Lee, DiChristofano, Ombao, and
Solo]{chung2019exact}
Moo~K Chung, Hyekyoung Lee, Alex DiChristofano, Hernando Ombao, and Victor
Solo.
\newblock Exact topological inference of the resting-state brain networks in
twins.
\newblock \emph{Netw. Neurosci.}, 3\penalty0 (3):\penalty0 674--694, 2019.

\bibitem[{Ib{\'a}{\~n}ez-Marcelo}
et~al.(2019{\natexlab{b}}){Ib{\'a}{\~n}ez-Marcelo}, Campioni, Manzoni,
Santarcangelo, and Petri]{ibanez2019spectral}
Esther {Ib{\'a}{\~n}ez-Marcelo}, Lisa Campioni, Diego Manzoni, Enrica~L
Santarcangelo, and Giovanni Petri.
\newblock Spectral and topological analyses of the cortical representation of
the head position: {{Does}} hypnotizability matter?
\newblock \emph{Brain Behav.}, 9\penalty0 (6):\penalty0 e01277,
2019{\natexlab{b}}.

\bibitem[Saggar et~al.(2018)Saggar, Sporns, {Gonzalez-Castillo}, Bandettini,
Carlsson, Glover, and Reiss]{saggar2018towards}
Manish Saggar, Olaf Sporns, Javier {Gonzalez-Castillo}, Peter~A Bandettini,
Gunnar Carlsson, Gary Glover, and Allan~L Reiss.
\newblock Towards a new approach to reveal dynamical organization of the brain
using topological data analysis.
\newblock \emph{Nat. Commun.}, 9\penalty0 (1):\penalty0 1--14, 2018.

\bibitem[Ellis et~al.(2019)Ellis, Lesnick, {Henselman-Petrusek}, Keller, and
Cohen]{ellis2019feasibility}
Cameron~T Ellis, Michael Lesnick, Gregory {Henselman-Petrusek}, Bryn Keller,
and Jonathan~D Cohen.
\newblock Feasibility of topological data analysis for event-related {{fMRI}}.
\newblock \emph{Netw. Neurosci.}, 3\penalty0 (3):\penalty0 695--706, 2019.

\bibitem[Giusti et~al.(2016)Giusti, Ghrist, and Bassett]{giusti2016two}
Chad Giusti, Robert Ghrist, and Danielle~S Bassett.
\newblock Two's company, three (or more) is a simplex.
\newblock \emph{J. Comput. Neurosci.}, 41\penalty0 (1):\penalty0 1--14, 2016.

\bibitem[Sizemore et~al.(2019)Sizemore, {Phillips-Cremins}, Ghrist, and
Bassett]{sizemore2019importance}
Ann~E Sizemore, Jennifer~E {Phillips-Cremins}, Robert Ghrist, and Danielle~S
Bassett.
\newblock The importance of the whole: Topological data analysis for the
network neuroscientist.
\newblock \emph{Netw Neurosci}, 3\penalty0 (3):\penalty0 656--673, 2019.

\bibitem[Case and Bender(1981)]{case1981testing}
Ted~J. Case and Edward~A. Bender.
\newblock Testing for higher order interactions.
\newblock \emph{Am. Nat.}, 118\penalty0 (6):\penalty0 920--929, 1981.

\bibitem[Abrams(1983)]{abrams1983arguments}
Peter~A. Abrams.
\newblock Arguments in favor of higher order interactions.
\newblock \emph{Am. Nat.}, 121\penalty0 (6):\penalty0 887--891, 1983.

\bibitem[Kareiva(1994)]{kareiva1994foil}
Peter Kareiva.
\newblock Special feature: {{Higher}} order interactions as a foil to
reductionist ecology.
\newblock \emph{Ecology}, 75\penalty0 (6), 1994.

\bibitem[Billick and Case(1994)]{billick1994higher}
Ian Billick and Ted~J Case.
\newblock Higher order interactions in ecological communities: What are they
and how can they be detected?
\newblock \emph{Ecology}, 75\penalty0 (6):\penalty0 1529--1543, 1994.

\bibitem[Wootton(1993)]{wootton1993indirect}
J~Timothy Wootton.
\newblock Indirect effects and habitat use in an intertidal community:
Interaction chains and interaction modifications.
\newblock \emph{Am. Nat.}, 141\penalty0 (1):\penalty0 71--89, 1993.

\bibitem[Bairey et~al.(2017)Bairey, Kelsic, and Kishony]{bairey2016high}
Eyal Bairey, Eric~D. Kelsic, and Roy Kishony.
\newblock High-order species interactions shape ecosystem diversity.
\newblock \emph{Nat. Commun.}, 7\penalty0 (1):\penalty0 12285, 2017.

\bibitem[Kelsic et~al.(2015)Kelsic, Zhao, Vetsigian, and
Kishony]{kelsic2015counteraction}
Eric~D Kelsic, Jeffrey Zhao, Kalin Vetsigian, and Roy Kishony.
\newblock Counteraction of antibiotic production and degradation stabilizes
microbial communities.
\newblock \emph{Nature}, 521\penalty0 (7553):\penalty0 516, 2015.

\bibitem[Perlin et~al.(2009)Perlin, Clark, McKenzie, Patel, Jackson, Kormanik,
Powell, Bajorek, Myers, Dugatkin, et~al.]{perlin2009protection}
Michael~H Perlin, Denise~R Clark, Courtney McKenzie, Himati Patel, Nikki
Jackson, Cecile Kormanik, Cayse Powell, Alexander Bajorek, David~A Myers,
Lee~A Dugatkin, et~al.
\newblock Protection of {{Salmonella}} by ampicillin-resistant {{Escherichia}}
coli in the presence of otherwise lethal drug concentrations.
\newblock \emph{Proc. R. Soc. B Biol. Sci.}, 276\penalty0 (1674):\penalty0
3759--3768, 2009.

\bibitem[Abrudan et~al.(2015)Abrudan, Smakman, Grimbergen, Westhoff, Miller,
Van~Wezel, and Rozen]{abrudan2015socially}
Monica~I Abrudan, Fokko Smakman, Ard~Jan Grimbergen, Sanne Westhoff, Eric~L
Miller, Gilles~P Van~Wezel, and Daniel~E Rozen.
\newblock Socially mediated induction and suppression of antibiosis during
bacterial coexistence.
\newblock \emph{Proc. Natl. Acad. Sci.}, 112\penalty0 (35):\penalty0
11054--11059, 2015.

\bibitem[{Koen-Alonso}(2007)]{koen2007process}
Mariano {Koen-Alonso}.
\newblock A process-oriented approach to the multispecies functional response.
\newblock In \emph{From Energetics to Ecosystems: The Dynamics and Structure of
    Ecological Systems}, pages 1--36. {Springer}, 2007.

\bibitem[{de Oliveira} and Fontanari(2000)]{deoliveira2000replicators}
Viviane~M. {de Oliveira} and J.~F. Fontanari.
\newblock Random replicators with high-order interactions.
\newblock \emph{Phys. Rev. Lett.}, 85\penalty0 (23):\penalty0 4984--4987, 2000.

\bibitem[Yoshino et~al.(2008)Yoshino, Galla, and Tokita]{yoshino2008rank}
Yoshimi Yoshino, Tobias Galla, and Kei Tokita.
\newblock Rank abundance relations in evolutionary dynamics of random
replicators.
\newblock \emph{Phys. Rev. E}, 78\penalty0 (3):\penalty0 031924, 2008.

\bibitem[Sonntag and Teichert(2004)]{sonntag2004competition}
Martin Sonntag and Hanns-Martin Teichert.
\newblock Competition hypergraphs.
\newblock \emph{Discrete Appl. Math.}, 143\penalty0 (1):\penalty0 324--329,
2004.

\bibitem[Golubski et~al.(2016)Golubski, Westlund, Vandermeer, and
Pascual]{golubski2016ecological}
Antonio~J Golubski, Erik~E Westlund, John Vandermeer, and Mercedes Pascual.
\newblock Ecological networks over the edge: Hypergraph trait-mediated indirect
interaction ({{TMII}}) structure.
\newblock \emph{Trends Ecol. Evol.}, 31\penalty0 (5):\penalty0 344--354, 2016.

\bibitem[May(1972)]{may1972stable}
Robert~M May.
\newblock Will a large complex system be stable?
\newblock \emph{Nature}, 436:\penalty0 413--414, 1972.

\bibitem[Vandermeer(1969)]{vandermeer1969competitive}
John~H. Vandermeer.
\newblock The competitive structure of communities: {{An}} experimental
approach with protozoa.
\newblock \emph{Ecology}, 50\penalty0 (3):\penalty0 362--371, 1969.

\bibitem[Neill(1974)]{neil1974competition}
William~E. Neill.
\newblock The community matrix and interdependence of the competition
coefficients.
\newblock \emph{Am. Nat.}, 108\penalty0 (962):\penalty0 399--408, 1974.

\bibitem[Dormann and Roxburgh(2005)]{dormann2005coexistence}
Carsten~F Dormann and Stephen~H Roxburgh.
\newblock Experimental evidence rejects pairwise modelling approach to
coexistence in plant communities.
\newblock \emph{Proc Biol Sci}, 272\penalty0 (1569):\penalty0 1279--1285, 2005.

\bibitem[Weigelt et~al.(2007)Weigelt, Schumacher, Walther, Bartelheimer,
Steinlein, and Beyschlag]{weigelt2007competition}
Alexandra Weigelt, Jens Schumacher, Tim Walther, Maik Bartelheimer, Tom
Steinlein, and Wolfram Beyschlag.
\newblock Identifying mechanisms of competition in multi-species communities.
\newblock \emph{J. Ecol.}, 95\penalty0 (1):\penalty0 53--64, 2007.

\bibitem[Allesina and Levine(2011)]{allesina2011competitive}
Stefano Allesina and Jonathan~M Levine.
\newblock A competitive network theory of species diversity.
\newblock \emph{Proc. Natl. Acad. Sci.}, 108\penalty0 (14):\penalty0
5638--5642, 2011.

\bibitem[Kerr et~al.(2002)Kerr, Riley, Feldman, and Bohannan]{kerr2002local}
Benjamin Kerr, Margaret~A Riley, Marcus~W Feldman, and Brendan~JM Bohannan.
\newblock Local dispersal promotes biodiversity in a real-life game of
rock\textendash{}paper\textendash{}scissors.
\newblock \emph{Nature}, 418\penalty0 (6894):\penalty0 171, 2002.

\bibitem[Hofbauer and Sigmund(2003)]{hofbauer2003evolutionary}
Josef Hofbauer and Karl Sigmund.
\newblock Evolutionary game dynamics.
\newblock \emph{Bull. Am. Math. Soc.}, 40\penalty0 (4):\penalty0 479--519,
2003.

\bibitem[Nowak and Sigmund(2004)]{nowak2004evolutionary}
Martin~A Nowak and Karl Sigmund.
\newblock Evolutionary dynamics of biological games.
\newblock \emph{science}, 303\penalty0 (5659):\penalty0 793--799, 2004.

\bibitem[Taylor and Jonker(1978)]{taylor1978evolutionary}
Peter~D Taylor and Leo~B Jonker.
\newblock Evolutionary stable strategies and game dynamics.
\newblock \emph{Math. Biosci.}, 40\penalty0 (1-2):\penalty0 145--156, 1978.

\bibitem[Hofbauer et~al.(2010)Hofbauer, Schuster, Sigmund,
et~al.]{hofbauer2010note}
Josef Hofbauer, Peter Schuster, Karl Sigmund, et~al.
\newblock A note on evolutionary stable strategies and game dynamics.
\newblock Technical report, {David K. Levine}, 2010.

\bibitem[Mayfield and Stouffer(2017)]{mayfield2017higher}
Margaret~M Mayfield and Daniel~B Stouffer.
\newblock Higher-order interactions capture unexplained complexity in diverse
communities.
\newblock \emph{Nat. Ecol. Evol.}, 1\penalty0 (3):\penalty0 0062, 2017.

\bibitem[Valverde et~al.(2020)Valverde, Vidiella, Monta{\~n}ez, Fraile,
Sacrist{\'a}n, and {Garc{\'i}a-Arenal}]{valverde2020coexistence}
Sergi Valverde, Blai Vidiella, Ra{\'u}l Monta{\~n}ez, Aurora Fraile, Soledad
Sacrist{\'a}n, and Fernando {Garc{\'i}a-Arenal}.
\newblock Coexistence of nestedness and modularity in hos-pathogen
infection networks.
\newblock \emph{Nat. Ecol. Evol.}, pages 1--10, 2020.

\bibitem[Mariani et~al.(2019)Mariani, Ren, Bascompte, and
Tessone]{mariani2019nestedness}
Manuel~Sebastian Mariani, Zhuo-Ming Ren, Jordi Bascompte, and Claudio~Juan
Tessone.
\newblock Nestedness in complex networks: Observation, emergence, and
implications.
\newblock \emph{Physics Reports}, 2019.

\bibitem[Oltvai and Barab{\'a}si(2002)]{oltvai2002life}
Zolt{\'a}n~N Oltvai and Albert-L{\'a}szl{\'o} Barab{\'a}si.
\newblock Life's complexity pyramid.
\newblock \emph{Science}, 298\penalty0 (5594):\penalty0 763--764, 2002.

\bibitem[Aittokallio and Schwikowski(2006)]{aittokallio2006graph}
Tero Aittokallio and Benno Schwikowski.
\newblock Graph-based methods for analysing networks in cell biology.
\newblock \emph{Brief. Bioinform.}, 7\penalty0 (3):\penalty0 243--255, 2006.

\bibitem[Vermeulen et~al.(2020)Vermeulen, Schymanski, Barab{\'a}si, and
Miller]{vermeulen2020exposome}
Roel Vermeulen, Emma~L Schymanski, Albert-L{\'a}szl{\'o} Barab{\'a}si, and
Gary~W Miller.
\newblock The exposome and health: {{Where}} chemistry meets biology.
\newblock \emph{Science}, 367\penalty0 (6476):\penalty0 392--396, 2020.

\bibitem[Ruepp et~al.(2010)Ruepp, Waegele, Lechner, Brauner,
{Dunger-Kaltenbach}, Fobo, Frishman, Montrone, and Mewes]{ruepp2010corum}
Andreas Ruepp, Brigitte Waegele, Martin Lechner, Barbara Brauner, Irmtraud
{Dunger-Kaltenbach}, Gisela Fobo, Goar Frishman, Corinna Montrone, and
H-Werner Mewes.
\newblock {{CORUM}}: The comprehensive resource of mammalian protein
complexes\textemdash{}2009.
\newblock \emph{Nucleic Acids Res.}, 38\penalty0 (suppl\_1):\penalty0
D497--D501, 2010.

\bibitem[Wong et~al.(2008)Wong, Althammer, Hildebrand, Kirschner, Pagel,
Geissler, Smialowski, Bl{\"o}chl, Oesterheld, Schmidt,
et~al.]{wong2008evolutionary}
Philip Wong, Sonja Althammer, Andrea Hildebrand, Andreas Kirschner, Philipp
Pagel, Bernd Geissler, Pawel Smialowski, Florian Bl{\"o}chl, Matthias
Oesterheld, Thorsten Schmidt, et~al.
\newblock An evolutionary and structural characterization of mammalian protein
complex organization.
\newblock \emph{Bmc Genomics}, 9\penalty0 (1):\penalty0 629, 2008.

\bibitem[Klamt et~al.(2009)Klamt, Haus, and Theis]{klamt2009hypergraphs}
Steffen Klamt, Utz-Uwe Haus, and Fabian Theis.
\newblock Hypergraphs and cellular networks.
\newblock \emph{PLoS Comput. Biol.}, 5:\penalty0 e1000385, 2009.

\bibitem[Ritz et~al.(2014)Ritz, Tegge, Kim, Poirel, and
Murali]{ritz2014signaling}
Anna Ritz, Allison~N. Tegge, Hyunju Kim, Christopher~L. Poirel, and T.M.
Murali.
\newblock Signaling hypergraphs.
\newblock \emph{Trends Biotechnol.}, 32\penalty0 (7):\penalty0 356--362, 2014.

\bibitem[Gaudelet et~al.(2018)Gaudelet, {Malod-Dognin}, and Pr{\v
    z}ulj]{gaudelet2018higher}
Thomas Gaudelet, Noel {Malod-Dognin}, and Nata{\v s}a Pr{\v z}ulj.
\newblock Higher-order molecular organization as a source of biological
function.
\newblock \emph{Bioinformatics}, 34\penalty0 (17):\penalty0 i944--i953, 2018.

\bibitem[Pr{\v{z}}ulj et~al.(2004)Pr{\v{z}}ulj, Corneil, and
Jurisica]{prvzulj2004modeling}
Natasa Pr{\v{z}}ulj, Derek~G Corneil, and Igor Jurisica.
\newblock Modeling interactome: scale-free or geometric?
\newblock \emph{Bioinformatics}, 20\penalty0 (18):\penalty0 3508--3515, 2004.

\bibitem[Franzese et~al.(2019)Franzese, Groce, Murali, and
Ritz]{franzese2019hypergraph}
Nicholas Franzese, Adam Groce, TM~Murali, and Anna Ritz.
\newblock Hypergraph-based connectivity measures for signaling pathway
topologies.
\newblock \emph{PLoS Comput. Biol.}, 15\penalty0 (10), 2019.

\bibitem[Klimm et~al.(2020)Klimm, Deane, and Reinert]{klimm2020hypergraphs}
Florian Klimm, Charlotte~M Deane, and Gesine Reinert.
\newblock Hypergraphs for predicting essential genes using multiprotein complex
data.
\newblock \emph{bioRxiv}, 2020.

\bibitem[Pearcy et~al.(2016)Pearcy, Chuzhanova, and
Crofts]{pearcy2016complexity}
Nicole Pearcy, Nadia Chuzhanova, and Jonathan~J Crofts.
\newblock Complexity and robustness in hypernetwork models of metabolism.
\newblock \emph{J. Theor. Biol.}, 406:\penalty0 99--104, 2016.

\bibitem[Shen et~al.(2018{\natexlab{b}})Shen, Zhang, Chen, Gu, Liang, Xu, Li,
Wei, Liu, Yi, et~al.]{shen2018genome}
Tie Shen, Zhengdong Zhang, Zhen Chen, Dagang Gu, Shen Liang, Yang Xu, Ruiyuan
Li, Yimin Wei, Zhijie Liu, Yin Yi, et~al.
\newblock A genome-scale metabolic network alignment method within a
hypergraph-based framework using a rotational tensor-vector product.
\newblock \emph{Sci. Rep.}, 8\penalty0 (1):\penalty0 1--16, 2018{\natexlab{b}}.

\bibitem[Jost and Mulas(2019)]{jost2019hypergraph}
J{\"u}rgen Jost and Raffaella Mulas.
\newblock Hypergraph {{Laplace}} operators for chemical reaction networks.
\newblock \emph{Adv. Math.}, 351:\penalty0 870--896, 2019.

\bibitem[Tian et~al.(2009)Tian, Hwang, and Kuang]{tian2009hypergraph}
Ze~Tian, TaeHyun Hwang, and Rui Kuang.
\newblock A hypergraph-based learning algorithm for classifying gene expression
and {{arrayCGH}} data with prior knowledge.
\newblock \emph{Bioinformatics}, 25\penalty0 (21):\penalty0 2831--2838, 2009.

\bibitem[Battle et~al.(2010)Battle, Jonikas, Walter, Weissman, and
Koller]{battle2010automated}
Alexis Battle, Martin~C Jonikas, Peter Walter, Jonathan~S Weissman, and Daphne
Koller.
\newblock Automated identification of pathways from quantitative genetic
interaction data.
\newblock \emph{Mol. Syst. Biol.}, 6\penalty0 (1), 2010.

\bibitem[Sumazin et~al.(2011)Sumazin, Yang, Chiu, Chung, Iyer, {Llobet-Navas},
Rajbhandari, Bansal, Guarnieri, Silva, et~al.]{sumazin2011extensive}
Pavel Sumazin, Xuerui Yang, Hua-Sheng Chiu, Wei-Jen Chung, Archana Iyer, David
{Llobet-Navas}, Presha Rajbhandari, Mukesh Bansal, Paolo Guarnieri, Jose
Silva, et~al.
\newblock An extensive {{microRNA}}-mediated network of {{RNA}}-{{RNA}}
interactions regulates established oncogenic pathways in glioblastoma.
\newblock \emph{Cell}, 147\penalty0 (2):\penalty0 370--381, 2011.

\bibitem[Rahman et~al.(2013)Rahman, Poirel, Badger, Estep, and
Murali]{rahman2013reverse}
Ahsanur Rahman, Christopher~L Poirel, David~J Badger, Craig Estep, and
TM~Murali.
\newblock Reverse engineering molecular hypergraphs.
\newblock \emph{IEEE/ACM Trans. Comput. Biol. Bioinform.}, 10\penalty0
(5):\penalty0 1113--1124, 2013.

\bibitem[Kong and Yu(2019)]{kong2019hypergraph}
Yunchuan Kong and Tianwei Yu.
\newblock A hypergraph-based method for large-scale dynamic correlation study
at the transcriptomic scale.
\newblock \emph{BMC Genomics}, 20\penalty0 (1):\penalty0 397, 2019.

\bibitem[Zimmer et~al.(2016)Zimmer, Katzir, Dekel, Mayo, and
Alon]{zimmer2016prediction}
Anat Zimmer, Itay Katzir, Erez Dekel, Avraham~E Mayo, and Uri Alon.
\newblock Prediction of multidimensional drug dose responses based on
measurements of drug pairs.
\newblock \emph{Proc. Natl. Acad. Sci.}, 113\penalty0 (37):\penalty0
10442--10447, 2016.

\bibitem[Katzir et~al.(2019)Katzir, Cokol, Aldridge, and
Alon]{katzir2019prediction}
Itay Katzir, Murat Cokol, Bree~B Aldridge, and Uri Alon.
\newblock Prediction of ultra-high-order antibiotic combinations based on
pairwise interactions.
\newblock \emph{PLoS Comput. Biol.}, 15\penalty0 (1):\penalty0 e1006774, 2019.

\bibitem[Tendler et~al.(2019)Tendler, Zimmer, Mayo, and Alon]{tendler2019noise}
Avichai Tendler, Anat Zimmer, Avi Mayo, and Uri Alon.
\newblock Noise-precision tradeoff in predicting combinations of mutations and
drugs.
\newblock \emph{PLoS Comput. Biol.}, 15\penalty0 (5):\penalty0 e1006956, 2019.

\bibitem[Zimmer et~al.(2017)Zimmer, Tendler, Katzir, Mayo, and
Alon]{zimmer2017prediction}
Anat Zimmer, Avichai Tendler, Itay Katzir, Avi Mayo, and Uri Alon.
\newblock Prediction of drug cocktail effects when the number of measurements
is limited.
\newblock \emph{PLoS Biol.}, 15\penalty0 (10):\penalty0 e2002518, 2017.

\bibitem[Otwinowski and Plotkin(2014)]{otwinowski2014inferring}
Jakub Otwinowski and Joshua~B Plotkin.
\newblock Inferring fitness landscapes by regression produces biased estimates
of epistasis.
\newblock \emph{Proc. Natl. Acad. Sci.}, 111\penalty0 (22):\penalty0
E2301--E2309, 2014.

\bibitem[Crona et~al.(2017)Crona, Gavryushkin, Greene, and
Beerenwinkel]{crona2017inferring}
Kristina Crona, Alex Gavryushkin, Devin Greene, and Niko Beerenwinkel.
\newblock Inferring genetic interactions from comparative fitness data.
\newblock \emph{Elife}, 6:\penalty0 e28629, 2017.

\bibitem[Weinreich et~al.(2013)Weinreich, Lan, Wylie, and
Heckendorn]{weinreich2013should}
Daniel~M Weinreich, Yinghong Lan, C~Scott Wylie, and Robert~B Heckendorn.
\newblock Should evolutionary geneticists worry about higher-order epistasis?
\newblock \emph{Curr. Opin. Genet. Dev.}, 23\penalty0 (6):\penalty0 700--707,
2013.

\bibitem[{Sanchez-Gorostiaga} et~al.(2018){Sanchez-Gorostiaga}, Baji{\'c},
Osborne, Poyatos, and Sanchez]{sanchez2018high}
Alicia {Sanchez-Gorostiaga}, Djordje Baji{\'c}, Melisa~L Osborne, Juan~F
Poyatos, and Alvaro Sanchez.
\newblock High-order interactions dominate the functional landscape of
microbial consortia.
\newblock \emph{bioRxiv}, page 333534, 2018.

\bibitem[Mackay and Moore(2014)]{mackay2014epistasis}
Trudy~FC Mackay and Jason~H Moore.
\newblock Why epistasis is important for tackling complex human disease
genetics.
\newblock \emph{Genome Med.}, 6\penalty0 (6):\penalty0 42, 2014.

\bibitem[Sanchez(2019)]{sanchez2019defining}
Alvaro Sanchez.
\newblock Defining higher-order interactions in synthetic ecology: {{Lessons}}
from physics and quantitative genetics.
\newblock \emph{Cell Syst.}, 9\penalty0 (6):\penalty0 519--520, 2019.

\bibitem[Guerrero et~al.(2019)Guerrero, Scarpino, Rodrigues, Hartl, and
Ogbunugafor]{guerrero2019proteostasis}
Rafael~F Guerrero, Samuel~V Scarpino, Jo{\~a}o~V Rodrigues, Daniel~L Hartl, and
C~Brandon Ogbunugafor.
\newblock Proteostasis environment shapes higher-order epistasis operating on
antibiotic resistance.
\newblock \emph{Genetics}, 212\penalty0 (2):\penalty0 565--575, 2019.

\bibitem[Yitbarek et~al.(2019)Yitbarek, Guittar, Knutie, and
Ogbunugafor]{yitbarek2019deconstructing}
Senay Yitbarek, John~Lee Guittar, Sarah~A Knutie, and C~Brandon Ogbunugafor.
\newblock Deconstructing higher-order interactions in the microbiota: {{A}}
theoretical examination.
\newblock \emph{bioRxiv}, page 647156, 2019.

\bibitem[Mickalide and Kuehn(2019)]{mickalide2019higher}
Harry Mickalide and Seppe Kuehn.
\newblock Higher-order interaction between species inhibits bacterial invasion
of a phototroph-predator microbial community.
\newblock \emph{Cell Syst.}, 9\penalty0 (6):\penalty0 521--533, 2019.

\bibitem[Niu et~al.(2019)Niu, Wang, Qu, and Yan]{niu2019rwhmda}
Yawei Niu, Guanghui Wang, Cunquan Qu, and Guiying Yan.
\newblock {{RWHMDA}}: {{Random}} walk on hypergraph for microbe-disease
association prediction.
\newblock \emph{Front. Microbiol.}, 10:\penalty0 1578, 2019.

\bibitem[St-Onge et~al.(2020)St-Onge, Thibeault, Allard, Dub{\'e}, and
H{\'e}bert-Dufresne]{stonge2020school}
Guillaume St-Onge, Vincent Thibeault, Antoine Allard, Louis~J Dub{\'e}, and
Laurent H{\'e}bert-Dufresne.
\newblock School closures, event cancellations, and the mesoscopic localization
of epidemics in networks with higher-order structure.
\newblock \emph{arXiv:2003.05924}, 2020.

\bibitem[Pokorny et~al.(2016)Pokorny, Hawasly, and
Ramamoorthy]{pokorny2016topological}
Florian~T Pokorny, Majd Hawasly, and Subramanian Ramamoorthy.
\newblock Topological trajectory classification with filtrations of simplicial
complexes and persistent homology.
\newblock \emph{Int. J. Robot. Res.}, 35\penalty0 (1-3):\penalty0 204--223,
2016.

\bibitem[Goubault et~al.(2018)Goubault, Ledent, and
Rajsbaum]{goubault2018simplicial}
{\'E}ric Goubault, J{\'e}r{\'e}my Ledent, and Sergio Rajsbaum.
\newblock A simplicial complex model for dynamic epistemic logic to study
distributed task computability.
\newblock In \emph{Proceedings Ninth International Symposium on Games,
    Automata, Logics, and Formal Verification}, 2018.

\bibitem[{van Ditmarsch} et~al.(2020){van Ditmarsch}, Goubault, Ledent, and
Rajsbaum]{van2020knowledge}
Hans {van Ditmarsch}, Eric Goubault, Jeremy Ledent, and Sergio Rajsbaum.
\newblock Knowledge and simplicial complexes.
\newblock \emph{arXiv:2002.08863}, 2020.

\bibitem[Reitz and Bianconi(2020)]{reitz2020higher}
Marcus Reitz and Ginestra Bianconi.
\newblock The higher-order spectrum of simplicial complexes: A renormalization
group approach.
\newblock \emph{arXiv:200309143}, 2020.

\bibitem[Kali{\v s}nik et~al.(2019)Kali{\v s}nik, Kurlin, and Le{\v
    s}nik]{kalivsnik2019higher}
Sara Kali{\v s}nik, Vitaliy Kurlin, and Davorin Le{\v s}nik.
\newblock A higher-dimensional homologically persistent skeleton.
\newblock \emph{Adv. Appl. Math.}, 102:\penalty0 113--142, 2019.

\bibitem[Guerra et~al.(2020)Guerra, Gregorio, Fugacci, Petri, and
Vaccarino]{guerra2020homological}
Marco Guerra, Alessandro~De Gregorio, Ulderico Fugacci, Giovanni Petri, and
Francesco Vaccarino.
\newblock Homological scaffold via minimal homology bases.
\newblock \emph{arXiv:2004.11606}, 2020.

\bibitem[Karypis et~al.(1999)Karypis, Aggarwal, Kumar, and
Shekhar]{karypis1999multilevel}
George Karypis, Rajat Aggarwal, Vipin Kumar, and Shashi Shekhar.
\newblock Multilevel hypergraph partitioning: Applications in {{VLSI}} domain.
\newblock \emph{IEEE Trans. Very Large Scale Integr. VLSI Syst.}, 7\penalty0
(1):\penalty0 69--79, 1999.

\bibitem[Neubauer and Obermayer(2009)]{neubauer2009towards}
Nicolas Neubauer and Klaus Obermayer.
\newblock Towards community detection in k-partite k-uniform hypergraphs.
\newblock In \emph{Proceedings of the {{NIPS}} 2009 Workshop on Analyzing
    Networks and Learning with Graphs}, pages 1--9, 2009.

\bibitem[Marietti and Testa(2008)]{marietti2008cores}
Mario Marietti and Damiano Testa.
\newblock Cores of simplicial complexes.
\newblock \emph{Discrete Comput. Geom.}, 40\penalty0 (3):\penalty0 444--468,
2008.

\bibitem[Duval et~al.(2013)Duval, Klivans, and Martin]{duval2013critical}
Art~M Duval, Caroline~J Klivans, and Jeremy~L Martin.
\newblock Critical groups of simplicial complexes.
\newblock \emph{Ann. Comb.}, 17\penalty0 (1):\penalty0 53--70, 2013.

\bibitem[Steenbergen et~al.(2014)Steenbergen, Klivans, and
Mukherjee]{steenbergen2014cheeger}
John Steenbergen, Caroline Klivans, and Sayan Mukherjee.
\newblock A {{Cheeger}}-type inequality on simplicial complexes.
\newblock \emph{Adv. Appl. Math.}, 56:\penalty0 56--77, 2014.

\bibitem[Parzanchevski(2017)]{parzanchevski2017mixing}
Ori Parzanchevski.
\newblock Mixing in high-dimensional expanders.
\newblock \emph{Comb. Probab. Comput.}, 26\penalty0 (5):\penalty0 746--761,
2017.

\bibitem[Sizemore et~al.(2017)Sizemore, Giusti, and
Bassett]{sizemore2017classification}
Ann Sizemore, Chad Giusti, and Danielle~S Bassett.
\newblock Classification of weighted networks through mesoscale homological
features.
\newblock \emph{J. Complex Netw.}, 5\penalty0 (2):\penalty0 245--273, 2017.

\bibitem[Petri et~al.(2013)Petri, Scolamiero, Donato, and
Vaccarino]{petri2013topological}
Giovanni Petri, Martina Scolamiero, Irene Donato, and Francesco Vaccarino.
\newblock Topological strata of weighted complex networks.
\newblock \emph{PLOS ONE}, 8\penalty0 (6), 2013.

\bibitem[Kuehn and Bick(2020)]{kuehn2020universal}
Christian Kuehn and Christian Bick.
\newblock A universal route to explosive phenomena.
\newblock \emph{arXiv:2002.10714}, 2020.

\bibitem[Bobrowski and Skraba(2020)]{bobrowski2020homological}
Omer Bobrowski and Primoz Skraba.
\newblock Homological percolation and the {{Euler}} characteristic.
\newblock \emph{Phys. Rev. E}, 101\penalty0 (3):\penalty0 032304, 2020.

\bibitem[Phinyomark et~al.(2017)Phinyomark, {Ibanez-Marcelo}, and
Petri]{phinyomark2017resting}
Angkoon Phinyomark, Esther {Ibanez-Marcelo}, and Giovanni Petri.
\newblock Resting-state fmri functional connectivity: {{Big}} data
preprocessing pipelines and topological data analysis.
\newblock \emph{IEEE Trans. Big Data}, 3\penalty0 (4):\penalty0 415--428, 2017.

\bibitem[Battiston et~al.(2010)Battiston, Glattfelder, Garlaschelli, Lillo, and
Caldarelli]{battiston2010structure}
Stefano Battiston, James~B Glattfelder, Diego Garlaschelli, Fabrizio Lillo, and
Guido Caldarelli.
\newblock The structure of financial networks.
\newblock In \emph{Network Science}, pages 131--163. {Springer}, 2010.

\bibitem[Faes et~al.(2015)Faes, Kugiumtzis, Nollo, Jurysta, and
Marinazzo]{faes2015estimating}
Luca Faes, Dimitris Kugiumtzis, Giandomenico Nollo, Fabrice Jurysta, and
Daniele Marinazzo.
\newblock Estimating the decomposition of predictive information in
multivariate systems.
\newblock \emph{Phys. Rev. E}, 91\penalty0 (3):\penalty0 032904, 2015.

\bibitem[Faes et~al.(2017)Faes, Marinazzo, and Stramaglia]{faes2017multiscale}
Luca Faes, Daniele Marinazzo, and Sebastiano Stramaglia.
\newblock Multiscale information decomposition: {{Exact}} computation for
multivariate {{Gaussian}} processes.
\newblock \emph{Entropy}, 19\penalty0 (8):\penalty0 408, 2017.

\bibitem[Rosas et~al.(2019)Rosas, Mediano, Gastpar, and
Jensen]{rosas2019quantifying}
Fernando~E Rosas, Pedro~AM Mediano, Michael Gastpar, and Henrik~J Jensen.
\newblock Quantifying high-order interdependencies via multivariate extensions
of the mutual information.
\newblock \emph{Phys. Rev. E}, 100\penalty0 (3):\penalty0 032305, 2019.

\bibitem[{H{\'e}bert-Dufresne} et~al.(2020){H{\'e}bert-Dufresne}, Scarpino, and
Young]{hebert2020macroscopic}
Laurent {H{\'e}bert-Dufresne}, Samuel~V Scarpino, and Jean-Gabriel Young.
\newblock Macroscopic patterns of interacting contagions are indistinguishable
from social reinforcement.
\newblock \emph{Nat. Phys.}, pages 1--6, 2020.

\bibitem[Peixoto(2019)]{peixoto2019network}
Tiago~P Peixoto.
\newblock Network reconstruction and community detection from dynamics.
\newblock \emph{Phys. Rev. Lett.}, 123\penalty0 (12):\penalty0 128301, 2019.
